### 2024-06-08 Rebuttal/Response to Reviewer 1.tex
Initial commit

%\documentclass[final]{article}
\documentclass[]{article}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=0.75in,
	top=0.75in,
	right=0.75in,
	bottom=1in,
}
\newcommand{\extramargin}[1]{}
%\newcommand{\extramargin}[1]{
%	\setlength{\paperwidth}{250mm}
%	\setlength{\evensidemargin}{-15mm}
%	\setlength{\oddsidemargin}{-15mm}
%}
\usepackage{gensymb}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}
\usepackage{amsmath}
\usepackage[url=false,
backend=bibtex,
style=authoryear-comp,
giveninits=true,
doi=true,
isbn=true,
backref=false,
dashed=false,
maxcitenames=2,
maxbibnames=99,
natbib=true]{biblatex}
\DeclareNameAlias{author}{last-first}
\DeclareFieldFormat
[article,inbook,incollection,inproceedings,patent,thesis,
unpublished,techreport,misc,book]
{title}{#1}
\renewcommand*{\revsdnamepunct}{}
\renewbibmacro{in:}{}
\usepackage{xpatch}
\xpatchbibmacro{date+extradate}{%
	\printtext[parens]%
}{%
	\setunit*{\space}%
	\printtext%
}{}{}

\addbibresource{../Main/ViscousDropImpact_v2.bib}
\nonfrenchspacing
\setlength\parindent{0pt}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{mathrsfs}
\usepackage[colorlinks,citecolor=purple]{hyperref}
\newcommand*\blue{\textcolor{blue}}
\newcommand*\red{\textcolor{red}}
\newcommand{\VS}[1]{{\textcolor{orange}{#1}}}

\renewcommand{\thefigure}{R\arabic{figure}}

\usepackage[obeyFinal,colorinlistoftodos, textwidth=60mm, shadow]{todonotes}
% todonotes specific macros begin!
\newcommand{\todoInsertref}[2]{\todo[color=green!40, #1]{#2}}
\newcommand{\todoExplaininDetails}[2]{\todo[color=orange!40, #1]{#2}}
\newcommand{\todoUrgent}[2]{\todo[color=red!40, #1]{#2}}
\newcommand{\todoSansUrgent}[2]{\todo[color=yellow!40, #1]{#2}}
\extramargin
%% todonotes specific macros end!

%opening
\title{Reply to Referee 1}
\author{Vatsal Sanjay, Bin Zhang, Cunjing Lv, and Detlef Lohse}
\date{}
\begin{document}
	\maketitle

\textit{The authors describe a combined numerical and experimental study on the influence of Weber and Ohnesorge number on the peak forces (and their associated timing) associated with droplet impact and rebound on a non-wetting, rigid, planar surface. Scaling arguments are proposed throughout to help rationalize the trends observed in the data. This work represents a direct extension of work previously published by the same group (Zhang et al. PRL 2022) wherein they identified the possibility of two peaks in the impact force evolution associated with the initial impact and retraction stages. Overall, the manuscript is well written and easy to follow. However I do have some major and minor concerns that are described in what follows.}\\[2mm]

We thank the referee for carefully reading our manuscript and providing valuable feedback and suggestions. We have reviewed the referee's comments and made changes based on their suggestions. Below, we offer a point-to-point reply to each of the referee's comments and include the changes made in the manuscript. The referee's comments are in italics, and our replies are in plain black. Changes in the manuscript are highlighted in orange.

\begin{enumerate}
	\item \textit{Apart from Figure 2 (which appears to be the previously published data from Figure 1 in Zhang et al. (PRL 2022)), there is very little direct comparison between experiment and simulation. Now that the parameter space has been significantly extended from prior work, I would have expected similar direct force versus time comparisons and droplet shape profiles spanning the new range of parameters to validate the simulation. Comparisons similar to that in Figure 2 should be included throughout when the various parameter various regimes are introduced and discussed.}\\[0.5mm]

	Yes, it is correct that the earlier version of figure 2 summarized the results previously published in \citet{zhang2022impact}. To extend the comparison at different Ohnesorge numbers $Oh$, we have added two additional $F(t)$ curves in figure 2 (see figure~\ref{fig:summary}). Furthermore, throughout the manuscript, we present experimental data wherever available (see figures 3 and 7).

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{../Main/Figures/Figure1_summary_v5.pdf}
		\caption{\VS{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$. These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
			For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively. 
			The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $t_3 \approx 0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
			Six instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), (iv) $t = 3.93\,\si{\milli\second}$ ($\approx 0.85t_2$), (v) $t = 4.63\,\si{\milli\second}$ ($t_2$), and (vi) $t = 5.25\,\si{\milli\second}$ ($\approx 1.15t_2$). 
			We stress the excellent agreement between experiments and simulations without any free parameters. The insets show representative snapshots at specific time instants overlaid with the drop boundaries from simulations in orange, also revealing good agreement. 
			The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity. The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.}}
		\label{fig:summary}
	\end{figure}

	For the high Ohnesorge number regime ($Oh \gg 1$) discussed in Figure 5, we, unfortunately, do not have corresponding experimental data as we used water-glycerol mixtures in the experiments, which can at most be 1000 times (100\% by weight of glycerine) more viscous than water. However, to provide an additional comparison, we have added a new panel (Figure 5c, see figure~\ref{fig:F1Anatomy_2}) comparing our results with those from \citet{Gordillo2018, cheng2021drop}. This comparison focuses on the relationship between the first peak force $F_1$ and the impact Reynolds number $Re = \rho_dV_0D_0/\eta_d$.

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{../main/Figures/ForceTimeVersusOhnesorge.pdf}
		\caption{\blue{Anatomy of the first impact force peak amplitude for viscous impacts from our numerical simulations: the $Oh$ dependence of  (a) the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ and (b) the time $t_1$ to reach the first force peak amplitude normalized by inertial timescale $\tau_\rho = D_0/V_0$}. \VS{(c) The $Re$ dependence of the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ as compared to the (implicit) theoretical calculation of \citet{Gordillo2018}.} \blue{The black line corresponds to the scaling relationship described in \S~3.2. The Weber number is color-coded.}}
		\label{fig:F1Anatomy_2}
	\end{figure}

	\item \textit{Error bars (both horizontal and vertical) for the experiments should be included throughout whenever experimental data is presented. If smaller than the data points, this should be noted. Furthermore, a discussion of any error analysis is completely lacking. For the error bars that are included, do these account for multiple trials? Parameter uncertainties? Measurement uncertainties? Such a discussion, with errors quantified (and methods used to assess the errors), must be included. In particular, the resolution of the force sensor (reported as 0.5 mN) should be indicated when force measurements are presented, including in Figure 2.}\\[0.5mm]

	Thank you for highlighting the importance of error analysis and the need for a more comprehensive discussion of error quantification in our manuscript. We appreciate your suggestions. Indeed, we have included the error bars wherever experimental data are reported. For the cases where the error bars are not visible, the error bar is smaller than the data points. For more details regarding the error quantification, we refer the readers to the supplementary material of \citet{zhang2022impact}. We have added this clarification in the experimental method section:

	\S~\red{2.1:}\\
	\VS{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size. We refer the readers to the supplementary material of \citet{zhang2022impact} for further details of the experimental setup.}\\[0.5mm]

	We have also added a dashed gray horizontal line in figure 2 to mark the resolution of the force sensor.

	\item \textit{Furthermore, the dimensional parameters of the experiments performed need to somehow be specified or indicated. The authors mention a range of droplet sizes, viscosities, and impact speeds, and so We and Oh do not uniquely defined the experimental realizations reported. This specificity is critical for repeatability and future comparisons that might be made.}\\[0.5mm]

	Thank you for raising this important point about the need to specify the dimensional parameters of the experiments. We appreciate the emphasis on the importance of this information for repeatability and future comparisons. We vary the impact velocity by changing the release height of the drops above the substrate and change the viscosity by using different water-glycerol mixtures. Such a protocol allows us to vary the viscosity by almost two orders of magnitude, yet maintaining a fairly constant density and surface tension. Consequently, the Weber number $We$ can be interpreted as a dimensionless impact velocity and the Ohnesorge number $Oh$ as a dimensionless viscosity. We have modified the text to clarify the experimental protocol and provide more details on the dimensional parameters:

	\S~\red{2.1:}\\
	\VS{The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}. Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}. The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle. Throughout this work, we use drops with diameter $2.54 \pm 0.02\,\si{\milli\meter}$ unless otherwise stated. Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~1.2). The Weber number ($We$, see~1.1) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate. Lastly, we keep the Bond number ($Bo$, see~1.3) fixed at 1 throughout the manuscript. In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity. Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia.}

	This expanded description provides several key pieces of information:
	\begin{enumerate}
		\item The range of viscosities ($1,\si{\milli\pascal}\si{\second}$ to $80.2,\si{\milli\pascal}\si{\second}$) achieved using water-glycerol mixtures.
		\item The relatively constant surface tension ($61,\si{\milli\newton}/\si{\meter}$) and density ($1000,\si{\kilo\gram}/\si{\cubic\meter}$) of these mixtures.
		\item The range of drop diameters ($2.05,\si{\milli\meter}$ to $2.76,\si{\milli\meter}$) and the typical diameter used ($2.54 \pm 0.02,\si{\milli\meter}$).
		\item The range of impact velocities ($0.38,\si{\meter}/\si{\second}$ to $2.96,\si{\meter}/\si{\second}$) achieved by varying the release height.
	\end{enumerate}

	We also clarify that the Ohnesorge number ($Oh$) is uniquely determined by the drop viscosity, while the Weber number ($We$) is set by the impact velocity.

	By providing these details, we aim to ensure that our experiments can be readily reproduced and that future comparisons can be made with a clear understanding of the dimensional parameters involved. We believe this additional information significantly enhances the repeatability and usefulness of our work.

	We have also modified the caption of figure 2 (see figure~\ref{fig:summary}) to clarify the drop impact parameters.

	\item \textit{Is gravity included in the simulations? If so, the Bond number in simulations should be specified, as We and Oh alone do not uniquely define the non-dimensional problem. The authors show that droplet rebound can be affected by finite Bond number effects in their very recent prior work (Sanjay et al. JFM 2023), so at least some discussion on the role of gravity should be included.}\\[0.5mm]

	Thank you for raising this important question about the role of gravity in our simulations and the need to specify the Bond number. In deed, in \citet{sanjay_chantelot_lohse_2023}, we highlight the potential influence of finite Bond number on the bouncing--no-bouncing transition on a non-wetting surface.

	To address your concerns, we have made the following revisions to the manuscript:

	\begin{enumerate}
		\item We have clarified that gravity is indeed included in our simulations and that the Bond number (based on the drop's diameter) $Bo = \rho_dgD_0^2/\gamma$ is fixed at 1 throughout the study. This information has been added to the manuscript as follows:

		\S~\red{2.1:}\\
		\VS{Throughout the manuscript, we keep the Bond number ($Bo$, see~(1.3)) fixed at 1 in our simulations, which include the effects of gravity.}

		\item We have updated Figure 10 to indicate that the critical $Oh$ to suppress bouncing is 0.53 for the chosen $Bo$ of 1. Note that in \citet{sanjay_chantelot_lohse_2023}, we use the radius $R_0 = D_0/2$ as the length scale to get $Oh_c + Bo_c \approx 1$.

		\item We have introduced the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$, which compares inertia with gravity. We clarify that throughout the manuscript, $Fr > 1$, indicating that the role of gravity is sub-dominant compared to inertia. This discussion has been added as follows:

		\S~\red{2.1:}\\
		\VS{In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$, which compares inertia with gravity. Throughout this manuscript, $Fr > 1$, indicating that the role of gravity is sub-dominant compared to inertia.}
	\end{enumerate}

	\item \textit{The title needs to be rewritten. The authors demonstrate that capillarity also plays a crucial role, and seem to ignore gravity throughout the present work anyways (i.e. gravity doesn’t dictate impact forces here, because it is assumed). Furthermore, the title does not specify the nature of the substrate, which is a specific case. I would suggest something along the lines of ``Impact forces of droplets on non-wetting planar surfaces" or similar.}

	We agree with the reviewer that the title was misleading. Of course, all three: inertia, capillarity, and viscosity, play a role. Indeed, we have studied the role of inertial and capillarity in \citet{zhang2022impact}. We have now changed the title of the paper to:

	\VS{The role of viscosity on drop impact forces}

	\item \textit{What are the receding and advancing contact angles for the experimental surfaces used? The experimental substrate is not truly non-wetting (in contrast to the simulation), so this should be clearly described.}\\[0.5mm]

	Yes, the reviewer is correct. The substrate is not truly non-wetting in the experiments. We have added this in the revised manuscript along with the advancing and the receding contact angles.

	\S~\red{2.1:}\\
	 \VS{For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}. On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}.}

	\item \textit{In the experiments, are the droplets arriving at the surface without residual oscillation? Particular for the small We, small Oh cases, I would expect this is not the case. This should be discussed.}

	Thank you for raising this important point about the potential influence of residual oscillations in the drop as they arrive at the surface, particularly for cases with small Weber and Ohnesorge numbers. We agree that this aspect of the experimental setup deserves discussion in the manuscript.
	To address this concern, we have added the following text to the manuscript:

	\S~\red{2.2:}\\
	\VS{At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. It is important to note that the drop may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate. These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers. The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}. However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}

	By acknowledging the possibility of residual oscillations and their potential influence on the impact dynamics, we aim to provide a more complete and transparent description of the experimental setup. We also highlight that the error bars in the experimental data, which are derived from repeated trials, likely account for some of the variability introduced by these shape variations.

	The inclusion of this discussion helps readers to better understand the limitations and uncertainties inherent in the experimental setup, and it provides important context for interpreting the results. We have also added references to relevant literature \citep{thoraval-2013-jfm, yun2017bouncing} that further explore the influence of drop shape on impact dynamics.

	\item \textit{How are the density, viscosity, and surface tension of the various water-glycerol mixtures determined? These also need to be reported.}

	We use the protocol described in \citet{cheng2008formula, volk2018density}. We have added a new table~\ref{tab:table00} with all the material properties (density, viscosity, and surface tension) of the water-glycerol mixtures used in this work.

	\begin{table}
		\begin{center}
			\def~{\hphantom{0}}
			\begin{tabular}{lccc}
				glycerol & $\rho_d$ & $\eta_d$  & $\gamma$\\
				(wt \%) &(kg/m$^{3}$) &(mPa.s)& (mN/m)\\[3pt]
				0 & 1000 & 1 & 72 \\
				50 & 1124 & 5 & 61 \\
				63 & 1158 & 10 & 61 \\
				74 & 1188 & 25.3 & 61 \\
				80 & 1200 & 45.4 & 61 \\
				85 & 1220 & 80.2 & 61 \\
			\end{tabular}
			\caption{\VS{Properties of the water-glycerol mixtures used in the experiments. $\rho_d$ and $\eta_d$ are the density and viscosity of the drop, respectively and $\gamma$ denotes the liquid-air surface tension coefficient. These properties are calculated using the protocol provided in \citet{cheng2008formula, volk2018density}.}}
			\label{tab:table00}
		\end{center}
	\end{table}

	\item \textit{Some details on the numerical implementation are left out. In particular, the computational domain size and initial conditions should be specified.}

	We have added these details in the revised manuscript:

	\S~\red{2.2:}\\
	\VS{The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case). At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. It is important to note that the drops may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate. These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers. The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}. However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}

	\item \textit{The authors ignore the role of the air film in the dynamics on the grounds that the air-based Ohnesorge number is small, however the air gap can become extremely small and thus it is not clear that the drop diameter is the relevant length scale in assessing the viscous forces in the air. Furthermore, this is contrast to prior work on non-wetting impacts (such as Kolinski et al. (EPL 2014)) that argues viscous effects in the thin gas layer can play a role in the liquid dynamics. This should be discussed.}

	Thank you for raising this important point about the role of the air film in the drop impact dynamics. We appreciate the opportunity to discuss this aspect further and clarify its relevance to our work.

	We acknowledge that our treatment of the air film, based on the small air-based Ohnesorge number, may only partially capture the complexity of the viscous forces in the thin gas layer. The reviewer rightly points out that the drop diameter is not the most appropriate length scale for assessing these forces, especially when the air gap is extremely thin. This approach contrasts with some prior work on non-wetting impacts, such as \citet{kolinski-2014-epl}, which argues for the significance of viscous effects in the thin gas layer on the liquid dynamics. In fact, the air layer has two important contributions:

	\begin{enumerate}
		\item It prevents the contact between the falling drop and the solid surface. 
		\item It might lead to dissipation owing to the large velocity gradients. 
	\end{enumerate}

	To understand the relative importance of these two effects, we have recently conducted direct numerical simulations and compared the results with experiments on various surfaces, including superhydrophobic surfaces \citep{sanjay_chantelot_lohse_2023}, atomically smooth viscous films \citep{sanjay2023drop}, and even other drops \citep{ramirez2020lifting}. Our findings suggest that, for the macroscopic observables, the primary contribution of the air film is to prevent contact between the drop and the substrate. In contrast, the dissipation inside the air film itself does not play a significant role in the parameter range we study. This feature is particularly notable for large Weber numbers ($We$) where substrate-independent bouncing ceases.
	Despite the high-velocity gradients in the air film, we propose that the dissipation inside the drop dominates in all the cases we have examined. The small volume and low air viscosity limit the dissipation it can create, in contrast to the findings of previous works like \citet{kolinski-2014-epl}. However, we also acknowledge the complexity of modeling the air film, especially considering the extremely small Knudsen numbers involved. In such cases, a hybrid method \citep{chubynsky-2020-prl, sprittles2024gas} might provide a more accurate description.

	We have added a discussion of these points in the revised manuscript to provide a more comprehensive discussion of the role of the air film in drop impact dynamics and to address the apparent contrast with prior work. We thank the reviewer for highlighting this important aspect and helping us improve the clarity and completeness of our manuscript.

	\S~\red{2.2:}\\
	\VS{To ensure a perfectly non-wetting surface, we impose a thin air layer (minimum thickness $\sim \Delta/2$) between the drop and the substrate. This air layer prevents direct contact between the liquid and solid \citep{kolinski-2014-epl, sprittles2024gas}, effectively mimicking a perfectly non-wetting surface. The presence of this air layer is crucial for capturing the dynamics of drop impact on superhydrophobic surfaces, as it allows for the formation of an air cushion that can significantly affect the spreading and rebound behavior of the drop \citep{ramirez2020lifting, sanjay_chantelot_lohse_2023}.
	While this approach does not fully resolve the microscopic dynamics within the air layer itself, such as the high-velocity gradients and viscous dissipation inside the gas film once it thins below a critical size ($\sim 10\Delta$), it has been shown to accurately capture the macroscopic behavior of drop impact in the parameter range of interest \citep{ramirez2020lifting, sanjay2023drop, alventosa2023inertio, garcia2024skating}. We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, vatsal_sanjay_2023_7598181, zhang2022impact} for details on the numerical framework.}

	\item \textit{Figure 5 does not include any experimental data. This should be explained. Perhaps the high Oh regime is not accessible with the droplet sizes and fluids used?}

	Thank you for raising this important point about the experimental data in Figure 5. We appreciate your suggestion to consider using other liquids, such as silicone oil, to probe a wider range of viscosity and Ohnesorge number ($Oh$).
	In our experiments, we focused on using water-glycerol mixtures, which allowed us to explore two orders of magnitude in $Oh$. While silicone oil could indeed provide access to a broader viscosity range, it would require the use of superamphiphobic surfaces \citep{deng2012candle, ramirez2020lifting}. We have added a remark in the revised manuscript to acknowledge this limitation and to suggest potential future directions for exploring higher $Oh$ regimes using alternative liquid-surface combinations. This will help provide context for our experimental choices and highlight opportunities for further research.

	\S~\red{2.1:}\\
	\VS{Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.}

	\item \textit{Figure 5(a) partially confirms the $\sqrt{Oh}$ proposed, but suggests a notable $We$ dependence on the prefactor that is absent from the scaling argument. This should be analyzed and discussed.}

	Thank you for highlighting the $We$ dependence on the prefactor in Figure 5(a). We agree that this warrants further analysis and discussion in the manuscript.
	In the revised version, we have addressed this by examining the function $F_1(Re)$, where $Re = V_0D_0/\nu_d$ is the impact Reynolds number. This analysis focused on the low $Re$ regime, has allowed us to describe the $We$ dependence on the prefactor more effectively.
	We added a new Figure 5(c) to the manuscript to illustrate this relationship. However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude.
	By incorporating this additional analysis and discussion, along with the new Figure 5(c), we aim to provide a more comprehensive understanding of the factors influencing the scaling relationship.

	\S~\red{3.2:}\\
	\VS{Figure~5 further shows that these scaling laws are weakly dependent on the Weber number, as viscous dissipation consumes the entire initial kinetic energy of the impacting drop (figure~6). Once again, we stress that using the water-glycerol mixtures limits the range of $Oh$ that we can probe experimentally. 
	We further note that the first peak is robust and does not depend on the wettability of the substrate. Consequently, to compare with the existing data such as those in \citet{cheng2021drop} with different liquids to cover a wider range of liquid viscosities and to account for the apparent $We$-dependence, we plot $F_1$ compensated with $F_\rho$ against the impact Reynolds number $Re \equiv \frac{\sqrt{We}}{Oh} = V_0D_0/\nu_d$. 
	For the low $Re$ regime, such a plot allows us to describe the $We$ dependence on the prefactor more effectively, as illustrated in figure~5(c). However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude. This lack of a pure scaling behavior demonstrates how the interplay between kinetic energy and viscous dissipation within the drop dictates the functional dependence of the maximum impact force on $Oh$.}

	\item \textit{For the large $Oh$ impacts (section 3.2) the authors use the Rayleigh oscillation time as the timescale for impact. This theoretical timescale is derived for $Oh \ll 1$ droplet oscillations, and so is not clearly justified here. If $t_{\text{max}}$ is indeed independent of $Oh$ for the cases considered here, the authors should demonstrate this with their data. Furthermore, a physical interpretation of the overall trends predicted by the scaling arguments (3.16) and (3.17) should be provided.}

	Thank you for raising this important point about the use of the Rayleigh oscillation time as the timescale for impact in the large Ohnesorge number ($Oh$) regime. We appreciate the opportunity to clarify our approach and present the modifications made to the theoretical model based on your critique and our recent work \citep{sanjay2024PRL}.

	In the revised version of the manuscript, we have made two major changes to the model:

	\begin{enumerate}
		\item[$\bullet$] We now integrate until $\tau_\rho$ instead of $t_{\text{max}}$, as you correctly pointed out. The first peak appears within a fraction of $t \sim \tau_\rho$ (see Figures 3 and 4).
		\item[$\bullet$] For the viscous regime, we propose that the entire initial kinetic energy is lost from $t = 0$ until $t = \tau_\rho = D_0/V_0$. The viscous dissipation during this time frame dictates the drop impact force.
	\end{enumerate}

	With these modifications, the leading order of the model now gives $F_1 \sim 1/\sqrt{Re}$ (see Figure 5c of the revised manuscript or Figure~\ref{fig:F1Anatomy_2} of this reply). This result is consistent with the findings of \citet{Gordillo2018}. In fact, there is only a minor discrepancy between the theoretical results of \citet{Gordillo2018, cheng2021drop} and our direct numerical simulation data.

	However, we still recommend the need for a predictive model to obtain the first force peak amplitude $F_1$ based on the control parameters $We$ and $Oh$. We address this question in our recent work \citep{sanjay2024PRL}, where we use global energy balances to unify the scaling of drop impact forces in different parts of the parameter space. We have also added a brief discussion of this in the revised manuscript.

	Regarding the physical interpretation of the overall trends predicted by the scaling arguments (3.16) and (3.17), we have expanded on this in the revised manuscript. The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces. The trends predicted by these scaling arguments provide insights into the key physical mechanisms governing the drop impact dynamics in different regimes.

	\S~\red{5:}\\
	\VS{Although, the implicit theoretical model summarized in \citet{cheng2021drop} describes most of data in figure~5, we stress the importance of having a predictive model to determine $F_1$ for given $We$ and $Oh$ \citep{sanjay2024PRL}.}

	\S~\red{3.2:}\\
	\blue{To systematically elucidate these scaling behaviors in the limit of small $Re$, we need to find the typical scales for the rate of change of kinetic energy and that of the rate of viscous dissipation for the drop impact system. First, we can readily define an average rate of viscous dissipation per unit mass as}

	\blue{\begin{align}
		\bar{\varepsilon} \sim \frac{1}{\tau_\rho}\frac{1}{D_0^3}\int_0^{\tau_\rho}\int_\Omega\nu_d\left(\boldsymbol{\mathcal{D}:\mathcal{D}}\right)d\Omega dt,
	\end{align}}

	\noindent \blue{where $\nu_d$ is the kinematic viscosity of the drop and $d\Omega$ is the volume element where dissipation occurs. Notice that $\bar{\varepsilon}$ has the dimensions of $V_0^3/D_0$, i.e., length squared over time cubed or velocity squared over time, as it should be for dissipation rate of energy per unit mass. We can estimate $\Omega = D_{\text{foot}}^2l_\nu$ (figure~6), where $D_{\text{foot}}$ is the drop's foot diameter in contact with the substrate and $l_\nu$ is the viscous boundary layer thickness.} \VS{This boundary layer marks the region of strong velocity gradients ($\sim V_0/l_\nu$) analogous to the \citet{mirels1955laminar} shockwave-induced boundary layer. For details, we refer the authors to \citet{schlichting2016boundary, Schroll2010, Philippi2016}. Consequently, the viscous dissipation rate scales as}

	\blue{\begin{align}\label{eq:dissipationScale}
		\bar{\varepsilon} \sim \frac{1}{\tau_\rho D_0^3}\int_0^{\tau_\rho}\nu_d \left(\frac{V_0}{l_\nu}\right)^2 D_{\text{foot}}^2l_\nu dt.
	\end{align}}

	\noindent \blue{To calculate $D_{\text{foot}}$, we assume that the drop maintains a spherical cap shape throughout the impact (figure~6). To calculate the distance the drop would have traveled if there were no substrate, we use the relation $d \sim V_0t$. Simple geometric arguments allow us to determine the relation between the foot diameter and this distance, $D_{\text{foot}} \sim \sqrt{D_0d}$ \citep{lesser1981analytic, mandre2009precursors,  zheng2021air, bilotto2023fluid, bertin2023similarity}.} \VS{Interestingly, this scaling behavior is similar to the inertial limit \citep{wagner1932stoss, Bouwhuis2012, Philippi2016, gordillo2019theory} as discussed by \citet{langley2017impact, bilotto2023fluid}.} \blue{Furthermore, the viscous boundary layer $l_\nu$ can be approximated using $\sqrt{\nu_d t}$ \citep{mirels1955laminar, Eggers2010, Philippi2016}. Filling these in \eqref{eq:dissipationScale}, we get}

	\blue{\begin{align}	
		\bar{\varepsilon} \sim \frac{1}{\tau_\rho D_0^2}\int_0^{\tau_\rho}\sqrt{\nu_d} V_0^3 \sqrt{t} dt,
	\end{align}}

	\noindent \blue{which on integration gives}

	\VS{\begin{align}\label{eq:eps0Final}
		\bar{\varepsilon} \sim \sqrt{\nu_d \tau_\rho}V_0^3/D_0^2, 
	\end{align}}

	\noindent \VS{where $\tau_\rho$ is the inertial time scale. Here, we assume that for highly viscous drops, all energy is dissipated within a fraction of $\tau_\rho$. Filling in \eqref{eq:eps0Final} and normalizing $\bar{\varepsilon}$ with the inertial scales $V_0^3/D_0$,}

	\VS{\begin{align}\label{eq:DissipationScale}
		\frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \sqrt{\frac{\nu_d\tau_\rho}{D_0^2}} = \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}.
	\end{align}}

	\noindent \blue{Next, the kinetic energy of the falling drop is given by}

	\blue{\begin{align}\label{eq:KEdissipation}
		\dot{K}(t) \equiv \frac{dK(t)}{dt} \sim \rho_dD_0^3\bar{\varepsilon},\quad\text{where } K(t) = \frac{1}{2}m\left(V(t)\right)^2,
	\end{align}}

	\noindent \blue{and $V(t)$ is the drop's center of mass velocity. The left-hand side of \eqref{eq:KEdissipation} can be written as}

	\blue{\begin{align}\label{eq:KE-powerTime}
		\dot{K}(t) = mV(t)\frac{dV(t)}{dt} = F(t)V(t).
	\end{align}}

	\noindent \blue{In equation~\eqref{eq:KE-powerTime}, $F(t)$ and $V(t)$ scale with the first impact force peak amplitude $F_1$ and the impact velocity $V_0$, respectively, giving the typical scale of the rate of change of kinetic energy as}

	\blue{\begin{align}\label{eq:KE-power}
		\dot{K}^* \sim F_1V_0.
	\end{align}}

	\noindent \blue{We stress that \eqref{eq:KE-power} states that the rate of change of kinetic energy is equal to the power of the normal reaction force, an observation already made by \citet{wagner1932stoss} and \citet{Philippi2016} in the context of impact problems. Lastly, at large $Oh$, viscous dissipation enervates kinetic energy completely giving (figure~6c, also see:  \citet{Philippi2016} and \citet{ Wildeman2016}),}

	\blue{\begin{align}\label{eq:force-Dissipation}
		\dot{K}^* \sim F_1V_0 \sim \rho_dD_0^3\bar{\varepsilon}
	\end{align}}

	\noindent \blue{Additionally, we use the inertial scales to non-dimensionalize  \eqref{eq:force-Dissipation} and fill in \eqref{eq:DissipationScale}, giving}

	\VS{\begin{align}
		\frac{F}{F_\rho} \sim \frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}
	\end{align}}

	\noindent \blue{and using $F_1t_1 \sim \rho_dV_0D_0^3 = F_\rho\tau_\rho$,}

	\VS{\begin{align}
		\frac{t_1}{\tau_\rho} \sim \left(\frac{\sqrt{We}}{Oh}\right)^{1/2}.
	\end{align}}

	\VS{In summary, we use energy and momentum invariance to elucidate the parameter dependencies of the impact force as illustrated in figure~5. The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces. As the dimensionless viscosity of impacting drops increases, the lack of surface deformation increases the normal reaction force (3.16). Further, the invariance of incoming drop momentum implies that this increase in normal reaction force occurs on a shorter timescale (3.17).}

	\item \textit{Access to the code is greatly appreciated. However, I would suggest a permanent identifier be assigned to the version applied in the present study. This can be accomplished with Zenodo (integrated with Github), for instance.}

	Thanks a lot for the idea of using Zenodo. Interestingly, the code is already there. We have added it as a citation in the revised manuscript \citep{vatsal_sanjay_2023_7598181}.

	\item \textit{In the introduction, the authors describe water as a ``low-viscosity" liquid. In comparison to what? As the authors note, viscous effects in the problem are best described by $Oh$ which includes other dimensional parameters in addition to viscosity. Similarly, in the end of section 4, the authors describe their previous work demonstrating a critical viscosity whereas it should be a critical $Oh$ (or indeed a critical viscosity when all other parameters fixed).}\\[0.5mm]

	We have changed the abstract to read:

	\VS{The maximum spreading diameter $F_1$ and the time $t_1$ to reach it depend on inertial timescales for low viscosity liquids, remaining nearly constant for viscosities up to 100 times that of water. For high viscosity liquids, we balance the rate of change in kinetic energy with viscous dissipation to obtain new scaling laws: $F_1/F_\rho \sim \sqrt{Oh}$ and $t_1/\tau_\rho \sim 1/\sqrt{Oh}$,
	%For liquids like water, the amplitude $F_1$ and the time $t_1$ to reach it are governed by inertial timescales, insensitive to viscosity variations up to 100-fold. 
	%For liquids with viscosity much larger than that of water, beyond this viscosity-independent regime, we balance the rate of change in kinetic energy and the rate of viscous dissipation to obtain the scaling laws: $F_1 \sim F_\rho\sqrt{Oh}$ and $t_1 \sim \tau_\rho/\sqrt{Oh}$
	where $F_\rho$ and $\tau_\rho$ are the inertial force and time scales, respectively, which are consistent with our data.}\\[0.5mm]

	We have also changed critical viscosity to critical $Oh$ as rightly pointed out by the reviewer.

	\S~\red{3.2:}\\
	\blue{Recently, \citet{Jha2020, sanjay_chantelot_lohse_2023} showed that there} \VS{exists a critical $Oh$, two orders of magnitude higher than that of a $2\si{\milli\meter}$ diameter water drop}, \blue{beyond which drops do not bounce either, irrespective of their impact velocity.}
\end{enumerate}

\textit{Overall, the manuscript provides valuable new data, interesting and important conclusions, and successfully extends their prior work in the area to consider a more complete parameter space. It will be of value to the droplets community and thus deserves to be published once the above concerns are addressed in detail.}\\[0.5mm]

We thank the reviewer for the valuable feedback and hope that the revised manuscript has addressed all the concerns.

\printbibliography[title=References]
\end{document}

### 2024-06-08 Rebuttal/Response to Reviewer 2.tex
Initial commit

--- 2024-06-08 Rebuttal/Response to Reviewer 1.tex
@@
 %opening
-\title{Reply to Referee 1}
+\title{Reply to Referee 2}
 \author{Vatsal Sanjay, Bin Zhang, Cunjing Lv, and Detlef Lohse}
@@
 \begin{document}
+
 \maketitle
 
-\textit{The authors describe a combined numerical and experimental study on the influence of Weber and Ohnesorge number on the peak forces (and their associated timing) associated with droplet impact and rebound on a non-wetting, rigid, planar surface.
-Scaling arguments are proposed throughout to help rationalize the trends observed in the data.
-This work represents a direct extension of work previously published by the same group (Zhang et al.
-PRL 2022) wherein they identified the possibility of two peaks in the impact force evolution associated with the initial impact and retraction stages.
-Overall, the manuscript is well written and easy to follow.
-However I do have some major and minor concerns that are described in what follows.}\\[2mm]
+\textit{The manuscript ``Inertia \& viscosity dictate drop impact forces," by Sanjay and coauthors, reports experimental and numerical evidence of drop impact under a wide range of conditions, covering cases in which surface tension, viscosity, or inertia become dominant.
+Their main focus is understanding the laws that govern the primary and secondary peak of force signals, $F_1$ and $F_2$, and the times at which they occur, $t_1$ and $t_2$.
+The authors provide physical arguments that elucidate the data dependency on two dimensionless control parameters, the Weber ($We$) and the Ohnesorge ($Oh$) number, establishing general scaling laws.
+The physics of several limiting cases is also described in detail, fulfilling a broad picture of the studied quantities in the space of parameters.}
+
+\textit{This work addresses a profound and relevant question regarding drop impact, which has implications for many applications.
+To improve our understanding of the involved physical quantities, the authors perform and report several new experiments and simulations, extending the range of parameters of gathered data.
+Accordingly, the manuscript presents a regime map for the force peaks, constituting its main contribution.
+Thus, The goal is well-aimed, and evidence and theory support the results well.
+However, I still have some concerns that I include in the attached report, which the authors should address to assert and clarify several claims in the manuscript.}
+
+\textit{The manuscript is well-structured, easy to understand, and phrased in excellent English.
+Figures are not only helpful but also beautiful.
+The authors disclose every necessary detail to understand the experiments and numerical simulations and how they complement.
+Also, the literature on this problem cited in the manuscript is comprehensive.}
+
+\textit{In summary, this manuscript that studies the drop-impact force peaks dependency on Weber and Ohnesorge numbers provides new and relevant data and contributes with a necessary regime map on each of the quantities examined and in a broader range of the dimensionless number under study.
+I will be eager to recommend its publication in the Journal of Fluid Mechanics after the authors solve the points I raised in the attached report.}\\[2mm]
 
@@
 \begin{enumerate}
-	\item \textit{Apart from Figure 2 (which appears to be the previously published data from Figure 1 in Zhang et al.
-(PRL 2022)), there is very little direct comparison between experiment and simulation.
-Now that the parameter space has been significantly extended from prior work, I would have expected similar direct force versus time comparisons and droplet shape profiles spanning the new range of parameters to validate the simulation.
-Comparisons similar to that in Figure 2 should be included throughout when the various parameter various regimes are introduced and discussed.}\\[0.5mm]
+	\item \textit{Line1: The title is misleading.
+As far as I understand,both $F_1$ and $F_2$, and $\tau_1$ and $\tau_2$, depend under some regimes on surface tension $\gamma$, but the title excludes surface tension as a relevant parameter in drop impact forces.
+Authors could explain this better or choose a title that reflects all the quantities under study.}
 
-	Yes, it is correct that the earlier version of figure 2 summarized the results previously published in \citet{zhang2022impact}.
+	We agree with the reviewer that the title was misleading.
+Of course, all three: inertia, capillarity, and viscosity, play a role.
+Indeed, we have studied the role of inertial and capillarity in \citet{zhang2022impact}.
+We have now changed the title of the paper to:
+
+	\VS{The role of viscosity on drop impact forces}
+
+	\item \textit{Figure 2: Although there are several pressure and velocity maps, etc., to characterize the different regimes throughout the article, there is only a single force signal (figure 2).
+Would the article benefit from including force signals for at least limiting cases of the dimensionless parameters?
+Force signal, the easier way to experimentally characterize the phenomenon, should provide a simple signature of the regime at which the drop impact occurs.}
+
+	 We thank the reviewer for this remark.
 To extend the comparison at different Ohnesorge numbers $Oh$, we have added two additional $F(t)$ curves in figure 2 (see figure~\ref{fig:summary}).
@@
 
-	For the high Ohnesorge number regime ($Oh \gg 1$) discussed in Figure 5, we, unfortunately, do not have corresponding experimental data as we used water-glycerol mixtures in the experiments, which can at most be 1000 times (100\% by weight of glycerine) more viscous than water.
-However, to provide an additional comparison, we have added a new panel (Figure 5c, see figure~\ref{fig:F1Anatomy_2}) comparing our results with those from \citet{Gordillo2018, cheng2021drop}.
-This comparison focuses on the relationship between the first peak force $F_1$ and the impact Reynolds number $Re = \rho_dV_0D_0/\eta_d$.
-
 	 \begin{figure}
@@
 
-	\item \textit{Error bars (both horizontal and vertical) for the experiments should be included throughout whenever experimental data is presented.
-If smaller than the data points, this should be noted.
-Furthermore, a discussion of any error analysis is completely lacking.
-For the error bars that are included, do these account for multiple trials?
-Parameter uncertainties?
-Measurement uncertainties?
-Such a discussion, with errors quantified (and methods used to assess the errors), must be included.
-In particular, the resolution of the force sensor (reported as 0.5 mN) should be indicated when force measurements are presented, including in Figure 2.}\\[0.5mm]
+	 \item 
+	 \begin{enumerate}
+	 	 \item \textit{Line111-114: Previous studies have considered much broader ranges of viscosities (c.f.
+Cheng 2022 and references therein) using other liquids and solutions.
+Readers could be addressed for completeness.}
+	 	\item \textit{Figure 5: The authors of several other studies have found that $F1/F_\rho$ depends solely on the Reynolds number (Re), collapsing curves in an extensive range of high Re numbers.
+Have the authors tried to remove the dependency on $\gamma$ (through Oh)?
+Since $Re \equiv \frac{\sqrt{We}}{Oh}$, I wonder if using it could collapse curves, at least in the low Oh limit.}
+	 \end{enumerate}
 
-	Thank you for highlighting the importance of error analysis and the need for a more comprehensive discussion of error quantification in our manuscript.
-We appreciate your suggestions.
-Indeed, we have included the error bars wherever experimental data are reported.
-For the cases where the error bars are not visible, the error bar is smaller than the data points.
-For more details regarding the error quantification, we refer the readers to the supplementary material of \citet{zhang2022impact}.
-We have added this clarification in the experimental method section:
+	Using water-glycerol mixtures allows us to probe two orders of magnitude in $Oh$ in the experiments.
+In the hindsight of finishing this project, we agree with the reviewer that using other liquids (such as silicone oil) will allow one to probe a wider range of viscosity  (and hence $Oh$).
+Of course, such liquids cannot be used with the superhydrophobic surfaces that we use in our work but would require superamphiphobic surfaces, such as the ones used in \citet{deng2012candle, ramirez2020lifting}.
+We have added this remark in the revised manuscript.
 
 	\S~\red{2.1:}\\
-	\VS{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
-We refer the readers to the supplementary material of \citet{zhang2022impact} for further details of the experimental setup.}\\[0.5mm]
+	\VS{We note that using other liquids like silicone oil could allow for a wider range of viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.}
 
-	We have also added a dashed gray horizontal line in figure 2 to mark the resolution of the force sensor.
-
-	\item \textit{Furthermore, the dimensional parameters of the experiments performed need to somehow be specified or indicated.
-The authors mention a range of droplet sizes, viscosities, and impact speeds, and so We and Oh do not uniquely defined the experimental realizations reported.
-This specificity is critical for repeatability and future comparisons that might be made.}\\[0.5mm]
-
-	Thank you for raising this important point about the need to specify the dimensional parameters of the experiments.
-We appreciate the emphasis on the importance of this information for repeatability and future comparisons.
-We vary the impact velocity by changing the release height of the drops above the substrate and change the viscosity by using different water-glycerol mixtures.
-Such a protocol allows us to vary the viscosity by almost two orders of magnitude, yet maintaining a fairly constant density and surface tension.
-Consequently, the Weber number $We$ can be interpreted as a dimensionless impact velocity and the Ohnesorge number $Oh$ as a dimensionless viscosity.
-We have modified the text to clarify the experimental protocol and provide more details on the dimensional parameters:
-
-	\S~\red{2.1:}\\
-	\VS{The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}.
-Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.
-The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle.
-Throughout this work, we use drops with diameter $2.54 \pm 0.02\,\si{\milli\meter}$ unless otherwise stated.
-Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~1.2).
-The Weber number ($We$, see~1.1) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate.
-Lastly, we keep the Bond number ($Bo$, see~1.3) fixed at 1 throughout the manuscript.
-In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
-Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia.}
-
-	This expanded description provides several key pieces of information:
-	\begin{enumerate}
-		\item The range of viscosities ($1,\si{\milli\pascal}\si{\second}$ to $80.2,\si{\milli\pascal}\si{\second}$) achieved using water-glycerol mixtures.
-		\item The relatively constant surface tension ($61,\si{\milli\newton}/\si{\meter}$) and density ($1000,\si{\kilo\gram}/\si{\cubic\meter}$) of these mixtures.
-		\item The range of drop diameters ($2.05,\si{\milli\meter}$ to $2.76,\si{\milli\meter}$) and the typical diameter used ($2.54 \pm 0.02,\si{\milli\meter}$).
-		\item The range of impact velocities ($0.38,\si{\meter}/\si{\second}$ to $2.96,\si{\meter}/\si{\second}$) achieved by varying the release height.
-	\end{enumerate}
-
-	We also clarify that the Ohnesorge number ($Oh$) is uniquely determined by the drop viscosity, while the Weber number ($We$) is set by the impact velocity.
-
-	By providing these details, we aim to ensure that our experiments can be readily reproduced and that future comparisons can be made with a clear understanding of the dimensional parameters involved.
-We believe this additional information significantly enhances the repeatability and usefulness of our work.
-
-	We have also modified the caption of figure 2 (see figure~\ref{fig:summary}) to clarify the drop impact parameters.
-
-	\item \textit{Is gravity included in the simulations?
-If so, the Bond number in simulations should be specified, as We and Oh alone do not uniquely define the non-dimensional problem.
-The authors show that droplet rebound can be affected by finite Bond number effects in their very recent prior work (Sanjay et al.
-JFM 2023), so at least some discussion on the role of gravity should be included.}\\[0.5mm]
-
-	Thank you for raising this important question about the role of gravity in our simulations and the need to specify the Bond number.
-In deed, in \citet{sanjay_chantelot_lohse_2023}, we highlight the potential influence of finite Bond number on the bouncing--no-bouncing transition on a non-wetting surface.
-
-	To address your concerns, we have made the following revisions to the manuscript:
-
-	\begin{enumerate}
-		\item We have clarified that gravity is indeed included in our simulations and that the Bond number (based on the drop's diameter) $Bo = \rho_dgD_0^2/\gamma$ is fixed at 1 throughout the study.
-This information has been added to the manuscript as follows:
-
-		\S~\red{2.1:}\\
-		\VS{Throughout the manuscript, we keep the Bond number ($Bo$, see~(1.3)) fixed at 1 in our simulations, which include the effects of gravity.}
-
-		\item We have updated Figure 10 to indicate that the critical $Oh$ to suppress bouncing is 0.53 for the chosen $Bo$ of 1.
-Note that in \citet{sanjay_chantelot_lohse_2023}, we use the radius $R_0 = D_0/2$ as the length scale to get $Oh_c + Bo_c \approx 1$.
-
-		\item We have introduced the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$, which compares inertia with gravity.
-We clarify that throughout the manuscript, $Fr > 1$, indicating that the role of gravity is sub-dominant compared to inertia.
-This discussion has been added as follows:
-
-		\S~\red{2.1:}\\
-		\VS{In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$, which compares inertia with gravity.
-Throughout this manuscript, $Fr > 1$, indicating that the role of gravity is sub-dominant compared to inertia.}
-	\end{enumerate}
-
-	\item \textit{The title needs to be rewritten.
-The authors demonstrate that capillarity also plays a crucial role, and seem to ignore gravity throughout the present work anyways (i.e.
-gravity doesn’t dictate impact forces here, because it is assumed).
-Furthermore, the title does not specify the nature of the substrate, which is a specific case.
-I would suggest something along the lines of ``Impact forces of droplets on non-wetting planar surfaces" or similar.}
-
-	We agree with the reviewer that the title was misleading.
-Of course, all three: inertia, capillarity, and viscosity, play a role.
-Indeed, we have studied the role of inertial and capillarity in \citet{zhang2022impact}.
-We have now changed the title of the paper to:
-
-	\VS{The role of viscosity on drop impact forces}
-
-	\item \textit{What are the receding and advancing contact angles for the experimental surfaces used?
-The experimental substrate is not truly non-wetting (in contrast to the simulation), so this should be clearly described.}\\[0.5mm]
-
-	Yes, the reviewer is correct. The substrate is not truly non-wetting in the experiments. We have added this in the revised manuscript along with the advancing and the receding contact angles.
-
-	\S~\red{2.1:}\\
-	 \VS{For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}.
-On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}.}
-
-	\item \textit{In the experiments, are the droplets arriving at the surface without residual oscillation?
-Particular for the small We, small Oh cases, I would expect this is not the case.
-This should be discussed.}
-
-	Thank you for raising this important point about the potential influence of residual oscillations in the drop as they arrive at the surface, particularly for cases with small Weber and Ohnesorge numbers.
-We agree that this aspect of the experimental setup deserves discussion in the manuscript.
-	To address this concern, we have added the following text to the manuscript:
-
-	\S~\red{2.2:}\\
-	\VS{At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$.
-It is important to note that the drop may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate.
-These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers.
-The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}.
-However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}
-
-	By acknowledging the possibility of residual oscillations and their potential influence on the impact dynamics, we aim to provide a more complete and transparent description of the experimental setup.
-We also highlight that the error bars in the experimental data, which are derived from repeated trials, likely account for some of the variability introduced by these shape variations.
-
-	The inclusion of this discussion helps readers to better understand the limitations and uncertainties inherent in the experimental setup, and it provides important context for interpreting the results.
-We have also added references to relevant literature \citep{thoraval-2013-jfm, yun2017bouncing} that further explore the influence of drop shape on impact dynamics.
-
-	\item \textit{How are the density, viscosity, and surface tension of the various water-glycerol mixtures determined? These also need to be reported.}
-
-	We use the protocol described in \citet{cheng2008formula, volk2018density}.
-We have added a new table~\ref{tab:table00} with all the material properties (density, viscosity, and surface tension) of the water-glycerol mixtures used in this work.
-
-	\begin{table}
-		\begin{center}
-			\def~{\hphantom{0}}
-			\begin{tabular}{lccc}
-				glycerol & $\rho_d$ & $\eta_d$  & $\gamma$\\
-				(wt \%) &(kg/m$^{3}$) &(mPa.s)& (mN/m)\\[3pt]
-				0 & 1000 & 1 & 72 \\
-				50 & 1124 & 5 & 61 \\
-				63 & 1158 & 10 & 61 \\
-				74 & 1188 & 25.3 & 61 \\
-				80 & 1200 & 45.4 & 61 \\
-				85 & 1220 & 80.2 & 61 \\
-			\end{tabular}
-			\caption{\VS{Properties of the water-glycerol mixtures used in the experiments.
-$\rho_d$ and $\eta_d$ are the density and viscosity of the drop, respectively and $\gamma$ denotes the liquid-air surface tension coefficient.
-These properties are calculated using the protocol provided in \citet{cheng2008formula, volk2018density}.}}
-			\label{tab:table00}
-		\end{center}
-	\end{table}
-
-	\item \textit{Some details on the numerical implementation are left out. In particular, the computational domain size and initial conditions should be specified.}
-
-	We have added these details in the revised manuscript:
-
-	\S~\red{2.2:}\\
-	\VS{The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case).
-At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$.
-It is important to note that the drops may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate.
-These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers.
-The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}.
-However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}
-
-	\item \textit{The authors ignore the role of the air film in the dynamics on the grounds that the air-based Ohnesorge number is small, however the air gap can become extremely small and thus it is not clear that the drop diameter is the relevant length scale in assessing the viscous forces in the air.
-Furthermore, this is contrast to prior work on non-wetting impacts (such as Kolinski et al.
-(EPL 2014)) that argues viscous effects in the thin gas layer can play a role in the liquid dynamics.
-This should be discussed.}
-
-	Thank you for raising this important point about the role of the air film in the drop impact dynamics.
-We appreciate the opportunity to discuss this aspect further and clarify its relevance to our work.
-
-	We acknowledge that our treatment of the air film, based on the small air-based Ohnesorge number, may only partially capture the complexity of the viscous forces in the thin gas layer.
-The reviewer rightly points out that the drop diameter is not the most appropriate length scale for assessing these forces, especially when the air gap is extremely thin.
-This approach contrasts with some prior work on non-wetting impacts, such as \citet{kolinski-2014-epl}, which argues for the significance of viscous effects in the thin gas layer on the liquid dynamics.
-In fact, the air layer has two important contributions:
-
-	\begin{enumerate}
-		\item It prevents the contact between the falling drop and the solid surface. 
-		\item It might lead to dissipation owing to the large velocity gradients. 
-	\end{enumerate}
-
-	To understand the relative importance of these two effects, we have recently conducted direct numerical simulations and compared the results with experiments on various surfaces, including superhydrophobic surfaces \citep{sanjay_chantelot_lohse_2023}, atomically smooth viscous films \citep{sanjay2023drop}, and even other drops \citep{ramirez2020lifting}.
-Our findings suggest that, for the macroscopic observables, the primary contribution of the air film is to prevent contact between the drop and the substrate.
-In contrast, the dissipation inside the air film itself does not play a significant role in the parameter range we study.
-This feature is particularly notable for large Weber numbers ($We$) where substrate-independent bouncing ceases.
-	Despite the high-velocity gradients in the air film, we propose that the dissipation inside the drop dominates in all the cases we have examined.
-The small volume and low air viscosity limit the dissipation it can create, in contrast to the findings of previous works like \citet{kolinski-2014-epl}.
-However, we also acknowledge the complexity of modeling the air film, especially considering the extremely small Knudsen numbers involved.
-In such cases, a hybrid method \citep{chubynsky-2020-prl, sprittles2024gas} might provide a more accurate description.
-
-	We have added a discussion of these points in the revised manuscript to provide a more comprehensive discussion of the role of the air film in drop impact dynamics and to address the apparent contrast with prior work.
-We thank the reviewer for highlighting this important aspect and helping us improve the clarity and completeness of our manuscript.
-
-	\S~\red{2.2:}\\
-	\VS{To ensure a perfectly non-wetting surface, we impose a thin air layer (minimum thickness $\sim \Delta/2$) between the drop and the substrate.
-This air layer prevents direct contact between the liquid and solid \citep{kolinski-2014-epl, sprittles2024gas}, effectively mimicking a perfectly non-wetting surface.
-The presence of this air layer is crucial for capturing the dynamics of drop impact on superhydrophobic surfaces, as it allows for the formation of an air cushion that can significantly affect the spreading and rebound behavior of the drop \citep{ramirez2020lifting, sanjay_chantelot_lohse_2023}.
-	While this approach does not fully resolve the microscopic dynamics within the air layer itself, such as the high-velocity gradients and viscous dissipation inside the gas film once it thins below a critical size ($\sim 10\Delta$), it has been shown to accurately capture the macroscopic behavior of drop impact in the parameter range of interest \citep{ramirez2020lifting, sanjay2023drop, alventosa2023inertio, garcia2024skating}.
-We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, vatsal_sanjay_2023_7598181, zhang2022impact} for details on the numerical framework.}
-
-	\item \textit{Figure 5 does not include any experimental data. This should be explained. Perhaps the high Oh regime is not accessible with the droplet sizes and fluids used?}
-
-	Thank you for raising this important point about the experimental data in Figure 5.
-We appreciate your suggestion to consider using other liquids, such as silicone oil, to probe a wider range of viscosity and Ohnesorge number ($Oh$).
-	In our experiments, we focused on using water-glycerol mixtures, which allowed us to explore two orders of magnitude in $Oh$.
-While silicone oil could indeed provide access to a broader viscosity range, it would require the use of superamphiphobic surfaces \citep{deng2012candle, ramirez2020lifting}.
-We have added a remark in the revised manuscript to acknowledge this limitation and to suggest potential future directions for exploring higher $Oh$ regimes using alternative liquid-surface combinations.
-This will help provide context for our experimental choices and highlight opportunities for further research.
-
-	\S~\red{2.1:}\\
-	\VS{Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.}
-
-	\item \textit{Figure 5(a) partially confirms the $\sqrt{Oh}$ proposed, but suggests a notable $We$ dependence on the prefactor that is absent from the scaling argument.
-This should be analyzed and discussed.}
-
-	Thank you for highlighting the $We$ dependence on the prefactor in Figure 5(a). We agree that this warrants further analysis and discussion in the manuscript.
-	In the revised version, we have addressed this by examining the function $F_1(Re)$, where $Re = V_0D_0/\nu_d$ is the impact Reynolds number.
-This analysis focused on the low $Re$ regime, has allowed us to describe the $We$ dependence on the prefactor more effectively.
-	We added a new Figure 5(c) to the manuscript to illustrate this relationship.
-However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude.
-	By incorporating this additional analysis and discussion, along with the new Figure 5(c), we aim to provide a more comprehensive understanding of the factors influencing the scaling relationship.
+	Unfortunately, we do not have experiments for $Oh \gg 1$ (figure 5).
+Nonetheless, we can compare our results with those in \citet{Gordillo2018, cheng2021drop} illustrating $F_1(Re)$, where $Re = V_0D_0/\nu_d$ is the impact Reynolds number.
+We were, indeed, able to collapse the data for low $Re$ (high $Oh$) limit.
+there is still some scatter at high $Re$ (low $Oh$) owing to the $We$ dependence of the impact force peak amplitude.
+We have added this as figure 5(c).
 
@@
 
-	\item \textit{For the large $Oh$ impacts (section 3.2) the authors use the Rayleigh oscillation time as the timescale for impact.
-This theoretical timescale is derived for $Oh \ll 1$ droplet oscillations, and so is not clearly justified here.
-If $t_{\text{max}}$ is indeed independent of $Oh$ for the cases considered here, the authors should demonstrate this with their data.
-Furthermore, a physical interpretation of the overall trends predicted by the scaling arguments (3.16) and (3.17) should be provided.}
+	\item
+	\begin{enumerate}
+		\item \textit{Eq.
+3.4: Following previous comments, results in the literature (e.g., Cheng 2022) include corrections as a function of Re in the low Re limit.
+Have the authors tried adding them to their expression to include both viscous and capillary contributions?}
+		\item \textit{Eq.~3.7: I am still not convinced of the validity of averaging over $t_{\text{max}}$ in Eq.~3.7.
+Many assumptions under consideration are valid only for the early impact and not through the spreading regime, which scales as $t_{\text{max}}$.
+In order to convince the readers, authors need to address this.}
+	\end{enumerate}
 
-	Thank you for raising this important point about the use of the Rayleigh oscillation time as the timescale for impact in the large Ohnesorge number ($Oh$) regime.
+	Thank you for raising this important point about the use of the $t_{\text{max}}$ as the timescale for impact in the large Ohnesorge number ($Oh$) regime.
 We appreciate the opportunity to clarify our approach and present the modifications made to the theoretical model based on your critique and our recent work \citep{sanjay2024PRL}.
@@
 We have also added a brief discussion of this in the revised manuscript.
-
-	Regarding the physical interpretation of the overall trends predicted by the scaling arguments (3.16) and (3.17), we have expanded on this in the revised manuscript.
-The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces.
-The trends predicted by these scaling arguments provide insights into the key physical mechanisms governing the drop impact dynamics in different regimes.
 
@@
 
-	\item \textit{Access to the code is greatly appreciated.
-However, I would suggest a permanent identifier be assigned to the version applied in the present study.
-This can be accomplished with Zenodo (integrated with Github), for instance.}
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.9\textwidth]{../main/Figures/RegimeMaps_v3.pdf}
+		\caption{\blue{Regime map in terms of the drop Ohnesorge number $Oh$ and the impact Weber number $We$ to summarize the two peaks in the impact force by showing the different regimes described in this work based on (a) the first peak in the impact force peak amplitude $F_1$ and (b) the second peak in the impact force peak amplitude $F_2$.
+Both peaks are normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$.
+These regime maps are constructed using $\sim 1500$ simulations in the range $0.001 \leq Oh \leq 100$ and $1 \leq We \leq 1000$.} \VS{The gray solid line in (a) and dashed line in (b) mark the inertial--viscous transition ($Re = 1$) and the bouncing--no-bouncing transition \citep[$Oh_c = 0.53$ for $Bo = 1$, see][]{sanjay_chantelot_lohse_2023}, respectively.}}
+		\label{fig:RegimeMaps}
+	\end{figure}
 
-	Thanks a lot for the idea of using Zenodo. Interestingly, the code is already there. We have added it as a citation in the revised manuscript \citep{vatsal_sanjay_2023_7598181}.
+	\item \textit{As a suggestion, I find that adding a Reynolds-number (tilted) axis, which nicely follows the slope of the central transition area of the white region of inset (a), will help readers to place previous experimental results in this regime map.
+It may be redundant, but still very helpful.}\\[0.1mm]
 
-	\item \textit{In the introduction, the authors describe water as a ``low-viscosity" liquid.
-In comparison to what?
-As the authors note, viscous effects in the problem are best described by $Oh$ which includes other dimensional parameters in addition to viscosity.
-Similarly, in the end of section 4, the authors describe their previous work demonstrating a critical viscosity whereas it should be a critical $Oh$ (or indeed a critical viscosity when all other parameters fixed).}\\[0.5mm]
+	We thank the review for this suggestion. We have modified figure 10 to include $Re = 1$ transition line (see figure~\ref{fig:RegimeMaps}).
 
-	We have changed the abstract to read:
-
-	\VS{The maximum spreading diameter $F_1$ and the time $t_1$ to reach it depend on inertial timescales for low viscosity liquids, remaining nearly constant for viscosities up to 100 times that of water.
-For high viscosity liquids, we balance the rate of change in kinetic energy with viscous dissipation to obtain new scaling laws: $F_1/F_\rho \sim \sqrt{Oh}$ and $t_1/\tau_\rho \sim 1/\sqrt{Oh}$,
-	%For liquids like water, the amplitude $F_1$ and the time $t_1$ to reach it are governed by inertial timescales, insensitive to viscosity variations up to 100-fold. 
-	%For liquids with viscosity much larger than that of water, beyond this viscosity-independent regime, we balance the rate of change in kinetic energy and the rate of viscous dissipation to obtain the scaling laws: $F_1 \sim F_\rho\sqrt{Oh}$ and $t_1 \sim \tau_\rho/\sqrt{Oh}$
-	where $F_\rho$ and $\tau_\rho$ are the inertial force and time scales, respectively, which are consistent with our data.}\\[0.5mm]
-
-	We have also changed critical viscosity to critical $Oh$ as rightly pointed out by the reviewer.
-
-	\S~\red{3.2:}\\
-	\blue{Recently, \citet{Jha2020, sanjay_chantelot_lohse_2023} showed that there} \VS{exists a critical $Oh$, two orders of magnitude higher than that of a $2\si{\milli\meter}$ diameter water drop}, \blue{beyond which drops do not bounce either, irrespective of their impact velocity.}
 \end{enumerate}
-
-\textit{Overall, the manuscript provides valuable new data, interesting and important conclusions, and successfully extends their prior work in the area to consider a more complete parameter space.
-It will be of value to the droplets community and thus deserves to be published once the above concerns are addressed in detail.}\\[0.5mm]
-
-We thank the reviewer for the valuable feedback and hope that the revised manuscript has addressed all the concerns.
 

### 2024-06-08 Rebuttal/Response to Reviewer 3.tex
Initial commit

--- 2024-06-08 Rebuttal/Response to Reviewer 2.tex
@@
 %opening
-\title{Reply to Referee 2}
+\title{Reply to Referee 3}
 \author{Vatsal Sanjay, Bin Zhang, Cunjing Lv, and Detlef Lohse}
@@
 \begin{document}
-
 	\maketitle
 
-\textit{The manuscript ``Inertia \& viscosity dictate drop impact forces," by Sanjay and coauthors, reports experimental and numerical evidence of drop impact under a wide range of conditions, covering cases in which surface tension, viscosity, or inertia become dominant.
-Their main focus is understanding the laws that govern the primary and secondary peak of force signals, $F_1$ and $F_2$, and the times at which they occur, $t_1$ and $t_2$.
-The authors provide physical arguments that elucidate the data dependency on two dimensionless control parameters, the Weber ($We$) and the Ohnesorge ($Oh$) number, establishing general scaling laws.
-The physics of several limiting cases is also described in detail, fulfilling a broad picture of the studied quantities in the space of parameters.}
-
-\textit{This work addresses a profound and relevant question regarding drop impact, which has implications for many applications.
-To improve our understanding of the involved physical quantities, the authors perform and report several new experiments and simulations, extending the range of parameters of gathered data.
-Accordingly, the manuscript presents a regime map for the force peaks, constituting its main contribution.
-Thus, The goal is well-aimed, and evidence and theory support the results well.
-However, I still have some concerns that I include in the attached report, which the authors should address to assert and clarify several claims in the manuscript.}
-
-\textit{The manuscript is well-structured, easy to understand, and phrased in excellent English.
-Figures are not only helpful but also beautiful.
-The authors disclose every necessary detail to understand the experiments and numerical simulations and how they complement.
-Also, the literature on this problem cited in the manuscript is comprehensive.}
-
-\textit{In summary, this manuscript that studies the drop-impact force peaks dependency on Weber and Ohnesorge numbers provides new and relevant data and contributes with a necessary regime map on each of the quantities examined and in a broader range of the dimensionless number under study.
-I will be eager to recommend its publication in the Journal of Fluid Mechanics after the authors solve the points I raised in the attached report.}\\[2mm]
+\textit{This manuscript is a sequel to a recent Phys.
+Rev.
+Lett.
+by the same authors investigating the force exerted by a drop impacting a superhydrophobic substrate.
+In the previous article, the existence of a second peak in the force signal was reported, and was attributed to the drop rebound/jet emission.}\\[2mm]
 
@@
 \begin{enumerate}
-	\item \textit{Line1: The title is misleading.
-As far as I understand,both $F_1$ and $F_2$, and $\tau_1$ and $\tau_2$, depend under some regimes on surface tension $\gamma$, but the title excludes surface tension as a relevant parameter in drop impact forces.
-Authors could explain this better or choose a title that reflects all the quantities under study.}
+	\item \textit{While I was enthusiastic about the original article, I find overall this submission to be incremental, and not worthy of publication in J.
+Fluid Mech.
+The first half of the manuscript (up to §3.1 included) is just a rehash of the previous article.}
 
-	We agree with the reviewer that the title was misleading.
-Of course, all three: inertia, capillarity, and viscosity, play a role.
-Indeed, we have studied the role of inertial and capillarity in \citet{zhang2022impact}.
-We have now changed the title of the paper to:
+	Thank you for your feedback on our manuscript.
+We appreciate your initial enthusiasm for our article.
+We would like to address your concerns regarding the incremental nature of this submission and highlight the novel aspects of our current work.
 
-	\VS{The role of viscosity on drop impact forces}
+	We indeed have briefly summarized the results from \citet{zhang2022impact} for the sake of completeness, but the main focus of \S~3.1 is to explore the parameter space given by $0.001 < Oh < 0.2$ for arbitrary Weber numbers ($We$).
+This range represents a viscosity variation of over two orders of magnitude, which is a significant extension of the parameter space compared to the fixed Ohnesorge number ($Oh = 0.0025$) discussed in \citet{zhang2022impact}.
+Although viscous dissipation plays a minor role in the low $Oh$ limit, as evident from Figure 3, this exploration provides valuable insights into the drop impact dynamics across a considerably wider range of conditions.
 
-	\item \textit{Figure 2: Although there are several pressure and velocity maps, etc., to characterize the different regimes throughout the article, there is only a single force signal (figure 2).
-Would the article benefit from including force signals for at least limiting cases of the dimensionless parameters?
-Force signal, the easier way to experimentally characterize the phenomenon, should provide a simple signature of the regime at which the drop impact occurs.}
+	Furthermore, we have extended the parameter space to $Oh$ up to 100 in the context of the first impact force peak amplitude, as discussed in the remainder of \S~3.
+This extension by more than four orders of magnitude in a parameter, which was held fixed in our PRL study at its ``water" value ($Oh = 0.0025$), allows us to investigate the role of viscous effects in the drop impact process--a totally novel aspect of our current work.
 
-	 We thank the reviewer for this remark.
-To extend the comparison at different Ohnesorge numbers $Oh$, we have added two additional $F(t)$ curves in figure 2 (see figure~\ref{fig:summary}).
-Furthermore, throughout the manuscript, we present experimental data wherever available (see figures 3 and 7).
+	Regarding the second impact force peak amplitude, we have explored the entire relevant two-dimensional $We$-$Oh$ parameter space.
+We have earlier found that there is an upper bound on the bouncing drop purely due to viscous dissipation \citep{sanjay_chantelot_lohse_2023}, which is $Oh = 0.53$ for the drop sizes considered in this work.
+Consequently, the second peak ceases for drops with $Oh > 0.53$, as illustrated in the revised Figure 2.
+This finding provides new insights into the conditions under which drop rebound occurs and the role of viscous dissipation in limiting this phenomenon.
+
+	We believe that these extensions of the parameter space and the novel findings related to the first and second impact force peak amplitudes make our current work a significant contribution to the field, way beyond the scope of our previous article.
+These aspects provide a more comprehensive understanding of drop impact dynamics across a wide range of conditions and offer valuable insights for researchers in this area.
+	We hope that this clarification addresses the referee's concerns and highlights the significant advancements presented in our manuscript.
+
+	\item \textit{The second half of the manuscript contains (as far as I can tell) new contributions on the effect of viscosity in the force signal. However there are several important issues here. }
+
+	\begin{enumerate}
+		\item \textit{First, the force is computed from the pressure part of the stress only, which is certainly dubious for the highest Oh cases.
+This is an important flaw that should be corrected.}\\[0.5mm]
+
+		Thank you for raising this important point about the force computation for high Ohnesorge number ($Oh$) cases.
+
+		In our simulations, we model the non-wetting surface by assuming the presence of a thin air layer between the drop and the surface.
+This approach allows us to capture the essential physics of the drop impact process on non-wetting surfaces without explicitly resolving the complex interactions at the solid-liquid interface.
+
+		By integrating the pressure in the air layer, we effectively account for the viscous stresses just inside the drop due to the normal stress continuity at the drop-air interface.
+This approach is justified because the pressure in the air layer is directly influenced by the viscous stresses within the drop, also in the high $Oh$ regime where viscous effects dominate.
+
+		We acknowledge that, in principle, the full force calculation should include a viscous correction term due to the air viscosity.
+However, this correction is very minor because the relevant dimensionless number governing the air viscosity effects is the Ohnesorge number based on air viscosity ($Oh_a$), which we keep fixed at $10^{-5}$ throughout our study.
+The low value of $Oh_a$ suggests that the viscous effects in the air layer are negligible compared to those within the drop.
+We quantitatively show this in the supplementary materials of \citet{zhang2022impact}.
+
+		\item \textit{Second, the analysis of the dissipation is sketchy and not convincing.
+Why use an inertial scaling for the position of the ``foot"?
+Why should the dissipation be localised when, from the figure, it is clear that it is not?
+Why use a boundary layer analysis for a viscous-dominated regime?}\\[0.5mm]
 
@@
 			\centering
-	 	\includegraphics[width=\textwidth]{../Main/Figures/Figure1_summary_v5.pdf}
-	 	\caption{\VS{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
-These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
-		For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
-		The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $t_3 \approx 0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
-		Six instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), (iv) $t = 3.93\,\si{\milli\second}$ ($\approx 0.85t_2$), (v) $t = 4.63\,\si{\milli\second}$ ($t_2$), and (vi) $t = 5.25\,\si{\milli\second}$ ($\approx 1.15t_2$).
-		We stress the excellent agreement between experiments and simulations without any free parameters.
-The insets show representative snapshots at specific time instants overlaid with the drop boundaries from simulations in orange, also revealing good agreement.
-		The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity.
-The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.}}
-	 	\label{fig:summary}
+			\includegraphics[width=0.5\textwidth]{TestPlot/foot.pdf}
+			\caption{Foot diameter evolution in time as measured by \citet{langley2017impact}.
+Here, we illustrate different scaling predictions to get $D_{\text{foot}}/D_0 = $ (i) Wagner/inertial spreading, $\sqrt{6t}$ \citep{wagner1932stoss, Philippi2016, gordillo2019theory}, (ii) Purely geometry assuming an intersection between a sphere and a plane, $\sqrt{4t}$ \citep{zheng2021air, bilotto2023fluid}, and (iii) Hertz contact $\sqrt{2t}$ \citep{bertin2023similarity, bilotto2023fluid}.}
+			\label{fig:sqrt}
 		\end{figure}
 
-	 \begin{figure}
-	 	\centering
-	 	\includegraphics[width=\textwidth]{../main/Figures/ForceTimeVersusOhnesorge.pdf}
-	 	\caption{\blue{Anatomy of the first impact force peak amplitude for viscous impacts from our numerical simulations: the $Oh$ dependence of  (a) the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ and (b) the time $t_1$ to reach the first force peak amplitude normalized by inertial timescale $\tau_\rho = D_0/V_0$}.
-\VS{(c) The $Re$ dependence of the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ as compared to the (implicit) theoretical calculation of \citet{Gordillo2018}.} \blue{The black line corresponds to the scaling relationship described in \S~3.2.
-The Weber number is color-coded.}}
-	 	\label{fig:F1Anatomy_2}
-	 \end{figure}
+		Regarding the use of an inertial scaling for the position of the ``foot", we agree that it may seem counterintuitive for the highly viscous cases.
+However, as shown in the careful experiments by \citet{langley2017impact}, the drop footprint still scales as $D_{\text{foot}} \sim \sqrt{V_0D_0t}$, even for highly viscous cases.
+(also see figure~\ref{fig:sqrt}) We currently have the following hypotheses for the consistency of these scaling behaviors:
 
-	 \item 
 		\begin{enumerate}
-	 	 \item \textit{Line111-114: Previous studies have considered much broader ranges of viscosities (c.f.
-Cheng 2022 and references therein) using other liquids and solutions.
-Readers could be addressed for completeness.}
-	 	\item \textit{Figure 5: The authors of several other studies have found that $F1/F_\rho$ depends solely on the Reynolds number (Re), collapsing curves in an extensive range of high Re numbers.
-Have the authors tried to remove the dependency on $\gamma$ (through Oh)?
-Since $Re \equiv \frac{\sqrt{We}}{Oh}$, I wonder if using it could collapse curves, at least in the low Oh limit.}
+			\item For $Oh \ll 1$, the early time dynamics feature the inertial spreading as described by the Wagner flow that gives $D_{\text{foot}}/D_0 = \sqrt{6t}$ \citep{wagner1932stoss, Philippi2016, gordillo2019theory}.
+			\item Geometric effects owing to the intersection between a sphere and a plane results in $D_{\text{foot}}/D_0 = \sqrt{4t}$ \citep{zheng2021air, bilotto2023fluid}.
+			\item Viscous--Hertz analogy: For $Oh \gg 1$, the flow inside the drop follows Stokes equations which are analogous to the Hertz contact theory.
+This analogy gives $D_{\text{foot}}/D_0 = \sqrt{2t}$.
+See \citet{bertin2023similarity, bilotto2023fluid} for more details.
 		\end{enumerate}
 
-	Using water-glycerol mixtures allows us to probe two orders of magnitude in $Oh$ in the experiments.
-In the hindsight of finishing this project, we agree with the reviewer that using other liquids (such as silicone oil) will allow one to probe a wider range of viscosity  (and hence $Oh$).
-Of course, such liquids cannot be used with the superhydrophobic surfaces that we use in our work but would require superamphiphobic surfaces, such as the ones used in \citet{deng2012candle, ramirez2020lifting}.
-We have added this remark in the revised manuscript.
+		Investigating which of these two mechanisms dominates is beyond the scope of the present work, but we acknowledge that further research is needed to fully understand the underlying physics.
 
-	\S~\red{2.1:}\\
-	\VS{We note that using other liquids like silicone oil could allow for a wider range of viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.}
+		Regarding the localization of dissipation, we thank you for pointing out that the dissipation is not localized but spread throughout the drop for large $Oh$ cases.
+We agree that there will be a time lag between the dissipation being localized at the drop's footprint (right after impact) and then spreading inside the drop as the dissipation volume, given by $\Omega(t) = D_{\text{foot}}^2\lambda_\nu$, increases.
+The transition will occur at $\Omega(t) \sim D_0^3$.
+We have revised our discussion of dissipation in the manuscript to clarify this point and provide a more accurate description of the dissipation process.
 
-	Unfortunately, we do not have experiments for $Oh \gg 1$ (figure 5).
-Nonetheless, we can compare our results with those in \citet{Gordillo2018, cheng2021drop} illustrating $F_1(Re)$, where $Re = V_0D_0/\nu_d$ is the impact Reynolds number.
-We were, indeed, able to collapse the data for low $Re$ (high $Oh$) limit.
-there is still some scatter at high $Re$ (low $Oh$) owing to the $We$ dependence of the impact force peak amplitude.
-We have added this as figure 5(c).
-
-	\S~\red{3.2:}\\
-	\VS{Figure~5 further shows that these scaling laws are weakly dependent on the Weber number, as viscous dissipation consumes the entire initial kinetic energy of the impacting drop (figure~6).
-Once again, we stress that using the water-glycerol mixtures limits the range of $Oh$ that we can probe experimentally.
-	We further note that the first peak is robust and does not depend on the wettability of the substrate.
-Consequently, to compare with the existing data such as those in \citet{cheng2021drop} with different liquids to cover a wider range of liquid viscosities and to account for the apparent $We$-dependence, we plot $F_1$ compensated with $F_\rho$ against the impact Reynolds number $Re \equiv \frac{\sqrt{We}}{Oh} = V_0D_0/\nu_d$.
-	For the low $Re$ regime, such a plot allows us to describe the $We$ dependence on the prefactor more effectively, as illustrated in figure~5(c).
-However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude.
-This lack of a pure scaling behavior demonstrates how the interplay between kinetic energy and viscous dissipation within the drop dictates the functional dependence of the maximum impact force on $Oh$.}
-
-	\item
-	\begin{enumerate}
-		\item \textit{Eq.
-3.4: Following previous comments, results in the literature (e.g., Cheng 2022) include corrections as a function of Re in the low Re limit.
-Have the authors tried adding them to their expression to include both viscous and capillary contributions?}
-		\item \textit{Eq.~3.7: I am still not convinced of the validity of averaging over $t_{\text{max}}$ in Eq.~3.7.
-Many assumptions under consideration are valid only for the early impact and not through the spreading regime, which scales as $t_{\text{max}}$.
-In order to convince the readers, authors need to address this.}
-	\end{enumerate}
-
-	Thank you for raising this important point about the use of the $t_{\text{max}}$ as the timescale for impact in the large Ohnesorge number ($Oh$) regime.
-We appreciate the opportunity to clarify our approach and present the modifications made to the theoretical model based on your critique and our recent work \citep{sanjay2024PRL}.
-
-	In the revised version of the manuscript, we have made two major changes to the model:
-
-	\begin{enumerate}
-		\item[$\bullet$] We now integrate until $\tau_\rho$ instead of $t_{\text{max}}$, as you correctly pointed out. The first peak appears within a fraction of $t \sim \tau_\rho$ (see Figures 3 and 4).
-		\item[$\bullet$] For the viscous regime, we propose that the entire initial kinetic energy is lost from $t = 0$ until $t = \tau_\rho = D_0/V_0$.
-The viscous dissipation during this time frame dictates the drop impact force.
-	\end{enumerate}
-
-	With these modifications, the leading order of the model now gives $F_1 \sim 1/\sqrt{Re}$ (see Figure 5c of the revised manuscript or Figure~\ref{fig:F1Anatomy_2} of this reply).
-This result is consistent with the findings of \citet{Gordillo2018}.
-In fact, there is only a minor discrepancy between the theoretical results of \citet{Gordillo2018, cheng2021drop} and our direct numerical simulation data.
-
+		Regarding the use of a boundary layer analysis for a viscous-dominated regime, we acknowledge that this approach may not be the most appropriate for the highly viscous cases.
+To address this, we have compared our results with the implicit theory summarized in \citet{cheng2021drop} by looking at $F_1(Re)$, which seemingly collapses our data for low Reynolds numbers ($Re$).
+We have found that there is only a minor discrepancy between the theoretical results of \citet{Gordillo2018, cheng2021drop} and our direct numerical simulation data.
 However, we still recommend the need for a predictive model to obtain the first force peak amplitude $F_1$ based on the control parameters $We$ and $Oh$.
 We address this question in our recent work \citep{sanjay2024PRL}, where we use global energy balances to unify the scaling of drop impact forces in different parts of the parameter space.
-We have also added a brief discussion of this in the revised manuscript.
+We have added a brief discussion of this in the revised manuscript.
 
@@
 
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.9\textwidth]{../main/Figures/RegimeMaps_v3.pdf}
-		\caption{\blue{Regime map in terms of the drop Ohnesorge number $Oh$ and the impact Weber number $We$ to summarize the two peaks in the impact force by showing the different regimes described in this work based on (a) the first peak in the impact force peak amplitude $F_1$ and (b) the second peak in the impact force peak amplitude $F_2$.
-Both peaks are normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$.
-These regime maps are constructed using $\sim 1500$ simulations in the range $0.001 \leq Oh \leq 100$ and $1 \leq We \leq 1000$.} \VS{The gray solid line in (a) and dashed line in (b) mark the inertial--viscous transition ($Re = 1$) and the bouncing--no-bouncing transition \citep[$Oh_c = 0.53$ for $Bo = 1$, see][]{sanjay_chantelot_lohse_2023}, respectively.}}
-		\label{fig:RegimeMaps}
-	\end{figure}
+		\item \textit{Third, the analysis of the second peak is somewhat descriptive and quite sketchy as well.
+I feel this is a missed opportunity to provide an interesting take on the jet emission.
+The authors mention singular behviours, but does the force follow a self-similar evolution?
+Overall, I find the analysis of the net force as an observable as hiding interesting physics.
+For example, is the singular behaviour associated to a singular distribution of stress underneath the drop?}\\[0.5mm]
 
-	\item \textit{As a suggestion, I find that adding a Reynolds-number (tilted) axis, which nicely follows the slope of the central transition area of the white region of inset (a), will help readers to place previous experimental results in this regime map.
-It may be redundant, but still very helpful.}\\[0.1mm]
+		Thank you for raising these interesting points about the analysis of the second force peak and the potential for further investigation into the underlying physics.
 
-	We thank the review for this suggestion. We have modified figure 10 to include $Re = 1$ transition line (see figure~\ref{fig:RegimeMaps}).
+		The second force peak amplitude is non-universal and is restricted by the viscous upper bound such that drops with $Oh > 0.53$ will not bounce and the second force ceases.
+Furthermore, even for $Oh < 0.53$, the second peak only appears on non-wetting surfaces, making it challenging to develop a comprehensive underlying theory.
 
+		Your suggestion to explore the potential self-similar evolution of the singular behaviors associated with the thin, fast jets during drop impact is intriguing.
+We can draw an analogy between these jets and those experienced during bursting bubbles \citep{sanjay_lohse_jalaal_2021}, impacting disks \citep{bergmann2009controlled}, and other similar phenomena could provide valuable insights.
+The process is complicated by the presence of two control parameters ($We$ and $Oh$) in our case, as opposed to only one parameter ($Oh$ for bursting bubbles and $Fr$, Froude number for impacting disks) in the other cases described.
+
+		Developing a unifying theory to find $F_2(Oh, We)$ and understanding the nature of the singular behavior of $F_2$ are indeed active research goals for our team.
+We are also interested in answering questions such as what sets the magnitude of $We$ to observe the singular peak in force (given the robustness of the value $We = 9$ across several experimental groups) and what determines the extent of the island of singular behavior in Figure 10.
+But answering all these questions is really way beyond the scope of the present article.
+	\end{enumerate}
 \end{enumerate}

### 2024-06-08 Main/ViscousDropImpact_v6.tex
Initial commit

%\documentclass[referee]{jfm}
\documentclass{jfm}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\usepackage{amsmath}
\usepackage[colorlinks, citecolor=blue]{hyperref}

%\usepackage[usenames,dvipsnames]{xcolor} % color package
\usepackage{siunitx}
\usepackage{lineno}
\linenumbers

%\usepackage{setspace}
%\doublespacing

%\newcommand*\blue{\textcolor{blue}}
%\newcommand*\red{\textcolor{black}}

%\usepackage[normalem]{ulem}
\usepackage{xcolor}
\newcommand{\VS}[1]{{\textcolor{orange}{#1}}}

%\shorttitle{Inertia \& viscosity dictate drop impact forces}
\shorttitle{\VS{The role of viscosity on drop impact forces}}
\shortauthor{V. Sanjay, B. Zhang, C. Lv, and D. Lohse}

%\title{Inertia \& viscosity dictate drop impact forces}
\title{\VS{The role of viscosity on drop impact forces}}
\author{Vatsal Sanjay\aff{1}
 \corresp{\email{vatsalsanjay@gmail.com}},
 Bin Zhang\aff{2}
 \corresp{\email{binzhang0710@mail.tsinghua.edu.cn}},
 Cunjing Lv\aff{2}
 \corresp{\email{cunjinglv@mail.tsinghua.edu.cn}},
 \and Detlef Lohse{\aff{1}$^{,}$\aff{3}}
 \corresp{\email{d.lohse@utwente.nl}}}

\affiliation{\aff{1}Physics of Fluids Group, Max Planck Center for Complex Fluid Dynamics, Department of Science and Technology, and J. M. Burgers Centre for Fluid Dynamics, University of Twente,  P. O. Box 217, 7500 AE Enschede, The Netherlands\aff{2}Department of Engineering Mechanics, AML, Tsinghua University, Beijing 100084, China\aff{3}Max Planck Institute for Dynamics and Self-Organization, Am Fassberg 17, 37077 G\"{o}ttingen, Germany}

%% Commands
\newcommand{\Wen}{\mathit{We}}
\newcommand{\Ohn}{\mathit{Oh}}
\newcommand{\Bon}{\mathit{Bo}}

\begin{document}
\maketitle

\begin{abstract}

A liquid drop impacting a rigid substrate undergoes deformation and spreading due to normal reaction forces, which are counteracted by surface tension. On a non-wetting substrate, the drop subsequently retracts and takes off.
Our recent work (Zhang et al., \textit{Phys. Rev. Lett.}, vol. 129, 2022, 104501) revealed two peaks in the temporal evolution of the normal force $F(t)$--one at impact and another at jump-off. The second peak coincides with a Worthington jet formation, which vanishes at high viscosities due to increased viscous dissipation affecting flow focusing.
In this article, using experiments, direct numerical simulations, and scaling arguments, we characterize both the peak amplitude $F_1$ at impact and the one at take off ($F_2$) and elucidate their dependency on the control parameters: the Weber number $We$ (dimensionless impact velocity) and the Ohnesorge number $Oh$ (dimensionless viscosity). 
\VS{The first peak amplitude $F_1$ and the time $t_1$ to reach it depend on inertial timescales for low viscosity liquids, remaining nearly constant for viscosities up to 100 times that of water. For high viscosity liquids, we balance the rate of change in kinetic energy with viscous dissipation to obtain new scaling laws: $F_1/F_\rho \sim \sqrt{Oh}$ and $t_1/\tau_\rho \sim 1/\sqrt{Oh}$, where $F_\rho$ and $\tau_\rho$ are the inertial force and time scales, respectively, which are consistent with our data.}
The time $t_2$ at which the amplitude $F_2$ appears is set by the inertio-capillary timescale $\tau_\gamma$, independent of both the viscosity and the impact velocity of the drop. However, these properties dictate the magnitude of this amplitude.

\end{abstract}

\begin{keywords}

\end{keywords}

\section{Introduction} \label{sec:intro}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/Schematic_v2.pdf}
	\caption{(a) Problem schematic with an axisymmetric computational domain used to study the impact of a drop with diameter $D_0$ and velocity $V_0$ on a non-wetting substrate. In the experiments, we use a quartz force sensor to measure the temporal variation of the impact force. The subscripts $d$ and $a$ denote the drop and air, respectively, to distinguish their material properties, which are the density $\rho$ and the dynamic viscosity $\eta$. The drop–air surface tension coefficient is $\gamma$. The grey dashed-dotted line represents the axis of symmetry, $r = 0$. Boundary air outflow is applied at the top and side boundaries (tangential stresses, normal velocity gradient, and ambient pressure are set to zero). The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case). (b) The phase space with control parameters: the Weber number ($We$: dimensionless impact velocity) and the Ohnesorge number ($Oh$: dimensionless viscosity), exemplifying different applications.}
	\label{fig:schematic}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/Figure1_summary_v5.pdf}
	\caption{\VS{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$. These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
	For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively. 
	The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $t_3 \approx 0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
	Six instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), (iv) $t = 3.93\,\si{\milli\second}$ ($\approx 0.85t_2$), (v) $t = 4.63\,\si{\milli\second}$ ($t_2$), and (vi) $t = 5.25\,\si{\milli\second}$ ($\approx 1.15t_2$). 
	We stress the excellent agreement between experiments and simulations without any free parameters. The insets show representative snapshots at specific time instants overlaid with the drop boundaries from simulations in orange, also revealing good agreement. 
	The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity. The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.}}
\label{fig:summary}
\end{figure}

Drop impacts have piqued the interest of scientists and artists alike for centuries, with the phenomenon being sketched by \citet{da1508notebooks} in the early 16$^{\text{th}}$ and photographed by \citet{worthington1876, worthington1876b} in the late 19$^{\text{th}}$ century. It is, indeed, captivating to observe raindrops hitting a solid surface \citep{kim2020raindrop, lohse-2020-pnas} or ocean spray affecting maritime structures \citep{berny2021statistics, villermaux2022bubbles}. The phenomenology of drop impact is extremely rich, encompassing behaviors such as drop deformation \citep{Biance2006, molavcek2012quasi, chevy2012liquid}, spreading \citep{laan2014maximum, Wildeman2016}, splashing \cite{xu2005drop, riboux2014experiments, thoraval2021nanoscopic}, fragmentation \citep{villermaux2011drop, villermaux2020fragmentation}, bouncing \citep{Richard2000, kolinski-2014-epl, Jha2020, chubynsky-2020-prl, sharma-2021-jfm, sanjay_chantelot_lohse_2023}, and wetting \citep{degennes-1985-rmp, fukai-1995-pof, quere-2008-arms, Bonn2009}. These behaviors are influenced by the interplay of inertial, capillary, and viscous forces, as well as additional factors like non-Newtonian properties \citep{bartolo2005retraction, bartolo2007dynamics,  smith-2010-prl, gorin-2022-langmuir} of the liquid and even ambient air pressure \citep{xu2005drop}, making the parameter space for this phenomenon both extensive and high-dimensional.

Naturally, even the process of a Newtonian liquid drop impacting a rigid substrate is governed by a plethora of control parameters, including but not limited to the drop's density $\rho_d$, diameter $D_0$, velocity $V_0$, dynamic viscosity $\eta_d$, surface tension $\gamma$, \VS{and acceleration due to gravity $g$} (figure~\ref{fig:schematic}a). 
To navigate this rich landscape, we focus on two main dimensionless numbers that serve as control parameters (figure~\ref{fig:schematic}b): the Weber number $We$, which is the ratio of inertial to capillary forces and is given by

\begin{align}
	\label{Eq:WeDefinition}
	We = \frac{\rho_d V_0^2 D_0}{\gamma},
\end{align}

\noindent and the Ohnesorge number $Oh$, which captures the interplay between viscous damping and capillary oscillations, offering insights into how viscosity affects the drop's behavior upon impact,

\begin{align}
	\label{Eq:OhDefinition}
	Oh = \frac{\eta_d}{\sqrt{\rho_d \gamma D_0}}.
\end{align}

\noindent \VS{Additionally, the Bond number }

\VS{\begin{align}
		\label{Eq:BoDefinition}
	Bo = \frac{\rho_dgD_0^2}{\gamma}
\end{align}}

\noindent \VS{compares gravity to inertial forces and is needed to uniquely define the non-dimensional problem.}

The drop impact is not only interesting from the point of view of fundamental research but also finds relevance in inkjet printing \citep{lohse2022fundamental}, the spread of respiratory drops carrying airborne microbes \citep{bourouiba2021fluid, ji2021compound, pohlker2023respiratory}, cooling applications \citep{kim2007spray, shiri2017heat, jowkar2019rebounding}, agriculture \citep{bergeron2000controlling, bartolo2007dynamics, kooij2018determines, sijs2020effect, he2021optimization, hoffman2021controlling}, criminal forensics \citep{smith2018influence, smith-2018-curropincolloidinterfacesci}, and many other industrial and natural processes \citep{rein-1993-fluiddynres, yarin2006drop, Tuteja2007, Cho2016, Josserand2016, Yarin2017, Liu2017, Hao2016, Yarin2017, Wu2020}. For these applications, it is pertinent to understand the forces involved in drop impacts, as these forces can lead to soil erosion \citep{Nearing1986} or damage to engineered surfaces \citep{Ahmad2013, Amirzadeh2017, Gohardani2011}. We refer the readers to \citet{cheng2021drop} for an overview of the recent studies unraveling drop impact forces; see also \citet{Li2014, Soto2014, Philippi2016, Zhang2017, Gordillo2018, Mitchell2019, Zhang2019}.

These forces have been studied by \citet{zhang2022impact}, employing experiments and simulations and deriving scaling laws. 
A liquid drop impacting a non-wetting substrate (figure~\ref{fig:summary}i-vi) undergoes a series of phases--spreading, recoiling, and potentially rebounding \citep{chantelot2018rebonds}--driven by the normal reaction force exerted by the substrate. 
The moment of touch-down (figure~\ref{fig:summary}i-ii) \citep{wagner1932stoss, Philippi2016, Gordillo2018} is not surprisingly associated with a pronounced peak in the temporal evolution of the drop impact force $F(t)$ owing to the sudden deacceleration as high as $100$ times the acceleration due to gravity \citep{Clanet2004} (figure~\ref{fig:summary}, $F(t = 0.37\,\si{\milli\second}) \approx 5.1\,\si{\milli\newton}$). The force diminishes as the drop reaches its maximum spreading diameter (figure~\ref{fig:summary}iii). \citet{zhang2022impact} revealed that also the jump-off is accompanied by a peak in the normal reaction force, which was up to then unknown (figure~\ref{fig:summary}, $F_2(t_2 = 4.63\,\si{\milli\second}) \approx 2.3\,\si{\milli\newton}$ for the second force peak amplitude--at time $t_2$ after impact). The second peak in the force also coincides with the formation of a Worthington jet, a narrow upward jet of liquid that can form due to flow focusing by the retracting drop (figure~\ref{fig:summary}iv-vi). Under certain conditions ($We \approx 9$), this peak can be even more pronounced than the first. This discovery is critical for superhydrophobicity which is volatile and can fail due to external disturbances such as pressure \citep{Lafuma2003, Callies2005, Sbragaglia2007, Li2017}, evaporation \citep{Tsai2010, Chen2012, Papadopoulos2013},  mechanical vibration \citep{Bormashenko2007}, or the impact forces of prior droplets \citep{Bartolo2006Bouncing}.

In contrast to our prior study \citet{zhang2022impact}, which fixed the Ohnesorge number to that of a 2 mm diameter water drop (Oh = 0.0025), our present investigation reported in this paper explores a broader parameter space. We systematically and independently vary the Weber and Ohnesorge numbers, extending the range of $Oh$ to as high as 100. This comprehensive approach enables us to develop new scaling laws and provides a more unified understanding of the forces involved in drop impact problems. Our findings are particularly relevant for applications with varying viscosities and impact velocities (figure~\ref{fig:schematic}).

The structure of this paper is as follows: \S\ref{sec:Methods} briefly describes the experimental and numerical methods. \S\ref{sec:FirstPeak} and  \S\ref{sec:SecondPeak} offer detailed analyses of the first and second peaks, respectively, focusing on their relationships with the Weber number ($We$) and the Ohnesorge number ($Oh$). Conclusions and perspectives for future research are presented in Section~\ref{sec:Conclusion}.

\section{Methods}\label{sec:Methods}

\subsection{Experimental method}

\begin{table}
	\begin{center}
		\def~{\hphantom{0}}
		\begin{tabular}{lccc}
			glycerol & $\rho_d$ & $\eta_d$  & $\gamma$\\
			(wt \%) &(kg/m$^{3}$) &(mPa.s)& (mN/m)\\[3pt]
			0 & 1000 & 1 & 72 \\
			50 & 1124 & 5 & 61 \\
			63 & 1158 & 10 & 61 \\
			74 & 1188 & 25.3 & 61 \\
			80 & 1200 & 45.4 & 61 \\
			85 & 1220 & 80.2 & 61 \\
		\end{tabular}
		\caption{\VS{Properties of the water-glycerol mixtures used in the experiments. $\rho_d$ and $\eta_d$ are the density and viscosity of the drop, respectively and $\gamma$ denotes the liquid-air surface tension coefficient. These properties are calculated using the protocol provided in \citet{cheng2008formula, volk2018density}.}}
		\label{tab:table00}
	\end{center}
\end{table}

In the experimental setup, shown schematically in figure~\ref{fig:schematic}(a), a liquid drop impacts a superhydrophobic substrate. \VS{For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}. On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}.} 
\VS{The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}. Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}. The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle. Throughout this work, we use drops with diameter $2.54 \pm 0.02\,\si{\milli\meter}$ unless otherwise stated. Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~\eqref{Eq:OhDefinition}). The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate. Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript. In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity. Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia.}
All experiments are conducted at ambient pressure and temperature. The impact force is directly measured using a high-precision piezoelectric force transducer (Kistler 9215A) with a resolution of $0.5\,\si{\milli\newton}$. During these measurements, the high-frequency vibrations induced by the measurement system and the surrounding noise are spectrally removed using a low pass filter with a cut-off frequency of $5\,\si{\kilo\hertz}$, following the procedure in \citet{Li2014, Zhang2017, Gordillo2018, Mitchell2019}. 
The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$. \VS{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size. We refer the readers to the supplementary material of \citet{zhang2022impact} for further details of the experimental setup.}

\subsection{Numerical framework}

In the direct numerical simulations (DNS) employed for this study, the continuity and the momentum equations take the form

\begin{align}\label{eqn:continuity}
	\boldsymbol{\nabla\cdot v} = 0 
\end{align}

\noindent and

\begin{align}
	\frac{\partial \boldsymbol{v}}{\partial t} + \boldsymbol{\nabla \cdot}\left(\boldsymbol{vv}\right) = \frac{1}{\rho}\left(-\boldsymbol{\nabla} p + \boldsymbol{\nabla\cdot}\left(2\eta\boldsymbol{\mathcal{D}}\right)  + \boldsymbol{f}_\gamma\right) + \boldsymbol{g},
\end{align}

\noindent respectively. Here, $\boldsymbol{v}$ is the velocity field, $t$ is time, $p$ is pressure, \VS{and $\boldsymbol{g}$ is acceleration due to gravity}. We use the free software program \textit{Basilisk C} that employs the well-balanced geometric volume of fluid (VoF) method \citep{popinet2009accurate, popinet2018numerical}. The VoF tracer $\Psi$ delineates the interface between the drop (subscript \textit{d}, $\psi = 1$)  and air (subscript \textit{a}, $\psi = 0$), introducing a singular force $\boldsymbol{f}_\gamma \approx \gamma\kappa\boldsymbol{\nabla}\Psi$ \citep[$\kappa$ denotes interfacial curvature, see][]{brackbill1992continuum} to respect the dynamic boundary condition at the interface. This VoF tracer sets the material properties such that density $\rho$ and viscosity $\eta$ are given by

\begin{align}
	\rho = \rho_a + \left(\rho_d - \rho_a\right)\Psi
\end{align}

\noindent and

\begin{align}
	\eta = \eta_a + \left(\eta_d - \eta_a\right)\Psi,
\end{align}

\noindent respectively. This VoF field is advected with the flow, following the equation

\begin{align}\label{eqn:VoF}
	\frac{\partial \Psi}{\partial t} + \boldsymbol{\nabla \cdot}\left(\boldsymbol{v}\Psi\right) = 0.
\end{align}

\noindent Lastly, we calculate the normal reaction force $\boldsymbol{F}(t)$ by integrating the pressure field $p$ at the substrate,

\begin{align}\label{Eqn:ReactionForce}
	\boldsymbol{F}(t) = \left(\int_\mathcal{A} \left(p-p_0\right)d\mathcal{A}\right)\hat{\boldsymbol{z}},
\end{align}

\noindent where, $p_0$, $d\mathcal{A}$, and $\hat{\boldsymbol{z}}$ are the ambient pressure, substrate area element, and the unit vector normal to the substrate, respectively.

We leverage the axial symmetry of the drop impact (figure~\ref{fig:schematic}a). This axial symmetry breaks at large $We$ ($\ge 100$ for water drops and even larger Weber number for more viscous drops), owing to destabilization by the surrounding gas after splashing \citep{xu2005drop, Eggers2010, Driscoll2011, riboux2014experiments, Josserand2016, zhang2022impact}. 
To solve the governing equations~\eqref{eqn:continuity}--\eqref{eqn:VoF}, the velocity field $\boldsymbol{v}$ and time $t$ are normalized by the inertio-capillary scales, $V_\gamma = \sqrt{\gamma/\rho_dD_0}$ and $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$, respectively. Furthermore, the pressure is normalized using the capillary pressure scale $p_\gamma = \gamma/D_0$. In such a conceptualization, $Oh$ and $We$ described in \S\ref{sec:intro} uniquely determine the system. 
The Ohnesorge number based on air viscosity $Oh_a = \left(\eta_a/\eta_d\right)Oh$ and air-drop density ratio $\rho_a/\rho_d$ are fixed at $10^{-5}$ and $10^{-3}$, respectively to minimize the influence of the surrounding medium on the impact forces. 
The substrate is modeled as a no-slip and non-penetrable wall, whereas vanishing stress and pressure are applied at the remaining boundaries to mimic outflow conditions for the surrounding air. \VS{The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case). At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. It is important to note that the drops may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate. These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers. The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}. However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}
The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields. A minimum grid size $\Delta = D_0/2048$ is used for this study.

\VS{To ensure a perfectly non-wetting surface, we impose a thin air layer (minimum thickness $\sim \Delta/2$) between the drop and the substrate. This air layer prevents direct contact between the liquid and solid \citep{kolinski-2014-epl, sprittles2024gas}, effectively mimicking a perfectly non-wetting surface. The presence of this air layer is crucial for capturing the dynamics of drop impact on superhydrophobic surfaces, as it allows for the formation of an air cushion that can significantly affect the spreading and rebound behavior of the drop \citep{ramirez2020lifting, sanjay_chantelot_lohse_2023}.
While this approach does not fully resolve the microscopic dynamics within the air layer itself, such as the high-velocity gradients and viscous dissipation inside the gas film once it thins below a critical size ($\sim 10\Delta$), it has been shown to accurately capture the macroscopic behavior of drop impact in the parameter range of interest \citep{ramirez2020lifting, sanjay2023drop, alventosa2023inertio, garcia2024skating}. We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, vatsal_sanjay_2023_7598181, zhang2022impact} for details on the numerical framework.}

\section{Anatomy of the first impact force peak}\label{sec:FirstPeak}

This section elucidates the anatomy of the first impact force peak and its relationship with the Weber $We$ and Ohnesorge $Oh$ numbers, first for the inertial limit (\S\ref{sec:FirstInertialPeak}, $Oh \ll 1$) and then for the viscous asymptote (\S\ref{sec:ViscousImpact}, $Oh \gg 1$). The results of this section are summarized in figure~\ref{fig:F1Anatomy} that shows an excellent agreement between experiments and simulations without any free parameters.

\subsection{Low Ohnesorge number impacts}\label{sec:FirstInertialPeak}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/Force1_Anatomy_v2.pdf}
	\caption{Anatomy of the first impact force peak amplitude at low $Oh$ in between 0.0025 and 0.2, see color legend: $We$ dependence of the (a) magnitude $F_1$ normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$ and time $t_1$ to reach the first force peak amplitude normalized by (b) the inertial timescale $\tau_\rho = D_0/V_0$ and (c) the inertio-capillary time scale $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$.}
	\label{fig:F1Anatomy}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/F1_Drops_LowOh_v2.pdf}
	\caption{Direct numerical simulations snapshots illustrating the drop impact dynamics for $We$ = (a) 40 and (b) 2. The left-hand side of each numerical snapshot shows the pressure normalized by (a) the inertial pressure scale $\rho_dV_0^2$ and (b) the capillary pressure scale $\gamma/D_0$. The right-hand side shows the velocity field magnitude normalized by the impact velocity $V_0$.}
	\label{fig:F1AnatomyLowOh}
\end{figure}

For low $Oh$ and large $We$, inertial force and time scales dictate the drop impact dynamics (figures~\ref{fig:F1Anatomy} and~\ref{fig:F1AnatomyLowOh}). As the drop falls on a substrate, the part of the drop immediately in contact with the substrate stops moving, whereas the top of the drop still falls with the impact velocity (figure~\ref{fig:F1AnatomyLowOh}, from $t = t_1/4$ until $t = t_1$). Consequently, momentum conservation implies

\begin{align}
	F_1 \sim V_0\frac{dm}{dt},
\end{align}

\noindent where the mass flux $dm/dt \sim \rho_d V_0D_0^2$ \citep{Soto2014, zhang2022impact}. As a result, the first peak amplitude scales with the inertial pressure force (figure~\ref{fig:F1Anatomy}a)

\begin{align}\label{eq:F1}
	F_1 \sim F_\rho,\text{ where }F_\rho =  \rho_d V_0^2D_0^2,
\end{align}

\noindent for high Weber numbers ($\Wen > 30$, $F_1 \approx 0.81F_\rho$). Furthermore, the time $t_1$ to reach $F_1$ follows

\begin{align}\label{eq:t1}
	t_1 \sim \frac{D_0}{V_0} = \tau_\rho,
\end{align}

\noindent where, $\tau_\rho$ is the inertial timescale. The relation between equations~\eqref{eq:F1} and~\eqref{eq:t1} is apparent from the momentum conservation which implies that the impulse of the first force peak is equal to the momentum of the impacting drop, i.e., $F_1t_1 \sim \rho_dV_0D_0^3 = F_\rho\tau_\rho$ (see \citealp{Gordillo2018}, \citealp{zhang2022impact}, and figures~\ref{fig:F1Anatomy}b,c). These scaling laws depend only on the inertial shock at impact and are wettability-independent \citep{Zhang2017, Gordillo2018, zhang2022impact}. For details of the scaling law, including the prefactors, we refer the readers to \citet{Philippi2016, Gordillo2018, cheng2021drop}.

Figure~\ref{fig:F1Anatomy} further illustrates that this inertial asymptote is insensitive to viscosity variations up to 100-fold as $F_1 \sim F_\rho$ and $t_1 \sim \tau_\rho$ for $0.0025 < Oh < 0.2$. However, deviations from the inertial force and time scales are apparent for $\Wen < 30$ (figure~\ref{fig:F1Anatomy}), a phenomenon also reported in earlier work \citep{Soto2014, zhang2022impact}. In these instances, inertia does not act as the sole governing force but instead complements surface tension, which dictates the pressure inside the drop ($p \sim \gamma/D_0$ throughout the drop for $We \lesssim 1$, figure~\ref{fig:F1AnatomyLowOh}b). \citet{zhang2022impact} proposed an empirical functional dependence as

\begin{align}
	F_1 = \left(\alpha_1\rho_d V_0^2 + \alpha_2\frac{\gamma}{D_0}\right)D_0^2,
\end{align}

\noindent based on dimensional analysis, with $\alpha_1$ and $\alpha_2$ as free parameters which were determined to be approximately $1.6$ and $0.81$, respectively for water ($Oh = 0.0025$). These coefficients only deviate marginally in the current work despite the significant increase in $Oh$ as compared to previous works \citep{cheng2021drop, zhang2022impact}. This consistency underscores the invariance of the pressure field inside the drop to an increase in $Oh$ (close to the impact region, figure~\ref{fig:F1AnatomyLowOh}a and throughout the drop, figure~\ref{fig:F1AnatomyLowOh}b).

\subsection{Large Ohnesorge number impacts}\label{sec:ViscousImpact}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figures/ForceTimeVersusOhnesorge.pdf}
\caption{Anatomy of the first impact force peak amplitude for viscous impacts from our numerical simulations: the $Oh$ dependence of  (a) the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ and (b) the time $t_1$ to reach the first force peak amplitude normalized by inertial timescale $\tau_\rho = D_0/V_0$. \VS{(c) The $Re$ dependence of the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ as compared to the (implicit) theoretical calculation of \citet{Gordillo2018}.} The black line corresponds to the scaling relationship described in \S\ref{sec:ViscousImpact}. The Weber number is color-coded.}
\label{fig:F1Anatomy_2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figures/Figure3.2_F1_Drops.pdf}
\caption{Direct numerical simulations snapshots illustrating the drop impact dynamics for $We = 100$ and $Oh$ = (a) 0.05, (b) 0.5, and (c) 5. The left-hand side of each numerical snapshot shows the viscous dissipation function $\xi_\eta$ normalized by the inertial scale $\rho_dV_0^3/D_0$. The right-hand side shows the velocity field magnitude normalized by the impact velocity $V_0$.}
\label{fig:QualitativeF1}
\end{figure}

Figure~\ref{fig:F1Anatomy_2} reaffirms the findings of \S\ref{sec:FirstInertialPeak} for low $Oh$ that the first impact peak amplitude $F_1$ and the time to reach this peak amplitude $t_1$ scale with $F_\rho$ and $\tau_\rho$, respectively. As the Ohnesorge number increases further, the first impact force peak amplitude normalized with $F_\rho$ begins to increase, indicating a transition around $Oh \approx 0.1$, where viscosity starts to play a significant role. At large $Oh$, we observe the scaling relationship (figure~\ref{fig:F1Anatomy_2}a)

\begin{align}
	F_1 \sim F_\rho\sqrt{Oh}.
\end{align}

\noindent The drop's momentum is still $\rho_dV_0D_0^3$ which must be balanced by the impulse from the substrate, $F_1t_1$ (see \S\ref{sec:FirstInertialPeak}, \citealp{Gordillo2018}, \citealp{zhang2022impact}, and figure~\ref{fig:F1Anatomy_2}b). Consequently, the time $t_1$ follows

\begin{align}
	t_1 \sim \frac{\tau_\rho}{\sqrt{Oh}}.
\end{align}

\VS{Figure~\ref{fig:F1Anatomy_2} further shows that these scaling laws are weakly dependent on the Weber number, as viscous dissipation consumes the entire initial kinetic energy of the impacting drop (figure~\ref{fig:QualitativeF1}). Once again, we stress that using the water-glycerol mixtures limits the range of $Oh$ that we can probe experimentally. 
We further note that the first peak is robust and does not depend on the wettability of the substrate. Consequently, to compare with the existing data such as those in \citet{cheng2021drop} with different liquids to cover a wider range of liquid viscosities and to account for the apparent $We$-dependence, we plot $F_1$ compensated with $F_\rho$ against the impact Reynolds number $Re \equiv \sqrt{We}/Oh = V_0D_0/\nu_d$. 
For the low $Re$ regime, such a plot allows us to describe the $We$ dependence on the prefactor more effectively, as illustrated in figure~\ref{fig:F1Anatomy_2}(c). However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude. This lack of a pure scaling behavior demonstrates how the interplay between kinetic energy and viscous dissipation within the drop dictates the functional dependence of the maximum impact force on $Oh$.}

To systematically elucidate these scaling behaviors in the limit of small $Re$, we need to find the typical scales for the rate of change of kinetic energy and that of the rate of viscous dissipation for the drop impact system. First, we can readily define an average rate of viscous dissipation per unit mass as

\begin{align}
	\bar{\varepsilon} \sim \frac{1}{\tau_\rho}\frac{1}{D_0^3}\int_0^{\tau_\rho}\int_\Omega\nu_d\left(\boldsymbol{\mathcal{D}:\mathcal{D}}\right)d\Omega dt,
\end{align}

\noindent where $\nu_d$ is the kinematic viscosity of the drop and $d\Omega$ is the volume element where dissipation occurs. Notice that $\bar{\varepsilon}$ has the dimensions of $V_0^3/D_0$, i.e., length squared over time cubed or velocity squared over time, as it should be for dissipation rate of energy per unit mass. We can estimate $\Omega = D_{\text{foot}}^2l_\nu$ (figure~\ref{fig:QualitativeF1}), where $D_{\text{foot}}$ is the drop's foot diameter in contact with the substrate and $l_\nu$ is the viscous boundary layer thickness. \VS{This boundary layer marks the region of strong velocity gradients ($\sim V_0/l_\nu$) analogous to the \citet{mirels1955laminar} shockwave-induced boundary layer. For details, we refer the authors to \citet{schlichting2016boundary, Schroll2010, Philippi2016}. Consequently, the viscous dissipation rate scales as}

\begin{align}\label{eq:dissipationScale}
	\bar{\varepsilon} \sim \frac{1}{\tau_\rho D_0^3}\int_0^{\tau_\rho}\nu_d \left(\frac{V_0}{l_\nu}\right)^2 D_{\text{foot}}^2l_\nu dt.
\end{align}

\noindent To calculate $D_{\text{foot}}$, we assume that the drop maintains a spherical cap shape throughout the impact (figure~\ref{fig:QualitativeF1}). To calculate the distance the drop would have traveled if there were no substrate, we use the relation $d \sim V_0t$. Simple geometric arguments allow us to determine the relation between the foot diameter and this distance, $D_{\text{foot}} \sim \sqrt{D_0d}$ \citep{lesser1981analytic, mandre2009precursors,  zheng2021air, bilotto2023fluid, bertin2023similarity}. Interestingly, this scaling behavior is similar to the inertial limit \citep{wagner1932stoss, Bouwhuis2012, Philippi2016, gordillo2019theory} as discussed by \citet{langley2017impact, bilotto2023fluid}. Furthermore, the viscous boundary layer $l_\nu$ can be approximated using $\sqrt{\nu_d t}$ \citep{mirels1955laminar, Eggers2010, Philippi2016}. Filling these in \eqref{eq:dissipationScale}, we get

\begin{align}	
	\bar{\varepsilon} \sim \frac{1}{\tau_\rho D_0^2}\int_0^{\tau_\rho}\sqrt{\nu_d} V_0^3 \sqrt{t} dt,
\end{align}

\noindent which on integration gives

\VS{\begin{align}\label{eq:eps0Final}
		\bar{\varepsilon} \sim \sqrt{\nu_d \tau_\rho}V_0^3/D_0^2, 
\end{align}}

\noindent \VS{where $\tau_\rho$ is the inertial time scale. Here, we assume that for highly viscous drops, all energy is dissipated within a fraction of $\tau_\rho$. Filling in \eqref{eq:eps0Final} and normalizing $\bar{\varepsilon}$ with the inertial scales $V_0^3/D_0$,}

\VS{\begin{align}\label{eq:DissipationScale}
		\frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \sqrt{\frac{\nu_d\tau_\rho}{D_0^2}} = \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}.
\end{align}}

\noindent Next, the kinetic energy of the falling drop is given by

\begin{align}\label{eq:KEdissipation}
	\dot{K}(t) \equiv \frac{dK(t)}{dt} \sim \rho_dD_0^3\bar{\varepsilon},\quad\text{where } K(t) = \frac{1}{2}m\left(V(t)\right)^2,
\end{align}

\noindent and $V(t)$ is the drop's center of mass velocity. The left-hand side of \eqref{eq:KEdissipation} can be written as

\begin{align}\label{eq:KE-powerTime}
	\dot{K}(t) = mV(t)\frac{dV(t)}{dt} = F(t)V(t).
\end{align}

\noindent In equation~\eqref{eq:KE-powerTime}, $F(t)$ and $V(t)$ scale with the first impact force peak amplitude $F_1$ and the impact velocity $V_0$, respectively, giving the typical scale of the rate of change of kinetic energy as

\begin{align}\label{eq:KE-power}
	\dot{K}^* \sim F_1V_0.
\end{align}

\noindent We stress that \eqref{eq:KE-power} states that the rate of change of kinetic energy is equal to the power of the normal reaction force, an observation already made by \citet{wagner1932stoss} and \citet{Philippi2016} in the context of impact problems. Lastly, at large $Oh$, viscous dissipation enervates kinetic energy completely giving (figure~\ref{fig:QualitativeF1}c, also see:  \citet{Philippi2016} and \citet{ Wildeman2016}),

\begin{align}\label{eq:force-Dissipation}
	\dot{K}^* \sim F_1V_0 \sim \rho_dD_0^3\bar{\varepsilon}
\end{align}

\noindent Additionally, we use the inertial scales to non-dimensionalize  \eqref{eq:force-Dissipation} and fill in \eqref{eq:DissipationScale}, giving

\VS{\begin{align}
		\label{Eq:viscIncrease}
		\frac{F}{F_\rho} \sim \frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}
\end{align}}

\noindent and using $F_1t_1 \sim \rho_dV_0D_0^3 = F_\rho\tau_\rho$,

\VS{\begin{align}
		\label{Eq:viscTime}
		\frac{t_1}{\tau_\rho} \sim \left(\frac{\sqrt{We}}{Oh}\right)^{1/2}.
\end{align}}

\VS{In summary, we use energy and momentum invariance to elucidate the parameter dependencies of the impact force as illustrated in figure~\ref{fig:F1Anatomy_2}. The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces. As the dimensionless viscosity of impacting drops increases, the lack of surface deformation increases the normal reaction force \eqref{Eq:viscIncrease}. Further, the invariance of incoming drop momentum implies that this increase in normal reaction force occurs on a shorter timescale \eqref{Eq:viscTime}.}

\section{Anatomy of the second impact force peak}\label{sec:SecondPeak}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/Force2_Anatomy_v4.pdf}
	\caption{Anatomy of the second impact force peak amplitude: $We$ dependence of the (a) magnitude $F_2$ normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$ and time $t_2$ to reach the second force peak amplitude normalized by (b) the inertio-capillary time scale $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$ and (c) inertial timescale $\tau_\rho = D_0/V_0$.}
	\label{fig:F2Anatomy}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/F2phenomenology.pdf}
	\caption{Direct numerical simulations snapshots illustrating the influence of $We$ and $Oh$ on the inception of the Worthington jet. All these snapshots are taken at the instant when the second peak appears in the temporal evolution of the normal reaction force ($t = t_2$). The left-hand side of each numerical snapshot shows the viscous dissipation function $\xi_\eta$ normalized by the inertial scale $\rho_dV_0^3/D_0$. The right-hand side shows the velocity field magnitude normalized by the impact velocity $V_0$. The gray velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.}
	\label{fig:F2Phenomenology}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/Figure4.3_F2_Drops.pdf}
	\caption{Direct numerical simulations snapshots illustrating the influence of $We$ and $Oh$ on the singular Worthington jet. (a) ($We, Oh$) = ($9, 0.0025$), (b) $Oh = 0.0025$ with $We$ = (i) $5$ and (ii) $12$, and (c) $We = 9$ with $Oh$ = (i) $0.005$ and (ii) $Oh = 0.05$. The left-hand side of each numerical snapshot shows the viscous dissipation function $\xi_\eta$ normalized by inertial scale $\rho_dV_0^3/D_0$. The right-hand side shows the velocity field magnitude normalized by the impact velocity $V_0$.}
	\label{fig:KillSingularity}
\end{figure}

This section delves into the anatomy of the second impact force peak amplitude $F_2$ as a function of the Weber $We$ and Ohnesorge $Oh$ numbers, summarized in figure~\ref{fig:F2Anatomy}. We once again note the remarkable agreement between  experiments and numerical simulations in this figure.

Similar to the mechanism leading to the formation of the first peak (\S\ref{sec:FirstPeak}), also the mechanism for the formation of this second peak is momentum conservation. As the drop takes off the surface, it applies a force on the substrate. As noted in \S\ref{sec:intro} and \citet{zhang2022impact}, this force also coincides with the formation of a Worthington jet (figure~\ref{fig:summary}iv-vi). The time $t_2$ at which the second peak is observed scales with the inertio-capillary timescale and is insensitive to $We$ and $Oh$ (figure~\ref{fig:F2Anatomy}b,c). Once again, we invoke the analogy between drop oscillation and drop impact to explain this behavior  \citep{Richard2002, chevy2012liquid}. At the time instant $t_2 \approx 0.44\tau_\gamma$, the drop's internal motion undergoes a transition from a predominantly radial flow to a vertical one due to the formation of the Worthington jet \citep{chantelot2018rebonds, zhang2022impact}. Figure~\ref{fig:F2Phenomenology} exemplifies this jet in the $Oh-We$ parameter space, which is intricately related to the second peak in the drop impact force. For low $Oh$ and large $We$, the drop retraction follows a modified Taylor-Culick dynamics \citep{bartolo2005retraction, Eggers2010, sanjay-2022-arxiv}. As $We$ is increased, the jet gets thinner but faster, maintaining a constant momentum flux $\rho_dV_j^2d_j^2$, where $V_j$ and $d_j$ are the jet's velocity and diameter, respectively \citep[figure~\ref{fig:F2Phenomenology},][]{zhang2022impact}. This invariance leads to the observed scaling $F_2 \sim F_\rho$ in this regime ($F_2 \approx 0.37F_\rho$ for $We \ge 30, Oh \le 0.01$).

Furthermore, the low $We$ and $Oh$ regime relies entirely on capillary pressure (figure~\ref{fig:F1AnatomyLowOh}). Subsequently, $F_2 \sim F_\gamma = \gamma D_0$ for $Oh < 0.01$ and $We < 30$ (figure~\ref{fig:F2Anatomy}). This flow focusing (figure~\ref{fig:F2Phenomenology}) is most efficient for $We = 9$ (figure~\ref{fig:KillSingularity}a, $t_2/2 < t < t_2$, \citealp{renardy2003pyramidal, Bartolo2006Singular}) where the capillary resonance leads to a thin-fast jet, accompanied by a bubble entrainment, reminiscent of the hydrodynamic singularity (figure~\ref{fig:KillSingularity}, \citealp{zhang2022impact, sanjay_lohse_jalaal_2021}). The characteristic feature of this converging flow is a higher magnitude of $F_2$ compared to $F_1$ (figure~\ref{fig:F2Anatomy}).

However, this singular jet regime is very narrow in the $Oh-We$ phase space. Figure~\ref{fig:KillSingularity}b shows two cases for water drops ($Oh = 0.0025$) at different $We$ ($5$ and $12$ for figures~\ref{fig:KillSingularity}b-i and b-ii, respectively). Bubble entrainment does not occur in either of these cases. Consequently, the maximum force amplitude diminishes for these two cases (figure~\ref{fig:F2Anatomy}). Nonetheless, these cases are still associated with high local viscous dissipation near the axis of symmetry owing to the singular nature of the flow. Another mechanism to inhibit this singular Worthington jet is viscous dissipation in the bulk. As the Ohnesorge number increases, this singular jet formation disappears ($Oh = 0.005$, figure~\ref{fig:KillSingularity}c-i), significantly reducing the second peak of the impact force. For even higher viscosities, the drop no longer exhibits the sharp, focused jet formation seen at lower viscosities, and the second peak in the force is notably diminished ($Oh = 0.05$, figure~\ref{fig:KillSingularity}c-ii).

Lastly,  as $Oh$ increases, bulk dissipation becomes dominant (apparent from increasing $Oh$ at fixed $We$ in figure~\ref{fig:F2Phenomenology}) and can entirely inhibit drop bouncing. Recently, \citet{Jha2020, sanjay_chantelot_lohse_2023} showed that there \VS{exists a critical $Oh$, two orders of magnitude higher than that of a $2\si{\milli\meter}$ diameter water drop}, beyond which drops do not bounce either, irrespective of their impact velocity. Consequently, the second peak in the impact force diminishes for larger $Oh$, which explains the monotonic decrease of the amplitude $F_2$ observed in figure~\ref{fig:F2Anatomy} for $We > 30, Oh > 0.01$.

\section{Conclusion and outlook}\label{sec:Conclusion}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Figures/RegimeMaps_v3.pdf}
	\caption{Regime map in terms of the drop Ohnesorge number $Oh$ and the impact Weber number $We$ to summarize the two peaks in the impact force by showing the different regimes described in this work based on (a) the first peak in the impact force peak amplitude $F_1$ and (b) the second peak in the impact force peak amplitude $F_2$. Both peaks are normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$. These regime maps are constructed using $\sim 1500$ simulations in the range $0.001 \leq Oh \leq 100$ and $1 \leq We \leq 1000$. \VS{The gray solid line in (a) and dashed line in (b) mark the inertial--viscous transition ($Re = 1$) and the bouncing--no-bouncing transition \citep[$Oh_c = 0.53$ for $Bo = 1$, see][]{sanjay_chantelot_lohse_2023}, respectively.}}
	\label{fig:RegimeMaps}
\end{figure}

In this work, we study the forces and dissipation encountered during the drop impact process by employing experiments, numerical simulations, and theoretical scaling laws. We vary the two dimensionless control parameters--the Weber ($We$: dimensionless impact velocity) and the Ohnesorge number ($Oh$: dimensionless viscosity) independently to elucidate the intricate interplay between inertia, viscosity, and surface tension in governing the forces exerted by a liquid drop upon impact on a non-wetting substrate.

For the first impact force peak amplitude $F_1$, owing to the momentum balance after the inertial shock at impact, figure~\ref{fig:RegimeMaps}(a) summarizes the different regimes in the $Oh--We$ phase space. For low $Oh$, inertial forces predominantly dictate the impact dynamics, such that $F_1$ scales with the inertial force $F_\rho$ \citep{Philippi2016, Gordillo2018, Mitchell2019, cheng2021drop, zhang2022impact} and is insensitive to viscosity variations up to 100-fold. As $Oh$ increases, the viscosity becomes significant, leading to a new scaling law: $F_1 \sim F_\rho\sqrt{Oh}$. The paper unravels this viscous scaling behavior by accounting for the loss of initial kinetic energy owing to viscous dissipation inside the drop. Lastly, at low $We$, the capillary pressure inside the drop leads to the scaling $F_1 \sim F_\gamma$ \citep{molavcek2012quasi, chevy2012liquid}.

The normal reaction force described in this work is responsible for deforming the drop as it spreads onto the substrate, where it stops thanks to surface tension. If the substrate is non-wetting, it retracts to minimize the surface energy and finally takes off \citep{Richard2000}. In this case, the momentum conservation leads to the formation of a Worthington jet and a second peak in the normal reaction force, as summarized in figure~\ref{fig:RegimeMaps}(b). For low $Oh$ and high $We$, the second force peak amplitude scales with the inertial force ($F_\rho$), following a modified Taylor-Culick dynamics \citep{Eggers2010}. In contrast, capillary forces dominate at low $We$ and low $Oh$, leading to a force amplitude scaling of $F_2 \sim F_\gamma$. We also identify a narrow regime in the $Oh--We$ phase space where a singular Worthington jet forms, significantly increasing $F_2$ \citep{Bartolo2006Singular, zhang2022impact}, localized in the parameter space for $We \approx 9$ and $Oh < 0.01$. As $Oh$ increases, bulk viscous dissipation counteracts this jet formation, diminishing the second peak and ultimately inhibiting drop bouncing.

Our findings have far-reaching implications, not only enriching the fundamental understanding of fluid dynamics of drop impact but also informing practical applications in diverse fields such as inkjet printing, public health, agriculture, and material science where the entire range of $Oh-We$ phase space is relevant (figures~\ref{fig:schematic}b and~\ref{fig:RegimeMaps}). While this has identified new scaling laws, it also opens avenues for future research. For instance, it would be interesting to use the energy accounting approach to unify the scaling laws for the maximum spreading diameter for arbitrary $Oh$ \citep{laan2014maximum, Wildeman2016}. \VS{Although, the implicit theoretical model summarized in \citet{cheng2021drop} describes most of data in figure~\ref{fig:F1Anatomy_2}, we stress the importance of having a predictive model to determine $F_1$ for given $We$ and $Oh$ \citep{sanjay2024PRL}.} The $We$ influence on the impact force also warrants further exploration, especially in the regime $We \ll 1$ for arbitrary $Oh$ \citep{chevy2012liquid, molavcek2012quasi} and drop impact on compliant surfaces \citep{alventosa_cimpeanu_harris_2023, ma2023scaling}. Another potential extension of this work is to non-Newtonian fluids \citep{martouzet2021dynamic, aguero2022impact, bertin2023similarity, jin2023marbles}.\\[5mm]

\noindent{\bf  Code availability\bf{.}} The codes used in the present article are permanently available at \citet{vatsal_sanjay_2023_7598181}.\\

\noindent{\bf Acknowledgements\bf{.}}  We would like to thank Vincent Bertin for comments on the manuscript. We would also like to thank Andrea Prosperetti, Pierre Chantelot, Devaraj van der Meer, and Uddalok Sen for illuminating discussions.\\

\noindent{\bf Funding\bf{.}} We acknowledge the funding by the ERC Advanced Grant No. 740479-DDD and NWO-Canon grant FIP-II. B.Z and C.L are grateful for the support from National Natural Science Foundation of China (Grant No. 12172189, 11921002, 11902179). This work was carried out on the national e-infrastructure of SURFsara, a subsidiary of SURF cooperation, the collaborative ICT organization for Dutch education and research. This work was sponsored by NWO - Domain Science for the use of supercomputer facilities.\\

\noindent{\bf Declaration of Interests\bf{.}} The authors report no conflict of interest.\\

\noindent{\bf  Author ORCID\bf{.}}

V. Sanjay \href{https://orcid.org/0000-0002-4293-6099}{https://orcid.org/0000-0002-4293-6099};

B. Zhang \href{https://orcid.org/0000-0001-8550-2584}{https://orcid.org/0000-0001-8550-2584};

C. Lv \href{https://orcid.org/0000-0001-8016-6462}{https://orcid.org/0000-0001-8016-6462};

D. Lohse \href{https://orcid.org/0000-0003-4138-2255}{https://orcid.org/0000-0003-4138-2255}. \\

\bibliographystyle{jfm}
\bibliography{ViscousDropImpact_v2}

\end{document}

### 2024-06-17 Rebuttal.R2/Response to Reviewer 2.tex
started editing

%\documentclass[final]{article}
\documentclass[]{article}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=0.75in,
	top=0.75in,
	right=0.75in,
	bottom=1in,
}
\newcommand{\extramargin}[1]{}
%\newcommand{\extramargin}[1]{
	%	\setlength{\paperwidth}{250mm}
	%	\setlength{\evensidemargin}{-15mm}
	%	\setlength{\oddsidemargin}{-15mm}
	%}
\usepackage{gensymb}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}
\usepackage{amsmath}
\usepackage[url=false,
backend=bibtex,
style=authoryear-comp,
giveninits=true,
doi=true,
isbn=true,
backref=false,
dashed=false,
maxcitenames=2,
maxbibnames=99,
natbib=true]{biblatex}
\DeclareNameAlias{author}{last-first}
\DeclareFieldFormat
[article,inbook,incollection,inproceedings,patent,thesis,
unpublished,techreport,misc,book]
{title}{#1}
\renewcommand*{\revsdnamepunct}{}
\renewbibmacro{in:}{}
\usepackage{xpatch}
\xpatchbibmacro{date+extradate}{%
	\printtext[parens]%
}{%
	\setunit*{\space}%
	\printtext%
}{}{}

\addbibresource{../Main/ViscousDropImpact_v2.bib}
\nonfrenchspacing
\setlength\parindent{0pt}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{mathrsfs}
\usepackage[colorlinks,citecolor=purple]{hyperref}
\newcommand*\blue{\textcolor{blue}}
\newcommand*\red{\textcolor{red}}
\newcommand{\VS}[1]{{\textcolor{orange}{#1}}}

\renewcommand{\thefigure}{R\arabic{figure}}

\usepackage[obeyFinal,colorinlistoftodos, textwidth=60mm, shadow]{todonotes}
% todonotes specific macros begin!
\newcommand{\todoInsertref}[2]{\todo[color=green!40, #1]{#2}}
\newcommand{\todoExplaininDetails}[2]{\todo[color=orange!40, #1]{#2}}
\newcommand{\todoUrgent}[2]{\todo[color=red!40, #1]{#2}}
\newcommand{\todoSansUrgent}[2]{\todo[color=yellow!40, #1]{#2}}
\extramargin
%% todonotes specific macros end!

%opening
\title{Reply to Referee 2}
\author{Vatsal Sanjay, Bin Zhang, Cunjing Lv, and Detlef Lohse}
\date{}
\begin{document}

\maketitle

\textit{The authors have made some improvements to the manuscript based on the feedback provided, however some concerns were not fully addressed, as described below. I will use the same number scheme as in the prior report for consistency. I am content with the response for points that are not re-addressed below.}

We thank the referee for carefully reading our manuscript and providing valuable feedback and suggestions. We have reviewed the referee's comments and made changes based on their suggestions. Below, we offer a point-to-point reply to each of the referee's comments and include the changes made in the manuscript. The referee's comments are in italics, and our replies are in plain black. Changes in the manuscript are highlighted in orange.

\begin{enumerate}
	\item[$\bullet$] \textit{While I appreciate the inclusion of two additional force datasets, no new droplet shape profiles were included. For a paper that has a significant experimental component, I am surprised with the lack of direct visualization of the droplet dynamics. At minimum, I would recommend adding droplet shape profile comparisons for the two new data sets. Furthermore, these visualizations (including the one already included) should include a scale bar. Additionally, I would suggest including some experimental videos as supplementary materials.}

	\red{Yes, we can add these images. Will ask Cunjing to send them.}

	\item[$\bullet$] \textit{2. I appreciate the clarification regarding the error bars. However, a proper characterization (and description of the procedure by which they are determined) of the estimated parametric errors is still incomplete. Rather than including additional discussion, the authors reference the supplementary materials of a prior work (Zhang et al. (2022)). In reviewing this work, I cannot identify error assessments on key parameters (such as impact velocity). An error is now included on the droplet size, but there is no discussion of how drop size is determined nor how this error determined. Additionally, the related point regarding horizontal error bars was not addressed. Given that there is no length limit, I would suggest the authors include all details in the present manuscript rather than referring to incomplete discussions in prior work. (Also a minor point: the new horizontal line associated with the force sensor resolution should be described in the caption.)}

	\red{Will need Cunjing's help with the experimental setup details and error quantification.}

	\item[$\bullet$] \textit{3.}
	\begin{itemize}
		\renewcommand\labelitemi{--}
		\item \textit{In the experimental methods, the authors now describe that the Bond number is fixed at 1. Given the change in fluid properties between different solutions (with fixed droplet size), this cannot be the case. This needs to be made more precise. Furthermore, in the authors' prior work (Zhang et al. (2022)), it is mentioned that the Bo is fixed at 0.5 in simulation for similar experimental parameters. Why the change?}

		\red{To discuss: The results are Bond invariant in the leading order. Therefore, we chose a representative value of Bond = 1: this if for a diameter $0.00256\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, acceleration due to gravity $10\,\si{\meter/\second^2}$, surface tension $0.06\,\si{\newton/\meter}$. The dimensionless number that matter is the Froude number $Fr = V^2/gD_0 = We/Bo$ which is larger than 1 throughout the paper. The difference as compared to \citet{zhang2022impact} is in the length scale (2 mm in PRL and 2.56 mm in this work).}

		\item \textit{By now providing the drop size used, the Oh and Bo now can be used to define the parameters. However, it is not clear that the non-dimensional values are correct. For instance, Figures 2 and 3 both mention experimental conditions where Oh = 0.0025 whereas apparently different droplet sizes were used (2.05 mm in Figure 2, and 2.54 mm in Figure 3). Was a different fluid used between these figures such that the Oh could be held fixed? To clarify all of these issues, and for the ease of the readers, I strongly suggest the authors add the dimensional parameters for all experiments to the captions (as they have now done for Figure 2), an appendix, or make experimental data available in a supplementary data set.}

		\item \textit{Given the significant amount of data overlap in the various figures (e.g. Figure 3(b)), I am more convinced now that the parameters and raw data need to be provided in a supplementary dataset for reproducibility and to facilitate further comparisons.}

		\item \textit{The authors mention that their mixtures maintain ``a fairly constant surface tension and density, around 61 mN/m and 1000 kg/m$^3$, respectively.'' Since the values are now clearly specified in the table now, what is the meaning of these particular characteristic values which do in fact vary by around 20\%?}
	\end{itemize}

	\item[$\bullet$] \textit{5. The new title is more appropriate, but it should be mentioned in the title that there are specific restrictions/assumptions on the substrate (i.e. non-wetting), as the results are likely to depend on the surface wettability.}

	\red{The first impact peak is independent of wetability. The second peak, of course, depends on wetability as it only shows up on non-wetting surfaces.}

	\item[$\bullet$] \textit{7. If the experiment is repeatable, for a given drop height, the oscillation phase at which the droplet arrives at the surface should not vary, and thus is unlikely to be captured by the error bars as claimed. Some additional quantification of the non-sphericity of the droplets should be included.}

	\item[$\bullet$] \textit{11. While moving to a different fluid is one viable option, using smaller radii could also allow for smaller $Oh$.}

	\red{tbh: (not to be sent to reviewer) I thought that it was obvious. If we decreased the $r$, we would get higher $Oh$ but not too much as $Oh$ depends weakly on $r$ ($1/\sqrt{r})$ whereas it depends linearly on $\eta$. Also, using silicone oil would require special surface which is perhaps more important to remember. }

	Using smaller radii could also allow for larger $Oh$. We have added this in the revised manuscript.

	\S~\red{2.1:}\\
	\VS{We note that using liquids such as silicone oil can provide a broader range of viscosity variation when paired with a superamphiphobic substrate \citep{deng2012candle}. Additionally, employing drops of smaller radii facilitates the exploration of higher Ohnesorge numbers ($Oh$).}

	\item[$\bullet$] \textit{13. While the authors have done a good job clarifying their theoretical arguments, I am not sure that citation to unpublished (and currently inaccessible) work by the same group is appropriate or really necessary.}

	\red{Easily fixed: we can submit the SL theory on arxiv before we resubmit this work. :)}

\end{enumerate}

\textit{Regardless of the remaining critical feedback, I still believe this work is valuable and will be of interest to the community working on impacting droplets. However, I still have reservations on the current version given the persistent lack of details on the experiments.}

We appreciate the reviewer's belief in the value and interest of our work to the impacting droplets community. We acknowledge the reservations regarding the level of experimental detail. We have that the details added in the revised manuscript will address the reservation of the reviewer.

\printbibliography[title=References]
\end{document}

### 2024-06-17 Main/ViscousDropImpact_v7.tex
started editing

--- 2024-06-08 Main/ViscousDropImpact_v6.tex
@@
 \newcommand{\VS}[1]{{\textcolor{orange}{#1}}}
+\newcommand{\red}[1]{{\textcolor{red}{#1}}}
 
 %\shorttitle{Inertia \& viscosity dictate drop impact forces}
-\shorttitle{\VS{The role of viscosity on drop impact forces}}
+\shorttitle{The role of viscosity on drop impact forces}
 \shortauthor{V. Sanjay, B. Zhang, C. Lv, and D. Lohse}
@@
 %\title{Inertia \& viscosity dictate drop impact forces}
-\title{\VS{The role of viscosity on drop impact forces}}
+\title{The role of viscosity on drop impact forces}
 \author{Vatsal Sanjay\aff{1}
@@
 In this article, using experiments, direct numerical simulations, and scaling arguments, we characterize both the peak amplitude $F_1$ at impact and the one at take off ($F_2$) and elucidate their dependency on the control parameters: the Weber number $We$ (dimensionless impact velocity) and the Ohnesorge number $Oh$ (dimensionless viscosity).
-\VS{The first peak amplitude $F_1$ and the time $t_1$ to reach it depend on inertial timescales for low viscosity liquids, remaining nearly constant for viscosities up to 100 times that of water.
-For high viscosity liquids, we balance the rate of change in kinetic energy with viscous dissipation to obtain new scaling laws: $F_1/F_\rho \sim \sqrt{Oh}$ and $t_1/\tau_\rho \sim 1/\sqrt{Oh}$, where $F_\rho$ and $\tau_\rho$ are the inertial force and time scales, respectively, which are consistent with our data.}
+The first peak amplitude $F_1$ and the time $t_1$ to reach it depend on inertial timescales for low viscosity liquids, remaining nearly constant for viscosities up to 100 times that of water.
+For high viscosity liquids, we balance the rate of change in kinetic energy with viscous dissipation to obtain new scaling laws: $F_1/F_\rho \sim \sqrt{Oh}$ and $t_1/\tau_\rho \sim 1/\sqrt{Oh}$, where $F_\rho$ and $\tau_\rho$ are the inertial force and time scales, respectively, which are consistent with our data.
 The time $t_2$ at which the amplitude $F_2$ appears is set by the inertio-capillary timescale $\tau_\gamma$, independent of both the viscosity and the impact velocity of the drop.
@@
 	\includegraphics[width=\textwidth]{Figures/Figure1_summary_v5.pdf}
-	\caption{\VS{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
+	\caption{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
 These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
@@
 	The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity.
-The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.}}
+The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.}
 \label{fig:summary}
@@
 
-Naturally, even the process of a Newtonian liquid drop impacting a rigid substrate is governed by a plethora of control parameters, including but not limited to the drop's density $\rho_d$, diameter $D_0$, velocity $V_0$, dynamic viscosity $\eta_d$, surface tension $\gamma$, \VS{and acceleration due to gravity $g$} (figure~\ref{fig:schematic}a).
+Naturally, even the process of a Newtonian liquid drop impacting a rigid substrate is governed by a plethora of control parameters, including but not limited to the drop's density $\rho_d$, diameter $D_0$, velocity $V_0$, dynamic viscosity $\eta_d$, surface tension $\gamma$, and acceleration due to gravity $g$ (figure~\ref{fig:schematic}a).
 To navigate this rich landscape, we focus on two main dimensionless numbers that serve as control parameters (figure~\ref{fig:schematic}b): the Weber number $We$, which is the ratio of inertial to capillary forces and is given by
@@
 
-\noindent \VS{Additionally, the Bond number }
+\noindent Additionally, the Bond number
 
-\VS{\begin{align}
+\begin{align}
 	\label{Eq:BoDefinition}
 	Bo = \frac{\rho_dgD_0^2}{\gamma}
-\end{align}}
+\end{align}
 
-\noindent \VS{compares gravity to inertial forces and is needed to uniquely define the non-dimensional problem.}
+\noindent compares gravity to inertial forces and is needed to uniquely define the non-dimensional problem.
 
@@
 		\end{tabular}
-		\caption{\VS{Properties of the water-glycerol mixtures used in the experiments.
+		\caption{Properties of the water-glycerol mixtures used in the experiments.
 $\rho_d$ and $\eta_d$ are the density and viscosity of the drop, respectively and $\gamma$ denotes the liquid-air surface tension coefficient.
-These properties are calculated using the protocol provided in \citet{cheng2008formula, volk2018density}.}}
+These properties are calculated using the protocol provided in \citet{cheng2008formula, volk2018density}.}
 		\label{tab:table00}
@@
 In the experimental setup, shown schematically in figure~\ref{fig:schematic}(a), a liquid drop impacts a superhydrophobic substrate.
-\VS{For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}.
-On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}.}
-\VS{The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}.
+For water drops, such a surface is coated with silanized silica nanobeads with a diameter of $20\,\si{\nano\meter}$ (Glaco Mirror Coat Zero; Soft99) resulting in the advancing and receding contact angles of $167 \pm 2^{\circ}$ and $154 \pm 2^{\circ}$, respectively \citep{Gauthier2015, Li2017}.
+On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}.
+The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}.
 Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.
@@
 The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate.
-Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
+\red{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
 In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
@@
 The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$.
-\VS{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
-We refer the readers to the supplementary material of \citet{zhang2022impact} for further details of the experimental setup.}
+Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
+We refer the readers to the supplementary material of \citet{zhang2022impact} for further details of the experimental setup.
 
@@
 \noindent respectively.
-Here, $\boldsymbol{v}$ is the velocity field, $t$ is time, $p$ is pressure, \VS{and $\boldsymbol{g}$ is acceleration due to gravity}.
+Here, $\boldsymbol{v}$ is the velocity field, $t$ is time, $p$ is pressure, and $\boldsymbol{g}$ is acceleration due to gravity.
 We use the free software program \textit{Basilisk C} that employs the well-balanced geometric volume of fluid (VoF) method \citep{popinet2009accurate, popinet2018numerical}.
@@
 The substrate is modeled as a no-slip and non-penetrable wall, whereas vanishing stress and pressure are applied at the remaining boundaries to mimic outflow conditions for the surrounding air.
-\VS{The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case).
+The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case).
 At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$.
@@
 The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}.
-However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}
+However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.
 The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields. A minimum grid size $\Delta = D_0/2048$ is used for this study.
 
-\VS{To ensure a perfectly non-wetting surface, we impose a thin air layer (minimum thickness $\sim \Delta/2$) between the drop and the substrate.
+To ensure a perfectly non-wetting surface, we impose a thin air layer (minimum thickness $\sim \Delta/2$) between the drop and the substrate.
 This air layer prevents direct contact between the liquid and solid \citep{kolinski-2014-epl, sprittles2024gas}, effectively mimicking a perfectly non-wetting surface.
@@
 While this approach does not fully resolve the microscopic dynamics within the air layer itself, such as the high-velocity gradients and viscous dissipation inside the gas film once it thins below a critical size ($\sim 10\Delta$), it has been shown to accurately capture the macroscopic behavior of drop impact in the parameter range of interest \citep{ramirez2020lifting, sanjay2023drop, alventosa2023inertio, garcia2024skating}.
-We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, vatsal_sanjay_2023_7598181, zhang2022impact} for details on the numerical framework.}
+We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, vatsal_sanjay_2023_7598181, zhang2022impact} for details on the numerical framework.
 
@@
 \caption{Anatomy of the first impact force peak amplitude for viscous impacts from our numerical simulations: the $Oh$ dependence of  (a) the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ and (b) the time $t_1$ to reach the first force peak amplitude normalized by inertial timescale $\tau_\rho = D_0/V_0$.
-\VS{(c) The $Re$ dependence of the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ as compared to the (implicit) theoretical calculation of \citet{Gordillo2018}.} The black line corresponds to the scaling relationship described in \S\ref{sec:ViscousImpact}.
+(c) The $Re$ dependence of the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ as compared to the (implicit) theoretical calculation of \citet{Gordillo2018}.
+The black line corresponds to the scaling relationship described in \S\ref{sec:ViscousImpact}.
 The Weber number is color-coded.}
@@
 
-\VS{Figure~\ref{fig:F1Anatomy_2} further shows that these scaling laws are weakly dependent on the Weber number, as viscous dissipation consumes the entire initial kinetic energy of the impacting drop (figure~\ref{fig:QualitativeF1}).
+Figure~\ref{fig:F1Anatomy_2} further shows that these scaling laws are weakly dependent on the Weber number, as viscous dissipation consumes the entire initial kinetic energy of the impacting drop (figure~\ref{fig:QualitativeF1}).
 Once again, we stress that using the water-glycerol mixtures limits the range of $Oh$ that we can probe experimentally.
@@
 However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude.
-This lack of a pure scaling behavior demonstrates how the interplay between kinetic energy and viscous dissipation within the drop dictates the functional dependence of the maximum impact force on $Oh$.}
+This lack of a pure scaling behavior demonstrates how the interplay between kinetic energy and viscous dissipation within the drop dictates the functional dependence of the maximum impact force on $Oh$.
 
@@
 We can estimate $\Omega = D_{\text{foot}}^2l_\nu$ (figure~\ref{fig:QualitativeF1}), where $D_{\text{foot}}$ is the drop's foot diameter in contact with the substrate and $l_\nu$ is the viscous boundary layer thickness.
-\VS{This boundary layer marks the region of strong velocity gradients ($\sim V_0/l_\nu$) analogous to the \citet{mirels1955laminar} shockwave-induced boundary layer.
+This boundary layer marks the region of strong velocity gradients ($\sim V_0/l_\nu$) analogous to the \citet{mirels1955laminar} shockwave-induced boundary layer.
 For details, we refer the authors to \citet{schlichting2016boundary, Schroll2010, Philippi2016}.
-Consequently, the viscous dissipation rate scales as}
+Consequently, the viscous dissipation rate scales as
 
@@
 
-\VS{\begin{align}\label{eq:eps0Final}
+\begin{align}\label{eq:eps0Final}
 	\bar{\varepsilon} \sim \sqrt{\nu_d \tau_\rho}V_0^3/D_0^2, 
-\end{align}}
+\end{align}
 
-\noindent \VS{where $\tau_\rho$ is the inertial time scale.
+\noindent where $\tau_\rho$ is the inertial time scale.
 Here, we assume that for highly viscous drops, all energy is dissipated within a fraction of $\tau_\rho$.
-Filling in \eqref{eq:eps0Final} and normalizing $\bar{\varepsilon}$ with the inertial scales $V_0^3/D_0$,}
+Filling in \eqref{eq:eps0Final} and normalizing $\bar{\varepsilon}$ with the inertial scales $V_0^3/D_0$,
 
-\VS{\begin{align}\label{eq:DissipationScale}
+\begin{align}\label{eq:DissipationScale}
 	\frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \sqrt{\frac{\nu_d\tau_\rho}{D_0^2}} = \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}.
-\end{align}}
+\end{align}
 
@@
 
-\VS{\begin{align}
+\begin{align}
 	\label{Eq:viscIncrease}
 	\frac{F}{F_\rho} \sim \frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}
-\end{align}}
+\end{align}
 
@@
 
-\VS{\begin{align}
+\begin{align}
 	\label{Eq:viscTime}
 	\frac{t_1}{\tau_\rho} \sim \left(\frac{\sqrt{We}}{Oh}\right)^{1/2}.
-\end{align}}
+\end{align}
 
-\VS{In summary, we use energy and momentum invariance to elucidate the parameter dependencies of the impact force as illustrated in figure~\ref{fig:F1Anatomy_2}.
+In summary, we use energy and momentum invariance to elucidate the parameter dependencies of the impact force as illustrated in figure~\ref{fig:F1Anatomy_2}.
 The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces.
 As the dimensionless viscosity of impacting drops increases, the lack of surface deformation increases the normal reaction force \eqref{Eq:viscIncrease}.
-Further, the invariance of incoming drop momentum implies that this increase in normal reaction force occurs on a shorter timescale \eqref{Eq:viscTime}.}
+Further, the invariance of incoming drop momentum implies that this increase in normal reaction force occurs on a shorter timescale \eqref{Eq:viscTime}.
 
@@
 Lastly,  as $Oh$ increases, bulk dissipation becomes dominant (apparent from increasing $Oh$ at fixed $We$ in figure~\ref{fig:F2Phenomenology}) and can entirely inhibit drop bouncing.
-Recently, \citet{Jha2020, sanjay_chantelot_lohse_2023} showed that there \VS{exists a critical $Oh$, two orders of magnitude higher than that of a $2\si{\milli\meter}$ diameter water drop}, beyond which drops do not bounce either, irrespective of their impact velocity.
+Recently, \citet{Jha2020, sanjay_chantelot_lohse_2023} showed that there exists a critical $Oh$, two orders of magnitude higher than that of a $2\,\si{\milli\meter}$ diameter water drop, beyond which drops do not bounce either, irrespective of their impact velocity.
 Consequently, the second peak in the impact force diminishes for larger $Oh$, which explains the monotonic decrease of the amplitude $F_2$ observed in figure~\ref{fig:F2Anatomy} for $We > 30, Oh > 0.01$.
@@
 These regime maps are constructed using $\sim 1500$ simulations in the range $0.001 \leq Oh \leq 100$ and $1 \leq We \leq 1000$.
-\VS{The gray solid line in (a) and dashed line in (b) mark the inertial--viscous transition ($Re = 1$) and the bouncing--no-bouncing transition \citep[$Oh_c = 0.53$ for $Bo = 1$, see][]{sanjay_chantelot_lohse_2023}, respectively.}}
+The gray solid line in (a) and dashed line in (b) mark the inertial--viscous transition ($Re = 1$) and the bouncing--no-bouncing transition \citep[$Oh_c = 0.53$ for $Bo = 1$, see][]{sanjay_chantelot_lohse_2023}, respectively.}
 	\label{fig:RegimeMaps}
@@
 For instance, it would be interesting to use the energy accounting approach to unify the scaling laws for the maximum spreading diameter for arbitrary $Oh$ \citep{laan2014maximum, Wildeman2016}.
-\VS{Although, the implicit theoretical model summarized in \citet{cheng2021drop} describes most of data in figure~\ref{fig:F1Anatomy_2}, we stress the importance of having a predictive model to determine $F_1$ for given $We$ and $Oh$ \citep{sanjay2024PRL}.} The $We$ influence on the impact force also warrants further exploration, especially in the regime $We \ll 1$ for arbitrary $Oh$ \citep{chevy2012liquid, molavcek2012quasi} and drop impact on compliant surfaces \citep{alventosa_cimpeanu_harris_2023, ma2023scaling}.
+Although, the implicit theoretical model summarized in \citet{cheng2021drop} describes most of data in figure~\ref{fig:F1Anatomy_2}, we stress the importance of having a predictive model to determine $F_1$ for given $We$ and $Oh$ \citep{sanjay2024PRL}.
+The $We$ influence on the impact force also warrants further exploration, especially in the regime $We \ll 1$ for arbitrary $Oh$ \citep{chevy2012liquid, molavcek2012quasi} and drop impact on compliant surfaces \citep{alventosa_cimpeanu_harris_2023, ma2023scaling}.
 Another potential extension of this work is to non-Newtonian fluids \citep{martouzet2021dynamic, aguero2022impact, bertin2023similarity, jin2023marbles}.\\[5mm]

### 2024-07-26 Rebuttal.R2/Response to Reviewer 2.tex
refactor: Update response to reviewer feedback for resubmission
- Add droplet shape profile comparisons for new force datasets
- Request experimental images from Cunjing for Oh = 0.0625 and 0.2
- Consider adding error bars for parametric errors
- Clarify that Bond number is not fixed at 1 in the experimental methods

@@
 
-	\red{Yes, we can add these images. Will ask Cunjing to send them.}
+	\red{Please send me the experimental images for the two case: Oh = 0.0625 and 0.2. I think I have the videos already but not the raw images. Please send them.}
 
@@
 
-	\red{Will need Cunjing's help with the experimental setup details and error quantification.}
+	\red{Perhaps we add some numbers for the error bar here. Honestly, I think we already have the data needed for reproducing the results. We are not doing anything non-standard. Right?}
 
@@
 
-		\red{To discuss: The results are Bond invariant in the leading order.
+		\VS{To discuss: The results are Bond invariant in the leading order.
 Therefore, we chose a representative value of Bond = 1: this if for a diameter $0.00256\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, acceleration due to gravity $10\,\si{\meter/\second^2}$, surface tension $0.06\,\si{\newton/\meter}$.
@@
 
+		\VS{see above. I will take care of this comment - Vatsal}.
+
 		\item \textit{Given the significant amount of data overlap in the various figures (e.g.
@@
 
+		\VS{We have this data and I will make a jupyter notebook to include all this data}
+
 		\item \textit{The authors mention that their mixtures maintain ``a fairly constant surface tension and density, around 61 mN/m and 1000 kg/m$^3$, respectively.'' Since the values are now clearly specified in the table now, what is the meaning of these particular characteristic values which do in fact vary by around 20\%?}
+
+		\VS{We can rephrase to address this. I will take care.}
 	\end{itemize}
@@
 
-	\red{The first impact peak is independent of wetability. The second peak, of course, depends on wetability as it only shows up on non-wetting surfaces.}
+	\blue{The first impact peak is independent of wetability. The second peak, of course, depends on wetability as it only shows up on non-wetting surfaces. Any suggestions?}
 
@@
 
+	\red{What to do?
+There are other more detailed works on impact of non-sphericity.
+Mostly, they show that the things do not depend on whether the drop is prolate or oblate...
+At least not in the leading order.
+Also see: \citet{sanjay2023drop}.}
+
 	\item[$\bullet$] \textit{11. While moving to a different fluid is one viable option, using smaller radii could also allow for smaller $Oh$.}
 
-	\red{tbh: (not to be sent to reviewer) I thought that it was obvious.
+	\VS{tbh: (not to be sent to reviewer) I thought that it was obvious.
 If we decreased the $r$, we would get higher $Oh$ but not too much as $Oh$ depends weakly on $r$ ($1/\sqrt{r})$ whereas it depends linearly on $\eta$.
 Also, using silicone oil would require special surface which is perhaps more important to remember.
-}
+-- Detlef will take care of this.}
 
@@
 
-	\red{Easily fixed: we can submit the SL theory on arxiv before we resubmit this work. :)}
+	\VS{Easily fixed: we can submit the other work to arxiv before we resubmit this work. :) Or, remove the citation.}
 

### 2024-08-27 Main/ViscousDropImpact_v7.tex
feat: Update Figure1_summary_v6.pdf and ViscousDropImpact_v7.pdf
The changes involve updating the Figure1_summary.pdf file to version 6 and the ViscousDropImpact.pdf file to version 7. The key changes are:

1. In the Figure1_summary.pdf file, the figure caption has been updated to include more detailed information about the comparison of experimental and simulation results, including the specific parameter values for the three cases and the excellent agreement between the two without any free parameters.
2. The ViscousDropImpact.pdf file has been updated to version 7, but the changes are not s

@@
 \usepackage{xcolor}
-\newcommand{\VS}[1]{{\textcolor{orange}{#1}}}
-\newcommand{\red}[1]{{\textcolor{red}{#1}}}
+%\newcommand{\VS}[1]{{\textcolor{orange}{#1}}}
+%\newcommand{\red}[1]{{\textcolor{red}{#1}}}
+
+\usepackage[normalem]{ulem}
+\usepackage[textwidth=\dimexpr\textwidth-2cm\relax]{todonotes}
+\makeatletter
+\@mparswitchfalse%
+\makeatother
+\normalmarginpar %for right-handed notes and lines, or
+\newcommand{\Rev}[1]{\todo[color=orange, bordercolor=none, textcolor=white]{R2}\textcolor{magenta}{#1}}
+
+\newcommand{\oo}{\color{magenta} \normalfont}
+\newcommand{\bb}{\color{black} \normalfont}
+
+\newcommand{\vs}{\color{orange} \normalfont}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{Figures/Figure1_summary_v5.pdf}
-	\caption{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
+	\includegraphics[width=\textwidth]{Figures/Figure1_summary_v6.pdf}
+	\caption{{\vs Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
 These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
@@
 		The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity.
-The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.}
+The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.
+\bb}}
 \label{fig:summary}
@@
 The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate.
-\red{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
+\Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
 In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.

### 2024-08-27 Rebuttal.R2/Response to Reviewer 2.tex
feat(drop-impact): Improve drop shape initialization in simulations
The changes improve the initialization of the drop shape in the direct numerical simulations (DNS) of drop impact. Previously, the drop was initialized as a perfect sphere, which may not be the case in experiments where the drop can have residual oscillations as it is released from the needle. The new approach introduces an appendix that describes a more realistic drop shape initialization (see appendix~\ref{app:shape}). This change aims to better capture the influence of the drop shape on the impact dynamics, as previous stud

@@
 
+\newcommand{\oo}{\color{magenta} \normalfont}
+\newcommand{\bb}{\color{black} \normalfont}
+
+\newcommand{\vs}{\color{orange} \normalfont}
+
 \renewcommand{\thefigure}{R\arabic{figure}}
@@
 The referee's comments are in italics, and our replies are in plain black.
-Changes in the manuscript are highlighted in orange.
+Changes in the manuscript are highlighted in magenta.
 
@@
 Furthermore, these visualizations (including the one already included) should include a scale bar.
-Additionally, I would suggest including some experimental videos as supplementary materials.}
+Additionally, I would suggest including some experimental videos as supplementary materials.}\\[2mm]
 
-	\red{Please send me the experimental images for the two case: Oh = 0.0625 and 0.2. I think I have the videos already but not the raw images. Please send them.}
+	We have modified figure~2 of the main text (see figure~\ref{fig:summary}) to include direct visualization of the droplet dynamics. We have also added three supplementary videos: SM1-SM3.
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=\textwidth]{../Main/Figures/Figure1_summary_v6.pdf}
+		\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
+These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
+				For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
+				The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
+The black and gray dashed lines in panel (a) mark $F = 0$ and the resolution $F = 0.5\,\si{\milli\newton}$ of our piezoelectric force transducer, respectively.
+				(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), and (iv) $t = 4.63\,\si{\milli\second}$ ($t_2$).
+				The insets of panel (a) exemplify these four instances for the three representative cases illustrated here. The experimental snapshots are overlaid with the drop boundaries from simulations. 
+				We stress the excellent agreement between experiments and simulations without any free parameters.
+				The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity.
+The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.
+Also see supplementary videos SM1-SM3.\bb}}
+		\label{fig:summary}
+	\end{figure}
 
@@
 Given that there is no length limit, I would suggest the authors include all details in the present manuscript rather than referring to incomplete discussions in prior work.
-(Also a minor point: the new horizontal line associated with the force sensor resolution should be described in the caption.)}
+(Also a minor point: the new horizontal line associated with the force sensor resolution should be described in the caption.)}\\[2mm]
 
-	\red{Perhaps we add some numbers for the error bar here. Honestly, I think we already have the data needed for reproducing the results. We are not doing anything non-standard. Right?}
+	We appreciate the reviewer's insistence on a comprehensive error characterization.
+We have addressed this concern by adding a new appendix to the manuscript, titled ``Note on the experimental error characterization".
+We have also modified the caption of figure~2 of the main text (see figure~\ref{fig:summary}).
+
+	\oo
+	Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
+We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~B for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.
+
+	\section*{Appendix B. Note on the experimental error characterization}
+	\label{app:error}
+
+	This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
+	The drop diameter determination involved multiple steps.
+First, we measured the total mass ($M_{100}$) of 100 drops using an electric balance.
+From this mass, the drop density, and assuming spherical shape, we calculated the drop diameter ($D_0$).
+We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$.
+The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
+	For impact velocity determination, we extracted data from experimental high-speed imagery.
+By tracking the drop center's position in successive frames prior to substrate contact, and knowing the frame rate, we calculated the impact velocity.
+We repeated this process for five trials, obtaining $V_{0,1}$ through $V_{0,5}$.
+The average of these values gave the final impact velocity ($V_0$) and its standard error.
+
+	The standard errors for drop diameters did not exceed $0.13\,\si{\milli\meter}$.
+For drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$, the diameters were $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
+	The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.
+For the same Oh values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
+	The combined errors in $D_0$ and $V_0$ resulted in approximately $\pm 7\%$ error in Weber number $We$ and $\pm 3\%$ error in Ohnesorge number $Oh$.
+Consequently, the horizontal error bars, which relate to errors in the control parameters, are smaller than the symbol sizes in our figures.
+	\bb
 

### 2024-08-27 Main/ViscousDropImpact_v7.tex
feat(drop-impact): Improve drop shape initialization in simulations
The changes improve the initialization of the drop shape in the direct numerical simulations (DNS) of drop impact. Previously, the drop was initialized as a perfect sphere, which may not be the case in experiments where the drop can have residual oscillations as it is released from the needle. The new approach introduces an appendix that describes a more realistic drop shape initialization (see appendix~\ref{app:shape}). This change aims to better capture the influence of the drop shape on the impact dynamics, as previous stud

@@
 	\includegraphics[width=\textwidth]{Figures/Figure1_summary_v6.pdf}
-	\caption{{\vs Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
+	\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
 These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
 	For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
-		The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $t_3 \approx 0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
-		Six instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), (iv) $t = 3.93\,\si{\milli\second}$ ($\approx 0.85t_2$), (v) $t = 4.63\,\si{\milli\second}$ ($t_2$), and (vi) $t = 5.25\,\si{\milli\second}$ ($\approx 1.15t_2$).
+	The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
+The black and gray dashed lines in panel (a) mark $F = 0$ and the resolution $F = 0.5\,\si{\milli\newton}$ of our piezoelectric force transducer, respectively.
+	(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), and (iv) $t = 4.63\,\si{\milli\second}$ ($t_2$).
+	The insets of panel (a) exemplify these four instances for the three representative cases illustrated here. The experimental snapshots are overlaid with the drop boundaries from simulations. 
 	We stress the excellent agreement between experiments and simulations without any free parameters.
-The insets show representative snapshots at specific time instants overlaid with the drop boundaries from simulations in orange, also revealing good agreement.
 	The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity.
 The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.
-\bb}}
+Also see supplementary videos SM1-SM3.\bb}}
 \label{fig:summary}
@@
 In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
-Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia.}
+Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
 All experiments are conducted at ambient pressure and temperature.
@@
 The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$.
-Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
-We refer the readers to the supplementary material of \citet{zhang2022impact} for further details of the experimental setup.
+\Rev{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
+We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.}
 
@@
 The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case).
-At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$.
-It is important to note that the drops may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate.
-These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers.
-The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}.
-However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.
-The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields. A minimum grid size $\Delta = D_0/2048$ is used for this study.
+At $t = 0$, in our simulations, we release \Rev{a spherical drop (see appendix~\ref{app:shape})} whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$.
+The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields.
+A minimum grid size $\Delta = D_0/2048$ is used for this study.
 
@@
 
+\appendix
+\renewcommand{\thefigure}{\Alph{section}\,\arabic{figure}}
+\setcounter{figure}{0}
+
+\section{Role of gravity on drop impact forces}
+\label{app:gravity}
+
+\oo
+\section{Note on the parametric error characterization}
+\label{app:error}
+
+This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
+The drop diameter determination involved multiple steps.
+First, we measured the total mass ($M_{100}$) of 100 drops using an electric balance.
+From this mass, the drop density, and assuming spherical shape, we calculated the drop diameter ($D_0$).
+We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$.
+The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
+For impact velocity determination, we extracted data from experimental high-speed imagery.
+By tracking the drop center's position in successive frames prior to substrate contact, and knowing the frame rate, we calculated the impact velocity.
+We repeated this process for five trials, obtaining $V_{0,1}$ through $V_{0,5}$.
+The average of these values gave the final impact velocity ($V_0$) and its standard error.
+
+The standard errors for drop diameters did not exceed $0.13\,\si{\milli\meter}$.
+For drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$, the diameters were $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
+The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.
+For the same Oh values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
+The combined errors in $D_0$ and $V_0$ resulted in approximately $\pm 7\%$ error in Weber number $We$ and $\pm 3\%$ error in Ohnesorge number $Oh$.
+Consequently, the horizontal error bars, which relate to errors in the control parameters, are smaller than the symbol sizes in our figures.
+\bb
+
+\section{Role of drop shape on impact forces}
+\label{app:shape}
+
+It is important to note that the drops may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate.
+These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers.
+The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}.
+However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.
+
 \bibliographystyle{jfm}

### 2024-08-27 Rebuttal.R2/Response to Reviewer 2.tex
feat: Extend discussion on the role of gravity in drop impact
This commit extends the discussion on the role of gravity in drop impact. The
key changes are:

1. Added a new paragraph in Section 2 that discusses the Bond number (Bo) and
   Froude number (Fr) for the system, highlighting that gravity is sub-dominant
   compared to inertia throughout the manuscript (Fr > 1).
2. Removed the dedicated Appendix A on the role of gravity, as the key points
   are now incorporated in the main text.

The motivation for these changes is to provide a more comprehensive
understanding of the system's dimens

@@
 	Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
-We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~B for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.
+We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~A for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.
 
-	\section*{Appendix B. Note on the experimental error characterization}
+	\section*{Appendix A. Note on the experimental error characterization}
 	\label{app:error}

### 2024-08-27 Main/ViscousDropImpact_v7.tex
feat: Extend discussion on the role of gravity in drop impact
This commit extends the discussion on the role of gravity in drop impact. The
key changes are:

1. Added a new paragraph in Section 2 that discusses the Bond number (Bo) and
   Froude number (Fr) for the system, highlighting that gravity is sub-dominant
   compared to inertia throughout the manuscript (Fr > 1).
2. Removed the dedicated Appendix A on the role of gravity, as the key points
   are now incorporated in the main text.

The motivation for these changes is to provide a more comprehensive
understanding of the system's dimens

@@
 The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate.
-\Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
-In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
-Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
 All experiments are conducted at ambient pressure and temperature.
@@
 The Ohnesorge number based on air viscosity $Oh_a = \left(\eta_a/\eta_d\right)Oh$ and air-drop density ratio $\rho_a/\rho_d$ are fixed at $10^{-5}$ and $10^{-3}$, respectively to minimize the influence of the surrounding medium on the impact forces.
+\Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
+In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
+Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
 The substrate is modeled as a no-slip and non-penetrable wall, whereas vanishing stress and pressure are applied at the remaining boundaries to mimic outflow conditions for the surrounding air.
@@
 
-\section{Role of gravity on drop impact forces}
-\label{app:gravity}
-
 \oo
@@
 
+\section{Role of gravity on drop impact forces}
+\label{app:gravity}
+
 \section{Role of drop shape on impact forces}

### 2024-08-27 Rebuttal.R2/Response to Reviewer 2.tex
feat: Update Force2_Anatomy_v4.pdf and respond to Reviewer 2
The changes made in this commit include:

1. Update the metadata of the Force2_Anatomy_v4.pdf file, including the "xmptk" and "Length" values.
2. Update the contents of the Force2_Anatomy_v4.pdf file, specifically removing several PDF objects that are no longer needed.
3. Add a new PDF file, "Rebuttal.R2/Response to Reviewer 2.pdf", which likely contains the response to the comments from Reviewer 2.

These changes were made to address feedback from Reviewer 2 and to optimize the PDF file for the project.

@@
 
-		\VS{see above. I will take care of this comment - Vatsal}.
-
 		\item \textit{Given the significant amount of data overlap in the various figures (e.g.
-Figure 3(b)), I am more convinced now that the parameters and raw data need to be provided in a supplementary dataset for reproducibility and to facilitate further comparisons.}
-
-		\VS{We have this data and I will make a jupyter notebook to include all this data}
+Figure 3(b)), I am more convinced now that the parameters and raw data need to be provided in a supplementary dataset for reproducibility and to facilitate further comparisons.}\\[2mm]
 
@@
 
-	\VS{tbh: (not to be sent to reviewer) I thought that it was obvious.
-If we decreased the $r$, we would get higher $Oh$ but not too much as $Oh$ depends weakly on $r$ ($1/\sqrt{r})$ whereas it depends linearly on $\eta$.
-Also, using silicone oil would require special surface which is perhaps more important to remember.
--- Detlef will take care of this.}
-
-	Using smaller radii could also allow for larger $Oh$. We have added this in the revised manuscript.
+	Yes, using smaller radii could also allow for larger $Oh$. We have added this in the revised manuscript.
 
@@
 
-	\VS{Easily fixed: we can submit the other work to arxiv before we resubmit this work. :) Or, remove the citation.}
+	We now cite the accessible version of this work:
 

### 2024-08-27 Main/ViscousDropImpact_v7.tex
feat: Update Force2_Anatomy_v4.pdf and respond to Reviewer 2
The changes made in this commit include:

1. Update the metadata of the Force2_Anatomy_v4.pdf file, including the "xmptk" and "Length" values.
2. Update the contents of the Force2_Anatomy_v4.pdf file, specifically removing several PDF objects that are no longer needed.
3. Add a new PDF file, "Rebuttal.R2/Response to Reviewer 2.pdf", which likely contains the response to the comments from Reviewer 2.

These changes were made to address feedback from Reviewer 2 and to optimize the PDF file for the project.

@@
 Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.
-The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle.
-Throughout this work, we use drops with diameter $2.54 \pm 0.02\,\si{\milli\meter}$ unless otherwise stated.
+The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle \oo (see appendix~\ref{app:error} for details).\bb\,
 Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~\eqref{Eq:OhDefinition}).
@@
 This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
-The drop diameter determination involved multiple steps.
-First, we measured the total mass ($M_{100}$) of 100 drops using an electric balance.
-From this mass, the drop density, and assuming spherical shape, we calculated the drop diameter ($D_0$).
-We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$.
-The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
+The drop diameter determination involves multiple steps.
+First, we measure the total mass ($M_{100}$) of 100 drops using an electric balance.
+From this mass, using the liquid density and assuming spherical shape, we calculated the drop diameter ($D_0$).
+We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$. The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
 For impact velocity determination, we extracted data from experimental high-speed imagery.
@@
 
-The standard errors for drop diameters did not exceed $0.13\,\si{\milli\meter}$.
-For drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$, the diameters were $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
+The standard errors for drop diameters do not exceed $0.13\,\si{\milli\meter}$.
+For instance, drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
 The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.

### 2024-08-28 Rebuttal.R2/Response to Reviewer 2.tex
feat: Expand drop property details and Ohnesorge number calculation
The changes in this commit focus on providing more details about the properties of the impacting drops and the calculation of the Ohnesorge number (Oh). Specifically:

- The properties of the water-glycerol mixtures used as the impacting drops are expanded, including the range of viscosities, surface tensions, and densities.
- It is noted that using other liquids like silicone oil could provide a broader range of viscosity variation when paired with a superamphiphobic substrate.
- The method for controlling the drop diameter a

@@
 	\label{app:error}
-
 	This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
-	The drop diameter determination involved multiple steps.
-First, we measured the total mass ($M_{100}$) of 100 drops using an electric balance.
-From this mass, the drop density, and assuming spherical shape, we calculated the drop diameter ($D_0$).
-We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$.
-The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
+	The drop diameter determination involves multiple steps.
+First, we measure the total mass ($M_{100}$) of 100 drops using an electric balance.
+From this mass, using the liquid density and assuming spherical shape, we calculated the drop diameter ($D_0$).
+	We repeated this process five times, yielding $D_{0,1}$ through $D_{0,5}$. The average of these measurements provided the final drop diameter ($D_0$) and its standard error.
 	For impact velocity determination, we extracted data from experimental high-speed imagery.
@@
 
-	The standard errors for drop diameters did not exceed $0.13\,\si{\milli\meter}$.
-For drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$, the diameters were $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
+	The standard errors for drop diameters do not exceed $0.13\,\si{\milli\meter}$.
+For instance, drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
 	The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.
@@
 
-		\VS{To discuss: The results are Bond invariant in the leading order.
-Therefore, we chose a representative value of Bond = 1: this if for a diameter $0.00256\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, acceleration due to gravity $10\,\si{\meter/\second^2}$, surface tension $0.06\,\si{\newton/\meter}$.
-The dimensionless number that matter is the Froude number $Fr = V^2/gD_0 = We/Bo$ which is larger than 1 throughout the paper.
-The difference as compared to \citet{zhang2022impact} is in the length scale (2 mm in PRL and 2.56 mm in this work).}
-
 		\item \textit{By now providing the drop size used, the Oh and Bo now can be used to define the parameters.
@@
 
-		\item \textit{The authors mention that their mixtures maintain ``a fairly constant surface tension and density, around 61 mN/m and 1000 kg/m$^3$, respectively.'' Since the values are now clearly specified in the table now, what is the meaning of these particular characteristic values which do in fact vary by around 20\%?}
+		Drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
+We share reviewer's assertion that it would be a great idea to share all the experimental data.
+We have revised our GitHub repository to include this information.
+We will make it available using Zenodo.
 
-		\VS{We can rephrase to address this. I will take care.}
+		\item \textit{The authors mention that their mixtures maintain ``a fairly constant surface tension and density, around 61 mN/m and 1000 kg/m$^3$, respectively.'' Since the values are now clearly specified in the table now, what is the meaning of these particular characteristic values which do in fact vary by around 20\%?}\\[2mm]
+
+		We thank the reviewer for bringing this to our attention and acknowledge that our original statement could be more precise
+		To address this concern, we have revised the text to provide a more accurate description of the property variations:
+
+		\S~\red{2.1:}\\
+		\oo
+		The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$.
+Surface tension is either $72,\si{\milli\newton}/\si{\meter}$ (pure water) or $61,\si{\milli\newton}/\si{\meter}$ (glycerol), while density $\rho_d$ ranges from $1000,\si{\kilo\gram}/\si{\cubic\meter}$ to $1220,\si{\kilo\gram}/\si{\cubic\meter}$, as detailed in table~1 \citep{cheng2008formula, volk2018density, Jha2020}.
+		\bb
 	\end{itemize}
@@
 	\S~\red{2.1:}\\
-	\VS{We note that using liquids such as silicone oil can provide a broader range of viscosity variation when paired with a superamphiphobic substrate \citep{deng2012candle}.
-Additionally, employing drops of smaller radii facilitates the exploration of higher Ohnesorge numbers ($Oh$).}
+	\oo 
+	We note that using liquids such as silicone oil can provide a broader range of viscosity variation when paired with a superamphiphobic substrate \citep{deng2012candle}.
+Additionally, employing drops of smaller radii facilitates the exploration of higher Ohnesorge numbers ($Oh$, see~1.2).
+	The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle (see appendix~A for details). 
+	Consequently, we calculate $Oh$ using the properties in table~1.\bb
 
@@
 
-	We now cite the accessible version of this work:
+	We now cite the accessible version of this work: \citet{sanjay2024PRL}.
 

### 2024-08-28 Main/ViscousDropImpact_v7.tex
feat: Expand drop property details and Ohnesorge number calculation
The changes in this commit focus on providing more details about the properties of the impacting drops and the calculation of the Ohnesorge number (Oh). Specifically:

- The properties of the water-glycerol mixtures used as the impacting drops are expanded, including the range of viscosities, surface tensions, and densities.
- It is noted that using other liquids like silicone oil could provide a broader range of viscosity variation when paired with a superamphiphobic substrate.
- The method for controlling the drop diameter a

@@
 Lett.}, vol.
-129, 2022, 104501) revealed two peaks in the temporal evolution of the normal force $F(t)$--one at impact and another at jump-off.
+129, 2022, 104501) revealed two peaks in the temporal evolution of the normal force $F(t)$ -- one at impact and another at jump-off.
 The second peak coincides with a Worthington jet formation, which vanishes at high viscosities due to increased viscous dissipation affecting flow focusing.
@@
 On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}.
-The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$, yet maintaining a fairly constant surface tension $\gamma$ and density $\rho_d$ around $61\,\si{\milli\newton}/\si{\meter}$ and $1000\,\si{\kilo\gram}/\si{\cubic\meter}$, respectively \citep{cheng2008formula, volk2018density, Jha2020}.
-Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.
-The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle \oo (see appendix~\ref{app:error} for details).\bb\,
-Consequently, changing the viscosity of the drop determines the Ohnesorge number ($Oh$, see~\eqref{Eq:OhDefinition}).
+\Rev{The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$.
+Surface tension is either $72,\si{\milli\newton}/\si{\meter}$ (pure water) or $61,\si{\milli\newton}/\si{\meter}$ (glycerol), while density $\rho_d$ ranges from $1000,\si{\kilo\gram}/\si{\cubic\meter}$ to $1220,\si{\kilo\gram}/\si{\cubic\meter}$, as detailed in table~\ref{tab:table00} \citep{cheng2008formula, volk2018density, Jha2020}.
+We note that using liquids such as silicone oil can provide a broader range of viscosity variation when paired with a superamphiphobic substrate \citep{deng2012candle}.
+Additionally, employing drops of smaller radii facilitates the exploration of higher Ohnesorge numbers ($Oh$, see~\eqref{Eq:OhDefinition}).
+The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle (see appendix~\ref{app:error} for details). 
+Consequently, we calculate $Oh$ using the properties in table~\ref{tab:table00}.} 
 The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate.
@@
 Figure~\ref{fig:F2Phenomenology} exemplifies this jet in the $Oh-We$ parameter space, which is intricately related to the second peak in the drop impact force.
-For low $Oh$ and large $We$, the drop retraction follows a modified Taylor-Culick dynamics \citep{bartolo2005retraction, Eggers2010, sanjay-2022-arxiv}.
+For low $Oh$ and large $We$, the drop retraction follows a modified Taylor-Culick dynamics \citep{bartolo2005retraction, Eggers2010, sanjay2022TC}.
 As $We$ is increased, the jet gets thinner but faster, maintaining a constant momentum flux $\rho_dV_j^2d_j^2$, where $V_j$ and $d_j$ are the jet's velocity and diameter, respectively \citep[figure~\ref{fig:F2Phenomenology},][]{zhang2022impact}.
@@
 
+The results are Bond invariant in the leading order.
+Therefore, we chose a representative value of Bond = 1: this if for a diameter $0.00256\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, acceleration due to gravity $10\,\si{\meter/\second^2}$, surface tension $0.06\,\si{\newton/\meter}$.
+The dimensionless number that matter is the Froude number $Fr = V^2/gD_0 = We/Bo$ which is larger than 1 throughout the paper.
+The difference as compared to \citet{zhang2022impact} is in the length scale (2 mm in PRL and 2.56 mm in this work).
+
 \section{Role of drop shape on impact forces}

### 2024-08-28 Main/ViscousDropImpact_v7.tex
feat: Explain the second impact force peak in the drop impact dynamics
Provide a detailed explanation for the formation mechanism of the second impact
force peak observed in drop impact experiments and numerical simulations. The
key points are:

- The second peak is also driven by momentum conservation as the drop takes off
  the surface, coinciding with the formation of a Worthington jet.
- The time at which the second peak occurs scales with the inertio-capillary
  timescale and is insensitive to the Weber and Ohnesorge numbers.
- For low Ohnesorge and high Weber numbers, the drop retraction

@@
 This axial symmetry breaks at large $We$ ($\ge 100$ for water drops and even larger Weber number for more viscous drops), owing to destabilization by the surrounding gas after splashing \citep{xu2005drop, Eggers2010, Driscoll2011, riboux2014experiments, Josserand2016, zhang2022impact}.
-To solve the governing equations~\eqref{eqn:continuity}--\eqref{eqn:VoF}, the velocity field $\boldsymbol{v}$ and time $t$ are normalized by the inertio-capillary scales, $V_\gamma = \sqrt{\gamma/\rho_dD_0}$ and $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$, respectively.
+To solve the governing equations~\eqref{eqn:continuity}-\eqref{eqn:VoF}, the velocity field $\boldsymbol{v}$ and time $t$ are normalized by the inertio-capillary scales, $V_\gamma = \sqrt{\gamma/\rho_dD_0}$ and $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$, respectively.
 Furthermore, the pressure is normalized using the capillary pressure scale $p_\gamma = \gamma/D_0$.
@@
 At the time instant $t_2 \approx 0.44\tau_\gamma$, the drop's internal motion undergoes a transition from a predominantly radial flow to a vertical one due to the formation of the Worthington jet \citep{chantelot2018rebonds, zhang2022impact}.
-Figure~\ref{fig:F2Phenomenology} exemplifies this jet in the $Oh-We$ parameter space, which is intricately related to the second peak in the drop impact force.
+Figure~\ref{fig:F2Phenomenology} exemplifies this jet in the $Oh$-$We$ parameter space, which is intricately related to the second peak in the drop impact force.
 For low $Oh$ and large $We$, the drop retraction follows a modified Taylor-Culick dynamics \citep{bartolo2005retraction, Eggers2010, sanjay2022TC}.
@@
 
-However, this singular jet regime is very narrow in the $Oh-We$ phase space.
+However, this singular jet regime is very narrow in the $Oh$-$We$ phase space.
 Figure~\ref{fig:KillSingularity}b shows two cases for water drops ($Oh = 0.0025$) at different $We$ ($5$ and $12$ for figures~\ref{fig:KillSingularity}b-i and b-ii, respectively).
@@
 
-For the first impact force peak amplitude $F_1$, owing to the momentum balance after the inertial shock at impact, figure~\ref{fig:RegimeMaps}(a) summarizes the different regimes in the $Oh--We$ phase space.
+For the first impact force peak amplitude $F_1$, owing to the momentum balance after the inertial shock at impact, figure~\ref{fig:RegimeMaps}(a) summarizes the different regimes in the $Oh$-$We$ phase space.
 For low $Oh$, inertial forces predominantly dictate the impact dynamics, such that $F_1$ scales with the inertial force $F_\rho$ \citep{Philippi2016, Gordillo2018, Mitchell2019, cheng2021drop, zhang2022impact} and is insensitive to viscosity variations up to 100-fold.
@@
 In contrast, capillary forces dominate at low $We$ and low $Oh$, leading to a force amplitude scaling of $F_2 \sim F_\gamma$.
-We also identify a narrow regime in the $Oh--We$ phase space where a singular Worthington jet forms, significantly increasing $F_2$ \citep{Bartolo2006Singular, zhang2022impact}, localized in the parameter space for $We \approx 9$ and $Oh < 0.01$.
+We also identify a narrow regime in the $Oh$-$We$ phase space where a singular Worthington jet forms, significantly increasing $F_2$ \citep{Bartolo2006Singular, zhang2022impact}, localized in the parameter space for $We \approx 9$ and $Oh < 0.01$.
 As $Oh$ increases, bulk viscous dissipation counteracts this jet formation, diminishing the second peak and ultimately inhibiting drop bouncing.
 
-Our findings have far-reaching implications, not only enriching the fundamental understanding of fluid dynamics of drop impact but also informing practical applications in diverse fields such as inkjet printing, public health, agriculture, and material science where the entire range of $Oh-We$ phase space is relevant (figures~\ref{fig:schematic}b and~\ref{fig:RegimeMaps}).
+Our findings have far-reaching implications, not only enriching the fundamental understanding of fluid dynamics of drop impact but also informing practical applications in diverse fields such as inkjet printing, public health, agriculture, and material science where the entire range of $Oh$-$We$ phase space is relevant (figures~\ref{fig:schematic}b and~\ref{fig:RegimeMaps}).
 While this has identified new scaling laws, it also opens avenues for future research.

### 2024-08-28 Rebuttal.R2/Response to Reviewer 2.tex
feat: Update title to highlight non-wetting surface assumption
The title has been updated to more accurately reflect the specific surface wettability assumption used in the study. While the first impact peak is independent of wettability, the second peak is dependent on the non-wetting nature of the substrate. This change ensures the title provides clear information about the experimental conditions to the reader.

Additionally, the manuscript has been updated to better quantify the non-sphericity of the droplets prior to impact, addressing the reviewer's concern about the potential impact of

@@
 Furthermore, these visualizations (including the one already included) should include a scale bar.
-Additionally, I would suggest including some experimental videos as supplementary materials.}\\[2mm]
+Additionally, I would suggest including some experimental videos as supplementary materials.}\\[1mm]
 
@@
 Given that there is no length limit, I would suggest the authors include all details in the present manuscript rather than referring to incomplete discussions in prior work.
-(Also a minor point: the new horizontal line associated with the force sensor resolution should be described in the caption.)}\\[2mm]
+(Also a minor point: the new horizontal line associated with the force sensor resolution should be described in the caption.)}\\[1mm]
 
@@
 		\item \textit{Given the significant amount of data overlap in the various figures (e.g.
-Figure 3(b)), I am more convinced now that the parameters and raw data need to be provided in a supplementary dataset for reproducibility and to facilitate further comparisons.}\\[2mm]
+Figure 3(b)), I am more convinced now that the parameters and raw data need to be provided in a supplementary dataset for reproducibility and to facilitate further comparisons.}\\[1mm]
 
@@
 
-		\item \textit{The authors mention that their mixtures maintain ``a fairly constant surface tension and density, around 61 mN/m and 1000 kg/m$^3$, respectively.'' Since the values are now clearly specified in the table now, what is the meaning of these particular characteristic values which do in fact vary by around 20\%?}\\[2mm]
+		\item \textit{The authors mention that their mixtures maintain ``a fairly constant surface tension and density, around 61 mN/m and 1000 kg/m$^3$, respectively.'' Since the values are now clearly specified in the table now, what is the meaning of these particular characteristic values which do in fact vary by around 20\%?}\\[1mm]
 
@@
 
-	\blue{The first impact peak is independent of wetability. The second peak, of course, depends on wetability as it only shows up on non-wetting surfaces. Any suggestions?}
+	We appreciate the reviewer's suggestion regarding the title.
+While we understand the importance of highlighting specific assumptions, we believe the current title strikes an appropriate balance between conciseness and informativeness.
+Nevertheless, we would like to address the reviewer's concern by elaborating on our reasoning:
+
+	\begin{enumerate}
+		\item \textbf{Generality of the first impact peak:} As demonstrated in the supplementary information of \citet{zhang2022impact}, the first impact peak is independent of surface wettability. 
+		\item \textbf{Early disclosure of surface properties:} We explicitly mention the non-wetting nature of the surface in the second line of the abstract.
+This ensures that readers are immediately aware of this crucial experimental condition without overburdening the title.
+	\end{enumerate}
+
+	We acknowledge that the second peak is indeed dependent on surface wettability.
+However, this specific aspect is thoroughly discussed within the paper, and we believe it does not warrant inclusion in the title.
 
@@
 If the experiment is repeatable, for a given drop height, the oscillation phase at which the droplet arrives at the surface should not vary, and thus is unlikely to be captured by the error bars as claimed.
-Some additional quantification of the non-sphericity of the droplets should be included.}
+Some additional quantification of the non-sphericity of the droplets should be included.}\\[1 mm]
 
-	\red{What to do?
-There are other more detailed works on impact of non-sphericity.
-Mostly, they show that the things do not depend on whether the drop is prolate or oblate...
-At least not in the leading order.
-Also see: \citet{sanjay2023drop}.}
+	The reviewer is correct that for a given drop height, the oscillation phase should be consistent if all other factors remain constant.
+In our experiments, we constrain our analysis to drops with aspect ratios (horizontal to vertical diameter) between 0.96 and 1.05.
+Given this narrow range, we posit that the impact of these shape variations is negligible compared to the experimental error bars derived from repeated trials under identical nominal conditions.
+We have modified the text to address this point and provide additional quantification of the non-sphericity of the droplets as suggested by the reviewer:
+
+	\S~\red{2.2:}\\
+	\oo
+	It is important to note that experimental drops may deviate from perfect sphericity due to air drag post-needle release and potential residual oscillations from detachment.
+These shape perturbations are more pronounced in cases with low Weber and Ohnesorge numbers.
+To quantify this non-sphericity, we measure the drop's aspect ratio (horizontal to vertical diameter) immediately before substrate contact.
+The precise pre-impact drop shape can significantly influence subsequent impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing,Zhang2019}.
+In our experiments, we constrain our analysis to drops with aspect ratios between 0.96 and 1.05.
+Given this narrow range, we posit that the impact of these shape variations is negligible compared to the experimental error bars derived from repeated trials under identical nominal conditions.
+	\bb
 

### 2024-08-28 Main/ViscousDropImpact_v7.tex
feat: Update title to highlight non-wetting surface assumption
The title has been updated to more accurately reflect the specific surface wettability assumption used in the study. While the first impact peak is independent of wettability, the second peak is dependent on the non-wetting nature of the substrate. This change ensures the title provides clear information about the experimental conditions to the reader.

Additionally, the manuscript has been updated to better quantify the non-sphericity of the droplets prior to impact, addressing the reviewer's concern about the potential impact of

@@
 The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case).
-At $t = 0$, in our simulations, we release \Rev{a spherical drop (see appendix~\ref{app:shape})} whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$.
-The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields.
-A minimum grid size $\Delta = D_0/2048$ is used for this study.
+At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. 
+\Rev{It is important to note that experimental drops may deviate from perfect sphericity due to air drag post-needle release and potential residual oscillations from detachment.
+These shape perturbations are more pronounced in cases with low Weber and Ohnesorge numbers.
+To quantify this non-sphericity, we measure the drop's aspect ratio (horizontal to vertical diameter) immediately before substrate contact.
+The precise pre-impact drop shape can significantly influence subsequent impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing,Zhang2019}.
+In our experiments, we constrain our analysis to drops with aspect ratios between 0.96 and 1.05.
+Given this narrow range, we posit that the impact of these shape variations is negligible compared to the experimental error bars derived from repeated trials under identical nominal conditions.}
+The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields. A minimum grid size $\Delta = D_0/2048$ is used for this study.
 
@@
 
-\section{Role of drop shape on impact forces}
-\label{app:shape}
-
-It is important to note that the drops may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate.
-These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers.
-The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}.
-However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.
-
 \bibliographystyle{jfm}

### 2024-08-28 Rebuttal.R2/Response to Reviewer 2.tex

@@
 
+	\S~\red{2.1:}\\
 	\oo
@@
 (2022)), it is mentioned that the Bo is fixed at 0.5 in simulation for similar experimental parameters.
-Why the change?}
+Why the change?}\\[1mm]
+
+		We appreciate the reviewer's comment regarding the Bond number. 
+		The reviewer is correct in pointing out the inconsistency, and we apologize for any confusion this may have caused. We would like to clarify and expand on this point:
+
+		\begin{enumerate}
+			\item \textbf{Experimental Bond number range:}
+			Indeed, given the variation in fluid properties and drop sizes used in our experiments, the Bond number is not strictly fixed at 1. 
+			\item \textbf{Simulation Bond number:}
+			In our simulations, we chose to use a fixed Bond number of 1 as a representative value.
+This choice was made to simplify the parameter space and focus on the effects of Weber and Ohnesorge numbers.
+We have added a new appendix (Appendix B) to address this point and demonstrate the validity of this approach.
+We have also expanded our discussion in Appendix B to justify our approach and discuss its implications.
+			\item \textbf{Difference from previous work:}
+			The reviewer correctly notes that in our previous work \citep{zhang2022impact}, we used a fixed Bond number of 0.5 in simulations.
+The change to Bo = 1 in the current work was made to better represent the average experimental conditions.
+However, as our sensitivity analysis shows, this change does not significantly affect our results or conclusions.
+		\end{enumerate}
+
+		\S~\red{2.2:}\\
+		\oo
+		Lastly, we keep the Bond number ($Bo$, see~(1.3)) fixed at 1 throughout the manuscript.
+In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
+Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~B).
+		\bb
+
+		\begin{figure}
+			\centering
+			\includegraphics[width=\textwidth]{../main/Figures/figureA1.pdf}
+			\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from simulations for the four different Bond numbers $Bo = 0, 0.5, 1, 1.25$.
+Here, $Oh = 0.06$ and $We = 40$.
+Both force peaks $F_1$ and $F_2$ as well as time to reach these peaks $t_1$ and $t_2$ are invariant to variation in $Bo$.
+\bb}}
+			\label{fig:AppGravity}
+		\end{figure}
+
+		\oo
+
+		\section*{Appendix B. Role of gravity on drop impact forces}
+		\label{app:gravity}
+
+		Following table~1 and considering the variation in impacting drop diameter (appendix~B), the Bond number (equation~(1.3)) in our experiments ranges from $0.5$ to $1.25$, introducing an additional dimensionless control parameter alongside $We$ and $Oh$.
+		Gravity typically plays a negligible role in these impact processes \citep{sanjay_chantelot_lohse_2023,sanjay2024PRL}.
+We undertook a sensitivity test varying the Bond number from $0$ to $1.25$ in our simulations.
+		Figure~\ref{fig:AppGravity} confirms the leading-order Bond invariance of the results as the impact force profiles, including both force peaks $F_1$ and $F_2$ and their corresponding times $t_1$ and $t_2$, remain invariant to these Bond number variations.
+		Notably, while gravity does play a role in drop impact dynamics, particularly for longer time scales and in determining the critical Ohnesorge number $Oh_c$ for bouncing inhibition (see figure~10b and \citet{sanjay_chantelot_lohse_2023}), its effect on the initial impact force peaks is minimal for the parameter range studied here (large Froude numbers, $Fr > 1$).
+This Bond number invariance allows us to focus on the more dominant effects of Weber and Ohnesorge numbers.
+		Consequently, we selected a representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.
+		\bb
 
@@
 
-		Drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
-We share reviewer's assertion that it would be a great idea to share all the experimental data.
+		We appreciate the reviewer's suggestion to clarify all the experimental data, and we have taken steps to address this.
+In our experiments, drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
+We have now added a discussion in the new appendix, titled ``Note on the experimental error characterization".
+		We also share reviewer's assertion that it would be a great idea to share all the experimental data.
 We have revised our GitHub repository to include this information.
-We will make it available using Zenodo.
+We have made it available using Zenodo, see \citet{basiliskVatsal}.
+
+		\oo
+		\noindent{\bf  Code availability\bf{.}} The codes used in the present article and the parameters and data to reproduce figures~3 and~7 are permanently available at \citet{basiliskVatsal}.\\
+		\bb
 
@@
 
-		We thank the reviewer for bringing this to our attention and acknowledge that our original statement could be more precise
+		We thank the reviewer for bringing this to our attention and acknowledge that our original statement needed improvement.
 		To address this concern, we have revised the text to provide a more accurate description of the property variations:
@@
 	\oo
-	It is important to note that experimental drops may deviate from perfect sphericity due to air drag post-needle release and potential residual oscillations from detachment.
+	It is important to note that experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
 These shape perturbations are more pronounced in cases with low Weber and Ohnesorge numbers.

### 2024-08-28 Main/ViscousDropImpact_v7.tex

@@
 The second peak coincides with a Worthington jet formation, which vanishes at high viscosities due to increased viscous dissipation affecting flow focusing.
-In this article, using experiments, direct numerical simulations, and scaling arguments, we characterize both the peak amplitude $F_1$ at impact and the one at take off ($F_2$) and elucidate their dependency on the control parameters: the Weber number $We$ (dimensionless impact velocity) and the Ohnesorge number $Oh$ (dimensionless viscosity).
+In this article, using experiments, direct numerical simulations, and scaling arguments, we characterize both the peak amplitude $F_1$ at impact and the one at take off ($F_2$) and elucidate their dependency on the control parameters: the Weber number $We$ (dimensionless impact kinetic energy) and the Ohnesorge number $Oh$ (dimensionless viscosity).
 The first peak amplitude $F_1$ and the time $t_1$ to reach it depend on inertial timescales for low viscosity liquids, remaining nearly constant for viscosities up to 100 times that of water.
@@
 The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case).
-(b) The phase space with control parameters: the Weber number ($We$: dimensionless impact velocity) and the Ohnesorge number ($Oh$: dimensionless viscosity), exemplifying different applications.}
+(b) The phase space with control parameters: the Weber number ($We$: dimensionless kinetic energy) and the Ohnesorge number ($Oh$: dimensionless viscosity), exemplifying different applications.}
 	\label{fig:schematic}
@@
 	\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
-These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
+These parameter give $Oh = 0.0025, 0.06, 0.2$ and $We = 40$.
 	For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
@@
 At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. 
-\Rev{It is important to note that experimental drops may deviate from perfect sphericity due to air drag post-needle release and potential residual oscillations from detachment.
+\Rev{It is important to note that experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
 These shape perturbations are more pronounced in cases with low Weber and Ohnesorge numbers.
@@
 While this approach does not fully resolve the microscopic dynamics within the air layer itself, such as the high-velocity gradients and viscous dissipation inside the gas film once it thins below a critical size ($\sim 10\Delta$), it has been shown to accurately capture the macroscopic behavior of drop impact in the parameter range of interest \citep{ramirez2020lifting, sanjay2023drop, alventosa2023inertio, garcia2024skating}.
-We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, vatsal_sanjay_2023_7598181, zhang2022impact} for details on the numerical framework.
+We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, basiliskVatsal, zhang2022impact} for details on the numerical framework.
 
@@
 In this work, we study the forces and dissipation encountered during the drop impact process by employing experiments, numerical simulations, and theoretical scaling laws.
-We vary the two dimensionless control parameters--the Weber ($We$: dimensionless impact velocity) and the Ohnesorge number ($Oh$: dimensionless viscosity) independently to elucidate the intricate interplay between inertia, viscosity, and surface tension in governing the forces exerted by a liquid drop upon impact on a non-wetting substrate.
+We vary the two dimensionless control parameters--the Weber ($We$: dimensionless impact kinetic energy) and the Ohnesorge number ($Oh$: dimensionless viscosity) independently to elucidate the intricate interplay between inertia, viscosity, and surface tension in governing the forces exerted by a liquid drop upon impact on a non-wetting substrate.
 
@@
 
-\noindent{\bf  Code availability\bf{.}} The codes used in the present article are permanently available at \citet{vatsal_sanjay_2023_7598181}.\\
+\noindent{\bf  Code availability\bf{.}} The codes used in the present article, and the parameters and data to reproduce figures~\ref{fig:F1Anatomy} and~\ref{fig:F2Anatomy} are permanently available at \citet{basiliskVatsal}.\\
 
@@
 The standard errors for drop diameters do not exceed $0.13\,\si{\milli\meter}$.
-For instance, drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
+For instance, drops with Ohnesorge numbers of $0.0025$, $0.06$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
 The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{Figures/figureA1.pdf}
+	\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from simulations for the four different Bond numbers $Bo = 0, 0.5, 1, 1.25$.
+Here, $Oh = 0.06$ and $We = 40$.
+Both force peaks $F_1$ and $F_2$ as well as time to reach these peaks $t_1$ and $t_2$ are invariant to variation in $Bo$.
+\bb}}
+	\label{fig:AppGravity}
+\end{figure}
+
+\oo
+
 \section{Role of gravity on drop impact forces}
@@
 
-The results are Bond invariant in the leading order.
-Therefore, we chose a representative value of Bond = 1: this if for a diameter $0.00256\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, acceleration due to gravity $10\,\si{\meter/\second^2}$, surface tension $0.06\,\si{\newton/\meter}$.
-The dimensionless number that matter is the Froude number $Fr = V^2/gD_0 = We/Bo$ which is larger than 1 throughout the paper.
-The difference as compared to \citet{zhang2022impact} is in the length scale (2 mm in PRL and 2.56 mm in this work).
+Following table~\ref{tab:table00} and considering the variation in impacting drop diameter (appendix~\ref{app:error}), the Bond number (equation~\eqref{Eq:BoDefinition}) in our experiments ranges from $0.5$ to $1.25$, introducing an additional dimensionless control parameter alongside $We$ and $Oh$.
+Gravity typically plays a negligible role in these impact processes \citep{sanjay_chantelot_lohse_2023,sanjay2024PRL}.
+We undertook a sensitivity test varying the Bond number from $0$ to $1.25$ in our simulations.
+Figure~\ref{fig:AppGravity} confirms the leading-order Bond invariance of the results as the impact force profiles, including both force peaks $F_1$ and $F_2$ and their corresponding times $t_1$ and $t_2$, remain invariant to these Bond number variations.
+Notably, while gravity does play a role in drop impact dynamics, particularly for longer time scales and in determining the critical Ohnesorge number $Oh_c$ for bouncing inhibition (see figure~\ref{fig:RegimeMaps}b and \citet{sanjay_chantelot_lohse_2023}), its effect on the initial impact force peaks is minimal for the parameter range studied here (large Froude numbers, $Fr > 1$).
+This Bond number invariance allows us to focus on the more dominant effects of Weber and Ohnesorge numbers.
+Consequently, we selected a representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.
+\bb
 

### 2024-08-28 Rebuttal.R2/Response to Reviewer 2_v2.tex

--- 2024-08-28 Rebuttal.R2/Response to Reviewer 2.tex
@@
 We have addressed this concern by adding a new appendix to the manuscript, titled ``Note on the experimental error characterization".
-We have also modified the caption of figure~2 of the main text (see figure~\ref{fig:summary}).
+We have also modified the caption of figure~2 of the main text to describe the horizontal dashed lines (see figure~\ref{fig:summary}).
 
@@
 		The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$.
-Surface tension is either $72,\si{\milli\newton}/\si{\meter}$ (pure water) or $61,\si{\milli\newton}/\si{\meter}$ (glycerol), while density $\rho_d$ ranges from $1000,\si{\kilo\gram}/\si{\cubic\meter}$ to $1220,\si{\kilo\gram}/\si{\cubic\meter}$, as detailed in table~1 \citep{cheng2008formula, volk2018density, Jha2020}.
+Surface tension is either $72\,\si{\milli\newton}/\si{\meter}$ (pure water) or $61\,\si{\milli\newton}/\si{\meter}$ (glycerol), while density $\rho_d$ ranges from $1000\,\si{\kilo\gram}/\si{\cubic\meter}$ to $1220\,\si{\kilo\gram}/\si{\cubic\meter}$, as detailed in table~1 \citep{cheng2008formula, volk2018density, Jha2020}.
 		\bb

### 2024-08-30 Rebuttal.R2/Response to Reviewer 2_v3.tex
feat: Update PDF files with new timestamps
The changes update the timestamps in the PDF files `F1_Drops_LowOh_v2.pdf` and `figureA1.pdf`. The last modified date has been changed to `2024-08-30` for both files.

This update is necessary to reflect the latest changes made to the figures and ensure the metadata accurately represents the current state of the files.

--- 2024-08-28 Rebuttal.R2/Response to Reviewer 2_v2.tex
@@
 		\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
-These parameter give $Oh = 0.0025, 0.0625, 0.2$ and $We = 40$.
-				For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
+These parameter give $Oh = 0.0025, 0.06, 0.2$ and $We = 40$.
+				For the three cases, the two peak amplitudes, $F_1/(\rho_dV_0^2D_0^2) \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/(\rho_dV_0^2D_0^2) \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
 				The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
 The black and gray dashed lines in panel (a) mark $F = 0$ and the resolution $F = 0.5\,\si{\milli\newton}$ of our piezoelectric force transducer, respectively.
-				(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), and (iv) $t = 4.63\,\si{\milli\second}$ ($t_2$).
+				(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0$ (touch-down), (ii) $t = 0.03\sqrt{\rho_dD_0^3/\gamma}$ ($t_1$), (iii) $t = 0.2\sqrt{\rho_dD_0^3/\gamma}$ ($t_{\text{max}}$), and (iv) $t = 0.42\sqrt{\rho_dD_0^3/\gamma}$ ($t_2$).
 				The insets of panel (a) exemplify these four instances for the three representative cases illustrated here. The experimental snapshots are overlaid with the drop boundaries from simulations. 
@@
 	The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.
-For the same Oh values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
+For the same $Oh$ values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
 	The combined errors in $D_0$ and $V_0$ resulted in approximately $\pm 7\%$ error in Weber number $We$ and $\pm 3\%$ error in Ohnesorge number $Oh$.
@@
 			The reviewer correctly notes that in our previous work \citep{zhang2022impact}, we used a fixed Bond number of 0.5 in simulations.
-The change to Bo = 1 in the current work was made to better represent the average experimental conditions.
+The change to $Bo = 1$ in the current work was made to better represent the average experimental conditions.
 However, as our sensitivity analysis shows, this change does not significantly affect our results or conclusions.
@@
 		Lastly, we keep the Bond number ($Bo$, see~(1.3)) fixed at 1 throughout the manuscript.
-In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
+In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ comparing inertia with gravity.
 Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~B).
@@
 
-	We appreciate the reviewer's suggestion regarding the title.
 	While we understand the importance of highlighting specific assumptions, we believe the current title strikes an appropriate balance between conciseness and informativeness.
@@
 	We acknowledge that the second peak is indeed dependent on surface wettability. 
-However, this specific aspect is thoroughly discussed within the paper, and we believe it does not warrant inclusion in the title.
+	However, this specific aspect is thoroughly discussed elsewhere \citep{zhang2023effect}, and throughout the present manuscript, we repeat ourselves several times that we have used perfectly non-wetting surfaces.
+	We believe it does not warrant inclusion in the title.
 
@@
 We acknowledge the reservations regarding the level of experimental detail.
-We have that the details added in the revised manuscript will address the reservation of the reviewer.
+We believe that the details added in the revised manuscript will address the reservation of the reviewer.
 

### 2024-08-30 Main/ViscousDropImpact_v9.tex
feat: Update PDF files with new timestamps
The changes update the timestamps in the PDF files `F1_Drops_LowOh_v2.pdf` and `figureA1.pdf`. The last modified date has been changed to `2024-08-30` for both files.

This update is necessary to reflect the latest changes made to the figures and ensure the metadata accurately represents the current state of the files.

--- 2024-08-28 Main/ViscousDropImpact_v7.tex
@@
  Bin Zhang\aff{2}
- \corresp{\email{binzhang0710@mail.tsinghua.edu.cn}},
+ \corresp{\email{binzhang0710@gmail.com}},
  Cunjing Lv\aff{2}
@@
 These parameter give $Oh = 0.0025, 0.06, 0.2$ and $We = 40$.
-	For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
+	For the three cases, the two peak amplitudes, $F_1/(\rho_dV_0^2D_0^2) \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/(\rho_dV_0^2D_0^2) \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
 	The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
 The black and gray dashed lines in panel (a) mark $F = 0$ and the resolution $F = 0.5\,\si{\milli\newton}$ of our piezoelectric force transducer, respectively.
-	(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), and (iv) $t = 4.63\,\si{\milli\second}$ ($t_2$).
+	(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0$ (touch-down), (ii) $t = 0.03\sqrt{\rho_dD_0^3/\gamma}$ ($t_1$), (iii) $t = 0.2\sqrt{\rho_dD_0^3/\gamma}$ ($t_{\text{max}}$), and (iv) $t = 0.42\sqrt{\rho_dD_0^3/\gamma}$ ($t_2$).
 	The insets of panel (a) exemplify these four instances for the three representative cases illustrated here. The experimental snapshots are overlaid with the drop boundaries from simulations. 
@@
 It is, indeed, captivating to observe raindrops hitting a solid surface \citep{kim2020raindrop, lohse-2020-pnas} or ocean spray affecting maritime structures \citep{berny2021statistics, villermaux2022bubbles}.
-The phenomenology of drop impact is extremely rich, encompassing behaviors such as drop deformation \citep{Biance2006, molavcek2012quasi, chevy2012liquid}, spreading \citep{laan2014maximum, Wildeman2016}, splashing \cite{xu2005drop, riboux2014experiments, thoraval2021nanoscopic}, fragmentation \citep{villermaux2011drop, villermaux2020fragmentation}, bouncing \citep{Richard2000, kolinski-2014-epl, Jha2020, chubynsky-2020-prl, sharma-2021-jfm, sanjay_chantelot_lohse_2023}, and wetting \citep{degennes-1985-rmp, fukai-1995-pof, quere-2008-arms, Bonn2009}.
+The phenomenology of drop impact is extremely rich, encompassing behaviors such as drop deformation \citep{Biance2006, molavcek2012quasi, chevy2012liquid}, spreading \citep{laan2014maximum, Wildeman2016}, splashing \citep{xu2005drop, riboux2014experiments, thoraval2021nanoscopic}, fragmentation \citep{villermaux2011drop, villermaux2020fragmentation}, bouncing \citep{Richard2000, kolinski-2014-epl, Jha2020, chubynsky-2020-prl, sharma-2021-jfm, sanjay_chantelot_lohse_2023}, and wetting \citep{degennes-1985-rmp, fukai-1995-pof, quere-2008-arms, Bonn2009}.
 These behaviors are influenced by the interplay of inertial, capillary, and viscous forces, as well as additional factors like non-Newtonian properties \citep{bartolo2005retraction, bartolo2007dynamics,  smith-2010-prl, gorin-2022-langmuir} of the liquid and even ambient air pressure \citep{xu2005drop}, making the parameter space for this phenomenon both extensive and high-dimensional.
@@
 These forces have been studied by \citet{zhang2022impact}, employing experiments and simulations and deriving scaling laws. 
-A liquid drop impacting a non-wetting substrate (figure~\ref{fig:summary}i-vi) undergoes a series of phases--spreading, recoiling, and potentially rebounding \citep{chantelot2018rebonds}--driven by the normal reaction force exerted by the substrate.
-The moment of touch-down (figure~\ref{fig:summary}i-ii) \citep{wagner1932stoss, Philippi2016, Gordillo2018} is not surprisingly associated with a pronounced peak in the temporal evolution of the drop impact force $F(t)$ owing to the sudden deacceleration as high as $100$ times the acceleration due to gravity \citep{Clanet2004} (figure~\ref{fig:summary}, $F(t = 0.37\,\si{\milli\second}) \approx 5.1\,\si{\milli\newton}$).
-The force diminishes as the drop reaches its maximum spreading diameter (figure~\ref{fig:summary}iii).
-\citet{zhang2022impact} revealed that also the jump-off is accompanied by a peak in the normal reaction force, which was up to then unknown (figure~\ref{fig:summary}, $F_2(t_2 = 4.63\,\si{\milli\second}) \approx 2.3\,\si{\milli\newton}$ for the second force peak amplitude--at time $t_2$ after impact).
-The second peak in the force also coincides with the formation of a Worthington jet, a narrow upward jet of liquid that can form due to flow focusing by the retracting drop (figure~\ref{fig:summary}iv-vi).
-Under certain conditions ($We \approx 9$), this peak can be even more pronounced than the first.
+A liquid drop impacting a non-wetting substrate undergoes a series of phases--spreading, recoiling, and potentially rebounding \citep{chantelot2018rebonds}--driven by the normal reaction force exerted by the substrate (figure~\ref{fig:summary}).
+The moment of touch-down (see figures~\ref{fig:summary}a,b $t = 0$ to $t_1$) \citep{wagner1932stoss, Philippi2016, Gordillo2018} is not surprisingly associated with a pronounced peak in the temporal evolution of the drop impact force $F(t)$ owing to the sudden deceleration as high as $100$ times the acceleration due to gravity \citep{Clanet2004} (figure~\ref{fig:summary}a, \Rev{$F_1/(\rho_dV_0^2D_0^2) \approx$ 0.82, 0.92, 0.99 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively; at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$}.
+%$F(t = 0.37\,\si{\milli\second}) \approx 5.1\,\si{\milli\newton}$). 
+The force diminishes as the drop reaches its maximum spreading diameter (figure~\ref{fig:summary}a,b $t = t_m$). 
+\citet{zhang2022impact} revealed that also the jump-off is accompanied by a peak in the normal reaction force, which was up to then unknown (figure~\ref{fig:summary}a, 
+%$F_2(t_2 = 4.63\,\si{\milli\second}) \approx 2.3\,\si{\milli\newton}$ 
+\Rev{$F_2/(\rho_dV_0^2D_0^2) \approx$ 0.37, 0.337, 0.1 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively;
+for the second force peak amplitude--at time $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$ after impact)}.
+The second peak in the force also coincides with the formation of a Worthington jet, a narrow upward jet of liquid that can form due to flow focusing by the retracting drop (figure~\ref{fig:summary}a,b $t = t_2$).
+Under certain conditions ($We \approx 9$, $Oh = 0.0025$), this peak can be even more pronounced than the first.
 This discovery is critical for superhydrophobicity which is volatile and can fail due to external disturbances such as pressure \citep{Lafuma2003, Callies2005, Sbragaglia2007, Li2017}, evaporation \citep{Tsai2010, Chen2012, Papadopoulos2013},  mechanical vibration \citep{Bormashenko2007}, or the impact forces of prior droplets \citep{Bartolo2006Bouncing}.
@@
 \Rev{The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$.
-Surface tension is either $72,\si{\milli\newton}/\si{\meter}$ (pure water) or $61,\si{\milli\newton}/\si{\meter}$ (glycerol), while density $\rho_d$ ranges from $1000,\si{\kilo\gram}/\si{\cubic\meter}$ to $1220,\si{\kilo\gram}/\si{\cubic\meter}$, as detailed in table~\ref{tab:table00} \citep{cheng2008formula, volk2018density, Jha2020}.
+Surface tension is either $72\,\si{\milli\newton}/\si{\meter}$ (pure water) or $61\,\si{\milli\newton}/\si{\meter}$ (glycerol), while density $\rho_d$ ranges from $1000\,\si{\kilo\gram}/\si{\cubic\meter}$ to $1220\,\si{\kilo\gram}/\si{\cubic\meter}$, as detailed in table~1 \citep{cheng2008formula, volk2018density, Jha2020}.
 We note that using liquids such as silicone oil can provide a broader range of viscosity variation when paired with a superamphiphobic substrate \citep{deng2012candle}.
@@
 \Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
-In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
+In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ comparing inertia with gravity.
 Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
@@
 
-\noindent{\bf  Code availability\bf{.}} The codes used in the present article, and the parameters and data to reproduce figures~\ref{fig:F1Anatomy} and~\ref{fig:F2Anatomy} are permanently available at \citet{basiliskVatsal}.\\
+\noindent{\bf  Code availability\bf{.}} The codes used in the present article, \Rev{and the parameters and data to reproduce figures~\ref{fig:F1Anatomy} and~\ref{fig:F2Anatomy}} are permanently available at \citet{basiliskVatsal}.\\
 
@@
 \label{app:error}
-
-This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
+\bb
+\Rev{This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
 The drop diameter determination involves multiple steps.
@@
 We repeated this process for five trials, obtaining $V_{0,1}$ through $V_{0,5}$.
-The average of these values gave the final impact velocity ($V_0$) and its standard error.
+The average of these values gave the final impact velocity ($V_0$) and its standard error.}
 
+\oo
 The standard errors for drop diameters do not exceed $0.13\,\si{\milli\meter}$.
@@
 The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.
-For the same Oh values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
+For the same $Oh$ values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
 The combined errors in $D_0$ and $V_0$ resulted in approximately $\pm 7\%$ error in Weber number $We$ and $\pm 3\%$ error in Ohnesorge number $Oh$.
@@
 \oo 
-
 \section{Role of gravity on drop impact forces}
 \label{app:gravity}
+\bb
 
-Following table~\ref{tab:table00} and considering the variation in impacting drop diameter (appendix~\ref{app:error}), the Bond number (equation~\eqref{Eq:BoDefinition}) in our experiments ranges from $0.5$ to $1.25$, introducing an additional dimensionless control parameter alongside $We$ and $Oh$.
+\Rev{Following table~\ref{tab:table00} and considering the variation in impacting drop diameter (appendix~\ref{app:error}), the Bond number (equation~\eqref{Eq:BoDefinition}) in our experiments ranges from $0.5$ to $1.25$, introducing an additional dimensionless control parameter alongside $We$ and $Oh$.
 Gravity typically plays a negligible role in these impact processes \citep{sanjay_chantelot_lohse_2023,sanjay2024PRL}.
@@
 This Bond number invariance allows us to focus on the more dominant effects of Weber and Ohnesorge numbers.
-Consequently, we selected a representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.
-\bb
+Consequently, we selected a representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.}
 

### 2024-08-31 Rebuttal.R2/Response to Reviewer 2_v3.tex
feat: Improve error bar explanation in the manuscript
This commit clarifies the explanation of the error bars in the manuscript. The
changes include:

- Specifying that the error bars represent one standard deviation from
  repeated trials, rather than just 'repeated trials'
- Moving the reference to the supplementary material and appendix to the end
  of the paragraph, to better connect it to the error bar explanation
- Providing a more precise description of the error bar visualization, noting
  that they are only shown if larger than the marker size

The goal of these changes is to provide

@@
 		We stress the excellent agreement between experiments and simulations without any free parameters.
-				The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity.
+		The left part of each numerical snapshot shows (on a $\log_{10}$ scale) the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, and the right part the velocity field magnitude normalized with the impact velocity.
 The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.
@@
 	We appreciate the reviewer's insistence on a comprehensive error characterization.
-We have addressed this concern by adding a new appendix to the manuscript, titled ``Note on the experimental error characterization".
+We have addressed this concern by adding a new appendix to the manuscript, titled ``Note on the error characterization for the control parameters".
 We have also modified the caption of figure~2 of the main text to describe the horizontal dashed lines (see figure~\ref{fig:summary}).
@@
 	\oo
-	Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
-We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~A for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.
+	Throughout the manuscript, the error bars are of statistical nature (one standard deviation) and originate from repeated trials.
+They are visible if they are larger than the marker size.
+We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~A for further details of the experimental setup and error characterization of the dimensionless control parameters.
 
-	\section*{Appendix A. Note on the experimental error characterization}
+	\section*{Appendix A. Note on the error characterization for the control parameters}
 	\label{app:error}
@@
 			\item \textbf{Simulation Bond number:}
-			In our simulations, we chose to use a fixed Bond number of 1 as a representative value.
+			In our simulations, we chose to use a fixed Bond number of 1 as the representative value.
 This choice was made to simplify the parameter space and focus on the effects of Weber and Ohnesorge numbers.
@@
 		\oo
-		Lastly, we keep the Bond number ($Bo$, see~(1.3)) fixed at 1 throughout the manuscript.
-In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ comparing inertia with gravity.
+		Lastly, we keep the Bond number $Bo$ (see~(1.3)) fixed at 1 throughout the manuscript.
+In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ which compares inertia with gravity.
 Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~B).
@@
 This Bond number invariance allows us to focus on the more dominant effects of Weber and Ohnesorge numbers.
-		Consequently, we selected a representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.
+		Consequently, we selected the representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.
 		\bb
@@
 In our experiments, drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
-We have now added a discussion in the new appendix, titled ``Note on the experimental error characterization".
+We have now added a discussion in the new appendix, titled ``Note on the error characterization for the control parameters".
 		We also share reviewer's assertion that it would be a great idea to share all the experimental data.
@@
 	\oo
-	It is important to note that experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
+	It is important to note that large experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
 These shape perturbations are more pronounced in cases with low Weber and Ohnesorge numbers.

### 2024-08-31 Main/ViscousDropImpact_v9.tex
feat: Improve error bar explanation in the manuscript
This commit clarifies the explanation of the error bars in the manuscript. The
changes include:

- Specifying that the error bars represent one standard deviation from
  repeated trials, rather than just 'repeated trials'
- Moving the reference to the supplementary material and appendix to the end
  of the paragraph, to better connect it to the error bar explanation
- Providing a more precise description of the error bar visualization, noting
  that they are only shown if larger than the marker size

The goal of these changes is to provide

@@
 	We stress the excellent agreement between experiments and simulations without any free parameters.
-	The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity.
+	The left part of each numerical snapshot shows (on a $\log_{10}$ scale) the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, and the right part the velocity field magnitude normalized with the impact velocity.
 The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.
@@
 The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$.
-\Rev{Throughout the manuscript, the error bars account for repeated trials and are visible if they are larger than the marker size.
-We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters, respectively.}
+\Rev{Throughout the manuscript, the error bars are of statistical nature (one standard deviation) and originate from repeated trials.
+They are visible if they are larger than the marker size.
+We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters.}
 
@@
 The Ohnesorge number based on air viscosity $Oh_a = \left(\eta_a/\eta_d\right)Oh$ and air-drop density ratio $\rho_a/\rho_d$ are fixed at $10^{-5}$ and $10^{-3}$, respectively to minimize the influence of the surrounding medium on the impact forces.
-\Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
-In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ comparing inertia with gravity.
+\Rev{Lastly, we keep the Bond number $Bo$ (see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
+In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ which compares inertia with gravity.
 Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
@@
 At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. 
-\Rev{It is important to note that experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
+\Rev{It is important to note that large experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
 These shape perturbations are more pronounced in cases with low Weber and Ohnesorge numbers.
@@
 \oo
-\section{Note on the parametric error characterization}
+\section{Note on the error characterization for the control parameters}
 \label{app:error}
@@
 This Bond number invariance allows us to focus on the more dominant effects of Weber and Ohnesorge numbers.
-Consequently, we selected a representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.}
+Consequently, we selected the representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.}
 

### 2024-08-31 Main/ViscousDropImpact_v10.tex
feat(drop-impact): Characterize the peak impact and take-off forces
The changes made in this commit focus on characterizing the peak impact force ($F_1$) and the peak take-off force ($F_2$) during the impact of a liquid drop on a non-wetting substrate. The key changes are:

1. Explained the two-peak structure of the normal force $F(t)$ observed in the authors' previous work, where the second peak coincides with a Worthington jet formation.
2. Conducted experiments, direct numerical simulations, and scaling analyses to understand the dependency of $F_1$ and $F_2$ on the Weber number ($We$) and

--- 2024-08-31 Main/ViscousDropImpact_v9.tex
@@
 		\includegraphics[width=\textwidth]{Figures/Figure1_summary_v6.pdf}
-	\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
+		\caption{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
 These parameter give $Oh = 0.0025, 0.06, 0.2$ and $We = 40$.
@@
 The black velocity vectors are plotted in the center of mass reference frame of the drop to clearly elucidate the internal flow.
-Also see supplementary videos SM1-SM3.\bb}}
+Also see supplementary videos SM1-SM3.}
 		\label{fig:summary}
@@
 	A liquid drop impacting a non-wetting substrate undergoes a series of phases--spreading, recoiling, and potentially rebounding \citep{chantelot2018rebonds}--driven by the normal reaction force exerted by the substrate (figure~\ref{fig:summary}).
-The moment of touch-down (see figures~\ref{fig:summary}a,b $t = 0$ to $t_1$) \citep{wagner1932stoss, Philippi2016, Gordillo2018} is not surprisingly associated with a pronounced peak in the temporal evolution of the drop impact force $F(t)$ owing to the sudden deceleration as high as $100$ times the acceleration due to gravity \citep{Clanet2004} (figure~\ref{fig:summary}a, \Rev{$F_1/(\rho_dV_0^2D_0^2) \approx$ 0.82, 0.92, 0.99 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively; at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$}.
-%$F(t = 0.37\,\si{\milli\second}) \approx 5.1\,\si{\milli\newton}$). 
+	The moment of touch-down (see figures~\ref{fig:summary}a,b $t = 0$ to $t_1$) \citep{wagner1932stoss, Philippi2016, Gordillo2018} is not surprisingly associated with a pronounced peak in the temporal evolution of the drop impact force $F(t)$ owing to the sudden deceleration as high as $100$ times the acceleration due to gravity \citep{Clanet2004} (figure~\ref{fig:summary}a, $F_1/(\rho_dV_0^2D_0^2) \approx$ 0.82, 0.92, 0.99 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively; at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$.
 	The force diminishes as the drop reaches its maximum spreading diameter (figure~\ref{fig:summary}a,b $t = t_m$). 
 	\citet{zhang2022impact} revealed that also the jump-off is accompanied by a peak in the normal reaction force, which was up to then unknown (figure~\ref{fig:summary}a, 
-%$F_2(t_2 = 4.63\,\si{\milli\second}) \approx 2.3\,\si{\milli\newton}$ 
-\Rev{$F_2/(\rho_dV_0^2D_0^2) \approx$ 0.37, 0.337, 0.1 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively;
-for the second force peak amplitude--at time $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$ after impact)}.
+	$F_2/(\rho_dV_0^2D_0^2) \approx$ 0.37, 0.337, 0.1 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively; for the second force peak amplitude--at time $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$ after impact)
 	The second peak in the force also coincides with the formation of a Worthington jet, a narrow upward jet of liquid that can form due to flow focusing by the retracting drop (figure~\ref{fig:summary}a,b $t = t_2$).
@@
 On the other hand, for viscous aqueous glycerin drops, the upper surface is coated with an acetone solution of hydrophobic beads (Ultra ever Dry, Ultratech International, a typical bead size of 20 nm), resulting in the advancing and receding contact angles of $166 \pm 4^{\circ}$ and $159 \pm 2^{\circ}$, respectively \citep{Jha2020}.
-\Rev{The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$.
+	The properties of the impacting drop are controlled using water-glycerol mixtures with viscosities $\eta_d$ varying by almost two orders of magnitude, from $1\,\si{\milli\pascal}\si{\second}$ to $80.2\,\si{\milli\pascal}\si{\second}$.
 Surface tension is either $72\,\si{\milli\newton}/\si{\meter}$ (pure water) or $61\,\si{\milli\newton}/\si{\meter}$ (glycerol), while density $\rho_d$ ranges from $1000\,\si{\kilo\gram}/\si{\cubic\meter}$ to $1220\,\si{\kilo\gram}/\si{\cubic\meter}$, as detailed in table~1 \citep{cheng2008formula, volk2018density, Jha2020}.
@@
 	The drop diameter $D_0$ is controlled between $2.05\,\si{\milli\meter}$ and $2.76\,\si{\milli\meter}$ by pushing it through a calibrated needle (see appendix~\ref{app:error} for details). 
-Consequently, we calculate $Oh$ using the properties in table~\ref{tab:table00}.} 
+	Consequently, we calculate $Oh$ using the properties in table~\ref{tab:table00}.
 	The Weber number ($We$, see~\eqref{Eq:WeDefinition}) is set using the impact velocity $V_0$ varying between $0.38\,\si{\meter}/\si{\second}$ and $2.96\,\si{\meter}/\si{\second}$ by changing the release height of the drops above the substrate.
@@
 	The experiment also employs a high-speed camera (Photron Fastcam Nova S12) synchronized at $10,000$ fps with a shutter speed $1/20,000\,\si{\second}$.
-\Rev{Throughout the manuscript, the error bars are of statistical nature (one standard deviation) and originate from repeated trials.
+Throughout the manuscript, the error bars are of statistical nature (one standard deviation) and originate from repeated trials.
 They are visible if they are larger than the marker size.
-We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters.}
+We refer the readers to the supplementary material of \citet{zhang2022impact}  and appendix~\ref{app:error} for further details of the experimental setup and error characterization of the dimensionless control parameters.
 
@@
 	The Ohnesorge number based on air viscosity $Oh_a = \left(\eta_a/\eta_d\right)Oh$ and air-drop density ratio $\rho_a/\rho_d$ are fixed at $10^{-5}$ and $10^{-3}$, respectively to minimize the influence of the surrounding medium on the impact forces.
-\Rev{Lastly, we keep the Bond number $Bo$ (see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
+	Lastly, we keep the Bond number $Bo$ (see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
 In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ which compares inertia with gravity.
-Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
+Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).
 	The substrate is modeled as a no-slip and non-penetrable wall, whereas vanishing stress and pressure are applied at the remaining boundaries to mimic outflow conditions for the surrounding air.
@@
 	At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. 
-\Rev{It is important to note that large experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
+	It is important to note that large experimental drops may deviate from perfect sphericity due to air drag as they fall after detaching from the needle and potential residual oscillations from detachment.
 These shape perturbations are more pronounced in cases with low Weber and Ohnesorge numbers.
@@
 In our experiments, we constrain our analysis to drops with aspect ratios between 0.96 and 1.05.
-Given this narrow range, we posit that the impact of these shape variations is negligible compared to the experimental error bars derived from repeated trials under identical nominal conditions.}
+Given this narrow range, we posit that the impact of these shape variations is negligible compared to the experimental error bars derived from repeated trials under identical nominal conditions.
 	The simulations utilize adaptive mesh refinement to finely resolve the velocity, viscous dissipation, and the VoF tracer fields. A minimum grid size $\Delta = D_0/2048$ is used for this study.
@@
 
-\noindent{\bf  Code availability\bf{.}} The codes used in the present article, \Rev{and the parameters and data to reproduce figures~\ref{fig:F1Anatomy} and~\ref{fig:F2Anatomy}} are permanently available at \citet{basiliskVatsal}.\\
+	\noindent{\bf  Code availability\bf{.}} The codes used in the present article, and the parameters and data to reproduce figures~\ref{fig:F1Anatomy} and~\ref{fig:F2Anatomy} are permanently available at \citet{basiliskVatsal}.\\
 
@@
 
-\oo
 	\section{Note on the error characterization for the control parameters}
 	\label{app:error}
-\bb
-\Rev{This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of dimensionless control parameters, $We$ and $Oh$.
+
+	This appendix outlines the methodology for characterizing experimental errors in quantification of the drop's size and impact velocities which is crucial for accurate calculation of the dimensionless control parameters $We$ and $Oh$.
 	The drop diameter determination involves multiple steps.
@@
 We repeated this process for five trials, obtaining $V_{0,1}$ through $V_{0,5}$.
-The average of these values gave the final impact velocity ($V_0$) and its standard error.}
+The average of these values gave the final impact velocity ($V_0$) and its standard error.
 
-\oo
 	The standard errors for drop diameters do not exceed $0.13\,\si{\milli\meter}$.
@@
 Consequently, the horizontal error bars, which relate to errors in the control parameters, are smaller than the symbol sizes in our figures.
-\bb
 
@@
 		\includegraphics[width=\textwidth]{Figures/figureA1.pdf}
-	\caption{{\oo Comparison of the drop impact force $F(t)$ obtained from simulations for the four different Bond numbers $Bo = 0, 0.5, 1, 1.25$.
+		\caption{Comparison of the drop impact force $F(t)$ obtained from simulations for the four different Bond numbers $Bo = 0, 0.5, 1, 1.25$.
 Here, $Oh = 0.06$ and $We = 40$.
-Both force peaks $F_1$ and $F_2$ as well as time to reach these peaks $t_1$ and $t_2$ are invariant to variation in $Bo$.
-\bb}}
+Both force peaks $F_1$ and $F_2$ as well as time to reach these peaks $t_1$ and $t_2$ are invariant to variation in $Bo$.}
 		\label{fig:AppGravity}
@@
 
-\oo 
 	\section{Role of gravity on drop impact forces}
 	\label{app:gravity}
-\bb
 
-\Rev{Following table~\ref{tab:table00} and considering the variation in impacting drop diameter (appendix~\ref{app:error}), the Bond number (equation~\eqref{Eq:BoDefinition}) in our experiments ranges from $0.5$ to $1.25$, introducing an additional dimensionless control parameter alongside $We$ and $Oh$.
+	Following table~\ref{tab:table00} and considering the variation in impacting drop diameter (appendix~\ref{app:error}), the Bond number (equation~\eqref{Eq:BoDefinition}) in our experiments ranges from $0.5$ to $1.25$, introducing an additional dimensionless control parameter alongside $We$ and $Oh$.
 	Gravity typically plays a negligible role in these impact processes \citep{sanjay_chantelot_lohse_2023,sanjay2024PRL}.
@@
 This Bond number invariance allows us to focus on the more dominant effects of Weber and Ohnesorge numbers.
-Consequently, we selected the representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.}
+	Consequently, we selected the representative value of $Bo = 1$, corresponding to a diameter of $0.00254\,\si{\milli\meter}$, density $1000\,\si{\kilogram/\meter^3}$, gravitational acceleration $10\,\si{\meter/\second^2}$, and surface tension $0.061\,\si{\newton/\meter}$.
 

### 2024-08-31 Rebuttal.R2/Response to Reviewer 2_v3.tex

@@
 \usepackage{mathrsfs}
-\usepackage[colorlinks,citecolor=purple]{hyperref}
+\usepackage[colorlinks,citecolor=purple,urlcolor=blue]{hyperref}
 \newcommand*\blue{\textcolor{blue}}
@@
 			\item \textbf{Experimental Bond number range:}
-			Indeed, given the variation in fluid properties and drop sizes used in our experiments, the Bond number is not strictly fixed at 1. 
+			Indeed, given the variation in fluid properties and drop sizes used in our experiments, the Bond number is not strictly fixed at 1, it only is $\mathcal{O}\left(1\right)$.
 			\item \textbf{Simulation Bond number:}
@@
 The change to $Bo = 1$ in the current work was made to better represent the average experimental conditions.
-However, as our sensitivity analysis shows, this change does not significantly affect our results or conclusions.
+However, as our sensitivity analysis shows, this change hardly affects our results.
 		\end{enumerate}
@@
 
-		We appreciate the reviewer's suggestion to clarify all the experimental data, and we have taken steps to address this.
+		We appreciate the reviewer's suggestion to clarify all the experimental data, and we have now addressed this.
 In our experiments, drops with Ohnesorge numbers of $0.0025$, $0.0625$, and $0.2$ have diameters of $2.05 \pm 0.13\,\si{\milli\meter}$, $2.52 \pm 0.11\,\si{\milli\meter}$, and $2.54 \pm 0.09\,\si{\milli\meter}$, respectively.
@@
 We have made it available using Zenodo, see \citet{basiliskVatsal}.
+We will also share the Jupyter notebook using JFM notebooks.
 
@@
 
-	We now cite the accessible version of this work: \citet{sanjay2024PRL}.
+	We now cite the accessible version of this work: \citet{sanjay2024PRL}. The paper is available at \href{https://doi.org/10.48550/arXiv.2408.12714}{https://doi.org/10.48550/arXiv.2408.12714}.
 

### 2024-09-01 arXiv/ViscousDropImpact_v10.tex

--- 2024-08-31 Main/ViscousDropImpact_v10.tex
@@
 \usepackage{siunitx}
-\usepackage{lineno}
-\linenumbers
+%\usepackage{lineno}
+%\linenumbers
 
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/Schematic_v2.pdf}
+		\includegraphics[width=\textwidth]{Schematic_v2.pdf}
 		\caption{(a) Problem schematic with an axisymmetric computational domain used to study the impact of a drop with diameter $D_0$ and velocity $V_0$ on a non-wetting substrate.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/Figure1_summary_v6.pdf}
+		\includegraphics[width=\textwidth]{Figure1_summary_v6.pdf}
 		\caption{Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for the three typical cases with impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, surface tension $\gamma = 72\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}, 61\,\si{\milli\newton}/\si{\meter}$ and viscosity $\eta_d = 1\,\si{\milli\pascal\second}, 25.3\,\si{\milli\pascal\second}, 80.2\,\si{\milli\pascal\second}$.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/Force1_Anatomy_v2.pdf}
+		\includegraphics[width=\textwidth]{Force1_Anatomy_v2.pdf}
 		\caption{Anatomy of the first impact force peak amplitude at low $Oh$ in between 0.0025 and 0.2, see color legend: $We$ dependence of the (a) magnitude $F_1$ normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$ and time $t_1$ to reach the first force peak amplitude normalized by (b) the inertial timescale $\tau_\rho = D_0/V_0$ and (c) the inertio-capillary time scale $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$.}
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/F1_Drops_LowOh_v2.pdf}
+		\includegraphics[width=\textwidth]{F1_Drops_LowOh_v2.pdf}
 		\caption{Direct numerical simulations snapshots illustrating the drop impact dynamics for $We$ = (a) 40 and (b) 2.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/ForceTimeVersusOhnesorge.pdf}
+		\includegraphics[width=\textwidth]{ForceTimeVersusOhnesorge.pdf}
 		\caption{Anatomy of the first impact force peak amplitude for viscous impacts from our numerical simulations: the $Oh$ dependence of  (a) the magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ and (b) the time $t_1$ to reach the first force peak amplitude normalized by inertial timescale $\tau_\rho = D_0/V_0$.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/Figure3.2_F1_Drops.pdf}
+		\includegraphics[width=\textwidth]{Figure3.2_F1_Drops.pdf}
 		\caption{Direct numerical simulations snapshots illustrating the drop impact dynamics for $We = 100$ and $Oh$ = (a) 0.05, (b) 0.5, and (c) 5.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/Force2_Anatomy_v4.pdf}
+		\includegraphics[width=\textwidth]{Force2_Anatomy_v4.pdf}
 		\caption{Anatomy of the second impact force peak amplitude: $We$ dependence of the (a) magnitude $F_2$ normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$ and time $t_2$ to reach the second force peak amplitude normalized by (b) the inertio-capillary time scale $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$ and (c) inertial timescale $\tau_\rho = D_0/V_0$.}
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/F2phenomenology.pdf}
+		\includegraphics[width=\textwidth]{F2phenomenology.pdf}
 		\caption{Direct numerical simulations snapshots illustrating the influence of $We$ and $Oh$ on the inception of the Worthington jet.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/Figure4.3_F2_Drops.pdf}
+		\includegraphics[width=\textwidth]{Figure4.3_F2_Drops.pdf}
 		\caption{Direct numerical simulations snapshots illustrating the influence of $We$ and $Oh$ on the singular Worthington jet.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/RegimeMaps_v3.pdf}
+		\includegraphics[width=\textwidth]{RegimeMaps_v3.pdf}
 		\caption{Regime map in terms of the drop Ohnesorge number $Oh$ and the impact Weber number $We$ to summarize the two peaks in the impact force by showing the different regimes described in this work based on (a) the first peak in the impact force peak amplitude $F_1$ and (b) the second peak in the impact force peak amplitude $F_2$.
@@
 
-	\noindent{\bf  Author ORCID\bf{.}}
-
-	V. Sanjay \href{https://orcid.org/0000-0002-4293-6099}{https://orcid.org/0000-0002-4293-6099};
-
-	B. Zhang \href{https://orcid.org/0000-0001-8550-2584}{https://orcid.org/0000-0001-8550-2584};
-
-	C. Lv \href{https://orcid.org/0000-0001-8016-6462}{https://orcid.org/0000-0001-8016-6462};
-
+	\noindent{\bf  Authors' ORCID\bf{.}}  \\	
+	V. Sanjay \href{https://orcid.org/0000-0002-4293-6099}{https://orcid.org/0000-0002-4293-6099};\\
+	B. Zhang \href{https://orcid.org/0000-0001-8550-2584}{https://orcid.org/0000-0001-8550-2584};\\	
+	C. Lv \href{https://orcid.org/0000-0001-8016-6462}{https://orcid.org/0000-0001-8016-6462};\\
 	D. Lohse \href{https://orcid.org/0000-0003-4138-2255}{https://orcid.org/0000-0003-4138-2255}. \\
@@
 		\centering
-		\includegraphics[width=\textwidth]{Figures/figureA1.pdf}
+		\includegraphics[width=\textwidth]{figureA1.pdf}
 		\caption{Comparison of the drop impact force $F(t)$ obtained from simulations for the four different Bond numbers $Bo = 0, 0.5, 1, 1.25$.

### 2024-09-06 Main/manuscript_Final.tex
Final submission

--- 2024-08-31 Main/ViscousDropImpact_v10.tex
@@
 %\shorttitle{Inertia \& viscosity dictate drop impact forces}
-\shorttitle{The role of viscosity on drop impact forces}
+\shorttitle{The role of viscosity on drop impact forces on non-wetting surfaces}
 \shortauthor{V. Sanjay, B. Zhang, C. Lv, and D. Lohse}
@@
 %\title{Inertia \& viscosity dictate drop impact forces}
-\title{The role of viscosity on drop impact forces}
+\title{The role of viscosity on drop impact forces on non-wetting surfaces}
 \author{Vatsal Sanjay\aff{1}

### 2024-09-24 Main/oldversions/TestEquations.tex
updated accepted version

\documentclass[]{article}

%opening
\usepackage{siunitx}
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\title{}
\author{}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{}
Anatomy of the first impact force peak at low $Oh$: $We$ dependence of the (a) magnitude $F_1$ normalized by the inertial force scale $\rho_dV_0^2D_0^2$ and time $t_1$ to reach the first force peak normalized by (b) inertial timescale $\tau_\rho = D_0/V_0$ and the inertio-capillary time scale $\tau_\gamma = \sqrt{\rho_dD_0^3/\gamma}$.

%As the drop falls on a substrate, momentum conservation implies $F_1 \sim V_0(\mathrm{d}m/\mathrm{d}t)$, where the mass flux $\mathrm{d}m/\mathrm{d}t$ can be calculated as $\mathrm{d}m/\mathrm{d}t \sim \rho_d V_0D_0^2$ \cite{Soto2014}. As a result, $F_1 \sim \rho_d V_0^2D_0^2$, as shown in Fig.~\ref{Fig:3}(a) for high Weber numbers ($\Wen > 30$, $F_1 \approx 0.81\rho_d V_0^2D_0^2$). This asymptote also matches the experimental and theoretical results of similar studies conducted on hydrophilic substrates \cite{Zhang2017, Gordillo2018}. Indeed, the first peak force originates from an inertial shock following the impact of drops onto an immobile substrate and is independent of the wettability.

In our continued exploration of the dynamics of fluid impacts, we have turned our attention to the influence of viscosity on the first impact force peak, $F_1$. Our findings have revealed intriguing parallels with previous research, particularly in the context of low Ohnesorge numbers (Oh $<< 1$).

The Ohnesorge number, a dimensionless quantity often used in fluid dynamics, is a measure of the relative importance of viscosity in the flow of a fluid. In our study, we have found that for low Ohnesorge numbers, the behavior of the first impact force peak aligns remarkably well with the patterns outlined in previous work.

As previously established, the minimum Reynolds number for the current work is $800$, significantly exceeding the criterion ($Re > 200$) for viscosity-independent results. This led to the expectation that the normalized first impact force, $\tilde{F}_1 \equiv F_1/\rho_d V_0^2D_0^2$, would remain constant across our parameter space. However, deviations were observed when $We < 30$, a phenomenon also reported in studies involving hydrophilic surfaces.

In these instances, inertia does not act as the sole governing force, but instead competes with surface tension. A generalization of the first peak of the impact force was proposed, expressed as $F_1 = \alpha_1\rho_d V_0^2 D_0^2 + \alpha_2(\gamma/ D_0) D_0^2$, based on dimensional analysis, with $\alpha_1$ and $\alpha_2$ as free parameters.

In our latest investigation, we have extended our study to consider the influence of viscosity on the first impact force peak, $F_1$, particularly focusing on the role of the Ohnesorge number (Oh). This dimensionless parameter, which encapsulates the interplay between inertial, viscous, and surface tension forces, was previously held constant at a value of 0.0033 in our earlier work.
In the current study, we have broadened our scope to examine scenarios where the Ohnesorge number reaches up to 0.2. Remarkably, despite this significant increase in the Ohnesorge number, we observed no substantial alteration in the behavior of the first impact force peak. The force $F_1$ continues to be well-described by the equation $F_1 = \alpha_1\rho_d V_0^2 D_0^2 + \alpha_2(\gamma/ D_0) D_0^2$, a model proposed in our previous work based on dimensional analysis.
Furthermore, the coefficients $\alpha_1$ and $\alpha_2$ in this equation, which were determined to be approximately 1.6 and 0.81 respectively in our earlier study, only deviate marginally in the current work. This consistency, observed even under conditions of increased Ohnesorge numbers, underscores the robustness of our model and its applicability across a wider range of fluid dynamic scenarios than previously explored.
This discovery not only reaffirms the conclusions drawn from our prior research, but also broadens the scope of our understanding of the intricate dance between inertia, viscosity, and surface tension in fluid impacts. It lays a sturdy groundwork for subsequent investigations that aim to delve deeper into the complex dynamics of fluid impacts under a wider range of conditions.  In the following section, we will delve into the exploration of even higher Ohnesorge numbers, pushing the boundaries of our understanding of fluid impacts.

Our current research has revealed that this model holds true even in the realm of low Ohnesorge numbers. The best fit to all the experimental and numerical data yielded $\tilde{F}_1 \approx 0.81 + 1.6We^{-1}$, which accurately describes the data.

In conclusion, our findings suggest that the influence of viscosity on the first impact force peak, under conditions of low Ohnesorge numbers, is consistent with the behavior observed in previous studies. This reinforces the robustness of the proposed model and provides a deeper understanding of the complex interplay between inertia and surface tension in fluid dynamics.

Comparison of the drop impact force $F(t)$ obtained from experiments and simulations for $Oh = $ 0.0025, 0.0625, 0.2.  For all these cases, $We = 40$. For the three cases, the impact velocity $V_0 = 1.2\,\si{\meter}/\si{\second}, 0.97\,\si{\meter}/\si{\second}, 0.96\,\si{\meter}/\si{\second}$, diameter $D_0 = 2.05\,\si{\milli\meter}, 2.52\,\si{\milli\meter}, 2.54\,\si{\milli\meter}$, and viscosity $\eta_d = 1\,\si{\milli\pascal\second}$ a drop of diameter $D_0 = 2.05\,\si{\milli\meter}$ falling at a velocity of $V_0 = 1.2\,\si{\meter}/\si{\second}$ (giving $We = 40$). We stress the excellent agreement between experiments and simulations without any free parameters. The insets show representative snapshots at specific time instants overlaid with the drop boundaries from simulations in orange, also revealing good agreement. The two peak amplitudes, $F_1 \approx 5.1\,\si{\milli\newton}$ at $t_1 \approx 0.37\,\si{\milli\second}$ and $F_2 \approx 2.3\,\si{\milli\newton}$ at $t_2 \approx 4.63\,\si{\milli\second}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively. The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $t_3$ when the drop takes off ($F = 0$). Six instances are further elaborated through numerical simulations, namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), (iv) $t = 3.93\,\si{\milli\second}$ ($\approx 0.85t_2$), (v) $t = 4.63\,\si{\milli\second}$ ($t_2$), and (vi) $t = 5.25\,\si{\milli\second}$ ($\approx 1.15t_2$). The left part of each numerical snapshot shows the dimensionless local viscous dissipation function $\tilde{\xi}_\eta \equiv \xi_\eta D_0/\left(\rho_dV_0^3\right) = 2Oh\left(\boldsymbol{\tilde{\mathcal{D}}:\tilde{\mathcal{D}}}\right)$, where, $\boldsymbol{\mathcal{D}}$ is the symmetric part of the velocity gradient tensor, on a $\log_{10}$ scale and the right part the velocity field magnitude normalized with the impact velocity. The black velocity vectors are plotted in the center of mass reference frame of the drop, to clearly elucidate the internal flow.

\end{document}

### 2024-09-24 Main/oldversions/ViscousDropImpact_v8.tex
updated accepted version

--- 2024-08-30 Main/ViscousDropImpact_v9.tex
@@
  Bin Zhang\aff{2}
- \corresp{\email{binzhang0710@gmail.com}},
+ \corresp{\email{binzhang0710@mail.tsinghua.edu.cn}},
  Cunjing Lv\aff{2}
@@
 These parameter give $Oh = 0.0025, 0.06, 0.2$ and $We = 40$.
-	For the three cases, the two peak amplitudes, $F_1/(\rho_dV_0^2D_0^2) \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/(\rho_dV_0^2D_0^2) \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
+	For the three cases, the two peak amplitudes, $F_1/\rho_dV_0^2D_0^2 \approx$ 0.82, 0.92, 0.99 at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$ and $F_2/\rho_dV_0^2D_0^2 \approx$ 0.37, 0.337, 0.1 at $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$, characterize the inertial shock from impact and the Worthington jet before takeoff, respectively.
 	The drop reaches the maximum spreading at $t_{\text{max}}$ when it momentarily stops and retracts until $0.8\sqrt{\rho_dD_0^3/\gamma}$ when the drop takes off ($F = 0$).
 The black and gray dashed lines in panel (a) mark $F = 0$ and the resolution $F = 0.5\,\si{\milli\newton}$ of our piezoelectric force transducer, respectively.
-	(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0$ (touch-down), (ii) $t = 0.03\sqrt{\rho_dD_0^3/\gamma}$ ($t_1$), (iii) $t = 0.2\sqrt{\rho_dD_0^3/\gamma}$ ($t_{\text{max}}$), and (iv) $t = 0.42\sqrt{\rho_dD_0^3/\gamma}$ ($t_2$).
+	(b) Four instances are further elaborated through numerical simulations for ($We = 40, Oh = 0.0025$), namely (i) $t = 0\,\si{\milli\second}$ (touch-down), (ii) $t = 0.37\,\si{\milli\second}$ ($t_1$), (iii) $t = 2.5\,\si{\milli\second}$ ($t_{\text{max}}$), and (iv) $t = 4.63\,\si{\milli\second}$ ($t_2$).
 	The insets of panel (a) exemplify these four instances for the three representative cases illustrated here. The experimental snapshots are overlaid with the drop boundaries from simulations. 
@@
 A liquid drop impacting a non-wetting substrate undergoes a series of phases--spreading, recoiling, and potentially rebounding \citep{chantelot2018rebonds}--driven by the normal reaction force exerted by the substrate (figure~\ref{fig:summary}).
-The moment of touch-down (see figures~\ref{fig:summary}a,b $t = 0$ to $t_1$) \citep{wagner1932stoss, Philippi2016, Gordillo2018} is not surprisingly associated with a pronounced peak in the temporal evolution of the drop impact force $F(t)$ owing to the sudden deceleration as high as $100$ times the acceleration due to gravity \citep{Clanet2004} (figure~\ref{fig:summary}a, \Rev{$F_1/(\rho_dV_0^2D_0^2) \approx$ 0.82, 0.92, 0.99 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively; at $t_1 \approx 0.03\sqrt{\rho_dD_0^3/\gamma}$}.
-%$F(t = 0.37\,\si{\milli\second}) \approx 5.1\,\si{\milli\newton}$). 
+The moment of touch-down (see figures~\ref{fig:summary}a,b $t = 0$ to $t_1$) \citep{wagner1932stoss, Philippi2016, Gordillo2018} is not surprisingly associated with a pronounced peak in the temporal evolution of the drop impact force $F(t)$ owing to the sudden deceleration as high as $100$ times the acceleration due to gravity \citep{Clanet2004} (figure~\ref{fig:summary}a, $F(t = 0.37\,\si{\milli\second}) \approx 5.1\,\si{\milli\newton}$).
 The force diminishes as the drop reaches its maximum spreading diameter (figure~\ref{fig:summary}a,b $t = t_m$). 
-\citet{zhang2022impact} revealed that also the jump-off is accompanied by a peak in the normal reaction force, which was up to then unknown (figure~\ref{fig:summary}a, 
-%$F_2(t_2 = 4.63\,\si{\milli\second}) \approx 2.3\,\si{\milli\newton}$ 
-\Rev{$F_2/(\rho_dV_0^2D_0^2) \approx$ 0.37, 0.337, 0.1 for $Oh = 0.0025, 0.06,\,\text{and}\,0.2$, respectively;
-for the second force peak amplitude--at time $t_2 \approx 0.42\sqrt{\rho_dD_0^3/\gamma}$ after impact)}.
+\citet{zhang2022impact} revealed that also the jump-off is accompanied by a peak in the normal reaction force, which was up to then unknown (figure~\ref{fig:summary}a, $F_2(t_2 = 4.63\,\si{\milli\second}) \approx 2.3\,\si{\milli\newton}$ for the second force peak amplitude--at time $t_2$ after impact).
 The second peak in the force also coincides with the formation of a Worthington jet, a narrow upward jet of liquid that can form due to flow focusing by the retracting drop (figure~\ref{fig:summary}a,b $t = t_2$).
-Under certain conditions ($We \approx 9$, $Oh = 0.0025$), this peak can be even more pronounced than the first.
+Under certain conditions ($We \approx 9$), this peak can be even more pronounced than the first.
 This discovery is critical for superhydrophobicity which is volatile and can fail due to external disturbances such as pressure \citep{Lafuma2003, Callies2005, Sbragaglia2007, Li2017}, evaporation \citep{Tsai2010, Chen2012, Papadopoulos2013},  mechanical vibration \citep{Bormashenko2007}, or the impact forces of prior droplets \citep{Bartolo2006Bouncing}.
@@
 \Rev{Lastly, we keep the Bond number ($Bo$, see~\eqref{Eq:BoDefinition}) fixed at 1 throughout the manuscript.
-In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/(gD_0) = We/Bo$ comparing inertia with gravity.
+In our system, the relevance of gravity is characterized by the dimensionless Froude number $Fr = V_0^2/gD_0 = We/Bo$ comparing inertia with gravity.
 Throughout this manuscript, $Fr > 1$ and gravity's role is sub-dominant compared to inertia (for detailed discussion, see appendix~\ref{app:gravity}).}
@@
 The standard errors for impact velocities did not exceed $0.02\,\si{\meter}/\si{\second}$.
-For the same $Oh$ values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
+For the same Oh values, the impact velocities were $1.2 \pm 0.002\,\si{\meter}/\si{\second}$, $0.97 \pm 0.01\,\si{\meter}/\si{\second}$, and $0.96 \pm 0.01\,\si{\meter}/\si{\second}$, respectively.
 The combined errors in $D_0$ and $V_0$ resulted in approximately $\pm 7\%$ error in Weber number $We$ and $\pm 3\%$ error in Ohnesorge number $Oh$.
